---
title: "Untitled"
output: html_document
date: "2024-07-16"
editor_options: 
  chunk_output_type: console
---

#Aim 

Codes for DC paper 


#General

1) I probably want to extract additional info on the queens reproductive output like tenure length, number of pups produced, number of litter produced to assess whether it affects their competitive abilities. That could be a subsequent and more detailed analysis for why they lose.

2) Predictors of Queen competitive abilities (when fighting a helper)

3) Predictors of helper competitive abilities (when fighting a helper)


#Library

```{r}

library(tidyverse)

#Modelling 
library(glmmTMB)
library(brms)

#Posthoc comparisons
library(emmeans)
library(ggeffects)

```


#Directory

```{r}

DC_dir <- "C:/Users/Philippe/Dropbox/PhD_20150515/Research projects/DMR_HelperBreedingOpp/DC/DC_Analyses"

```



#Data 

```{csv}

#DC info
DC_Info_F <- read.csv("DC_Info_F_20240710.csv") %>% 
  
  #REFORMAT DATE
    mutate(BirthDate = ymd(BirthDate),
         PairingDate = ymd(PairingDate),
         KingRemovalDate = ymd(KingRemovalDate),
         OriginalGroup_LastParturitionDate = ymd(OriginalGroup_LastParturitionDate),
         IsolationDate = ymd(IsolationDate),
         DeathDate = ymd(DeathDate),
         LastDate = ymd(LastDate),
         FirstDCConceptionDate = ymd(FirstDCConceptionDate),
         FirstDCParturitionDate = ymd(FirstDCParturitionDate),
         EvictionDate = ymd(EvictionDate))


#Relevant weight
DC_ClosestWeight <- read.csv("DC_ClosestWeight_20240710.csv") %>% 
  mutate(Date = ymd(Date)) %>% 
  rename(WeightDate = Date)


#Urine info 
#check what info is there
DC_Info_Urine_F <- read.csv("DC_Info_Urine_F_20240710.csv") %>%
  rename(SampleID = UrineNumber) %>% 
  mutate(urineDate = ymd(UrineDate))



#Hormone concentration 
DC_Conc_All <-read.csv("DC_Conc_All_20240710.csv")

```


#Methods 

##Sample Size 

```{r}

#Number of pairs
SampleSize <- DC_Info_F %>% 
  group_by(Treatment) %>% 
  summarize(SampleSize = n_distinct(ExperimentalGroup)) %>% 
  ungroup()
View(SampleSize)
#12 Queens
#13 Sub 


#Number of groups from which females were taken
OriginalGroup_F <- DC_Info_F %>% 
  summarize(SampleSize = n_distinct(OriginalGroup))
View(OriginalGroup_F)
#17 groups


#Duration of isolation period 
IsolationDuration <-  DC_Info_F %>% 
  mutate(IsolDur = PairingDate - IsolationDate) %>% 
  distinct(ExperimentalGroup,.keep_all = TRUE) %>% 
  summarise(IsolMean = mean(IsolDur),
            SD = sd(IsolDur))
View(IsolationDuration)


#Number of groups where queen was removed 
KingRemovalCount <- DC_Info_F %>% 
  filter(!is.na(KingRemovalDate)) %>% 
  distinct(OriginalGroup,.keep_all = TRUE)
View(KingRemovalCount)
#10 groups meaning two groups already had their king removed


View(DC_Info_F %>% 
       filter(Treatment == "Queen",
              is.na(KingRemovalDate)) %>% 
       distinct(ExperimentalGroup,.keep_all = TRUE))
#In Ruru and the Maags the king was already absent


#Number of groups from which males were taken 

```



##Experimental design


###Age

Age of males and females at the beginning of the experiments (isolation)

```{r Summary}

#Age female
Age_Female <- DC_Info_F %>% 
  summarize(Min = min(Age/365.25, na.rm = T),
         Max = max(Age/365.25, na.rm = T),
         Median = median(Age/365.25, na.rm = T),
         Avg = mean(Age/365.25, na.rm = T),
         FirstQuartile = quantile(Age/365.25, probs = 0.25, na.rm = T)) %>% 
  ungroup()
View(Age_Female)

#Age of females by status
Age_Female_ByBS <- DC_Info_F %>% 
  group_by(BS_Original) %>% 
  summarize(Min = min(Age/365.25, na.rm = T),
         Max = max(Age/365.25, na.rm = T),
         Median = median(Age/365.25, na.rm = T),
         Avg = mean(Age/365.25, na.rm = T),
         FirstQuartile = quantile(Age/365.25, probs = 0.25, na.rm = T)) %>% 
  ungroup()
View(Age_Female)


#Age of females by status and treatment
Age_Female_ByBS <- DC_Info_F %>% 
  group_by(BS_Original, Treatment) %>% 
  summarize(Min = min(Age/365.25, na.rm = T),
         Max = max(Age/365.25, na.rm = T),
         Median = median(Age/365.25, na.rm = T),
         Avg = mean(Age/365.25, na.rm = T),
         FirstQuartile = quantile(Age/365.25, probs = 0.25, na.rm = T)) %>% 
  ungroup()


#Age of males



```


There is a trend for females to be older in the breeder treatment than in the non-breeder treatment

```{r Abs Treatment}

LM_Age <- lm(as.integer(Age/365.25) ~ Treatment, 
              data = DC_Info_F)
summary(LM_Age)
#There is a trend for females to be older in the queen treatment. It certainly is driven by the queens 

```


The age difference within pair is significantly greater in the breeder treatment than in the non-breeder treatment 

```{r Relative Treatment}

LM_AgeDiff <- lm(as.integer(AgeDiff/365.25) ~ Treatment, 
              data = DC_Info_F %>% 
                filter(AgeDiff_Cat == "Older"))
summary(LM_AgeDiff)
#There is a super significant difference in Age 

```


Breeding females are significantly older than paired daughters and females from the non-breeder treatment.

There are no differences in age between sub across treatments


```{r B/H}

#Model
LM_Age_BS <- lm(as.integer(Age/365.25) ~ BS_PlotCategory, 
              data = DC_Info_F)
summary(LM_Age_BS)


#Post hoc comparison
emm <- emmeans(LM_Age_BS, ~ BS_PlotCategory)
#Specify the contrast wanted
contrast(emm, method = list("Sub_Q - Sub_S" = c(0, 1, -1)))

```


```{r Plot}

#By treatment
ggplot(DC_Info_F,
       aes(x=BS_PlotCategory,y=Age)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col = BS_Original)) +

  theme_classic()

```


### BM 

There were no significant difference in BM at the start of the experiment across treatments

I guess one alternative would be to use all weights rather than just weight at a specific date. 

Also just check in data prep whether isolation weight and pairing weight had any constraints on whether was taken before or after. 

```{r Abs Isol}

#At isolation 
#Already moved into analyses (No model validation done yet)
LM_BMIsol <- lm(Weight ~ Treatment, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Isolation"))
summary(LM_BMIsol)

```


```{r Abs Pairing}

#At pairing
#Already moved into analyses (No model validation done yet)
LM_BMPairing <- lm(Weight ~ Treatment, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Pairing")) 
summary(LM_BMPairing)


```

There is no difference in body-mass difference within pair across treatment 
```{r Relative isol}

#At isolation 
LM_BMDiff_Isol <- lm(WeightDiff ~ Treatment, 
              data = WeightDiff %>% 
                filter(DateType == "Isolation",
                       WeightDiff_Cat == "Heavier"))
summary(LM_BMDiff_Isol)
#No significant difference
names(WeightDiff)


```


```{r Relative pairing}

#At isolation 
LM_BMDiff_Pair <- lm(WeightDiff ~ Treatment, 
              data = WeightDiff %>% 
                filter(DateType == "Pairing",
                       WeightDiff_Cat == "Heavier"))
summary(LM_BMDiff_Pair)
#No significant difference

```

Despite the lack of significant differences in body mass between queen and helpers, helpers were heavier than the animals they were paired with in 9/12 cases at isolation

i) Chouffe: NBF was 3 grams heavier 
ii) BitBurger: NBF was 8 grams heavier
iii) Leffe: NBF was 4g heavier at isolation, same at pairing, lighter at eviction.

```{r Plot}


#Heavier as focal 
ggplot(Heavier %>% 
         filter(DateType == "Isolation"),
       aes(x=Treatment,y=WeightDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col=BS_Original)) +

  theme_classic()
#At isolation 3 helpers heavier than queen
#Model suggests the difference is not significant though I have not done model validation on it

```


All of them eventually evicted the queen, despite Leffe getting much lighter

However this number goes up to 5 at eviction 

i) Chouffe: 4 grams heavier => evictor
ii) BitBurger: 15 grams heavier => evictor
iii) Tusker: 27 grams heavier => evictor 
iv) Guiness: 32 grams heavier => evictor 
v) Corona: 4 grams heavier => evictor 


```{r Plot}

#Sub heavier than queen at isolation 
View(HeavierIsol %>% 
       filter(Treatment == "Queen",
              Isolation_HeavierRef == 1, 
              BS_Original == "Helper"))
#There are 3 females sub that are heavier at isolation than queen 


#Sub heavier at queen at eviction 
View(WeightDiff %>% 
       filter(Treatment == "Queen",
              BS_Original == "Helper",
              DateType == "Eviction",
              WeightDiff_Cat == "Heavier"))


```

There are no differences in body mass between queen and helpers  from the queen and the sub treatment  

```{r B/H Isol}

#Are queen heavier than all other females?
LM_BMIsol_QueenSub <- lm(Weight ~ BS_PlotCategory, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Isolation"))
summary(LM_BMIsol_QueenSub)


#Post hoc comparison
emm <- emmeans(LM_BMIsol_QueenSub, ~ BS_PlotCategory)
#Specify the contrast wanted
contrast(emm, method = list("Sub_Q - Sub_S" = c(0, 1, -1)))



```


```{r B/H pairing}

LM_BMPair_QueenSub <- lm(Weight ~ BS_PlotCategory, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Pairing"))
summary(LM_BMPair_QueenSub)


emm <- emmeans(LM_BMPair_QueenSub, ~ BS_PlotCategory)
#Specify the contrast wanted
contrast(emm, method = list("Sub_Q - Sub_S" = c(0, 1, -1)))

```


###BM-Age correlation 

One wants to know whether there are any correlation between BM and age 


###Delta BM - Delta Age correlation 

One wants to know whether there are any correlation between differences in BM and differences in ages

#Occurences of eviction

There weer eviction in 23/25 groups. No eviction in DP and Lion, both from the sub treatment 

Thus there were 11/13 eviction in Sub and 12/12 in queen treatment 

```{r}

#Groups without eviction
View(DC_Info_F %>% 
       filter(EvictionStatus == "InGroup"))
#Lion and DP do not have eviction

```


Use Firth logistic regression or brms due to separation of data. Code available in DC_DataExploration. Copy and paste once a decision has been made



#Prob of winning


##All data

In the NBT, heavier helper at eviction have a 82% chance of victory. 9 wins and 2 losses

In the BT heavier helper at eviction have a 100% chance of victory. 5 wins

In the BT heavier queen at eviction have a 28.5% chance of vitory. 5 lossess and 2 wins 

The 3 helpers that were heavier than queens (Chouffe, Bitburger, Leffe) at pairing eventually evicted the queen (Note that Leffe was lighter at eviction). The 5 helpers that were heavier than queens at eviction were evictor (Chouffe, Bitburger, Tusker, Guiness, Corona). 


```{r Descriptive}

#How many queens were heavier at eviction
Eviction_BMdiff_BreederSum <- WeightDiff %>% 
       filter(BS_Original == "Breeder") %>% 
       group_by(DateType, EvictionStatus, WeightDiff_Cat) %>% 
       summarize(Count = n()) %>% 
       ungroup() %>% 
       arrange(DateType,
               EvictionStatus,
               WeightDiff_Cat)
View(Eviction_BMdiff_BreederSum)
#7 queens heavier (H lighter) => 2 evictor, 5 evictees => 28% chance of winning 
#5 queens lighter (H heavier) => all evicted 


#Likelihood to win if you are heavier at eviction
Eviction_Heavier_WinProb <- WeightDiff %>% 
       filter(WeightDiff_Cat == "Heavier",
              DateType == "Eviction") %>% 
       group_by(Treatment, BS_Original) %>% 
       summarize(Win = sum(EvictionStatus == "Evictor"),
                 Lose = sum(EvictionStatus == "Evictee")) %>% 
       ungroup() %>% 
  mutate(ProbWin = Win/ (Win+Lose))
View(Eviction_Heavier_WinProb)


#What are the two sub that lost despite being heavier
HeavierEvictee_NBT <- WeightDiff %>% 
       filter(Treatment == "Sub",
              DateType == "Eviction",
              EvictionStatus == "Evictee") 
View(HeavierEvictee_NBT)

View(WeightDiff)

```


For the model, I am planning to use the heavier animals as reference

```{r Data}

#Heavier as Reference
Heavier_Winp_Plot <- WeightDiff %>% 
  #RETAIN HEAVIER OR SAME 
  filter(WeightDiff_Cat %in% c("Same", "Heavier")) %>% 
  #REMOVE NO EVICTION GROUP
  #ADD Model CAT
  mutate(BM_MCat = case_when(Treatment == "Sub" ~ "HH",
                             Treatment == "Queen" & BS_Original == "Helper" ~ "HQ",
                             Treatment == "Queen" & BS_Original == "Breeder" ~ "QH"))




#Heavier as Reference
View(WeightDiff %>% 
       filter(EvictionStatus == "InGroup"))
```


```{r Plot}

#Isolation
HeavierI_Eviction_Plot <- ggplot(Heavier_Winp_Plot %>% 
                                   filter(DateType == "Isolation"),
       aes(x=BM_MCat,y=WeightDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col=EvictionStatus)) +

  theme_classic()
#At isolation 3 helpers heavier than queen
#Model suggests the difference is not significant though I have not done model validation on it


#Pairing


#Eviction






```



probwin ~ Dyad Type (3 levels S-S / S-Q / Q-S) fixing for the heavier animals 

Questions:
1) How to incorporate age info 
2) Can we use delat BM as continuous rather than binary? 
```{r Models}

probwin ~ Dyad Type 

```



##NBT 


##BT




