---
title: "Untitled"
output: html_document
date: '2023-01-16'
---

#General

Script started 16th January 2023 to generate a list of DC sample export and suggest a budget for hormone analyses to TCB


#Package 

```{r package, include=FALSE}

library(tidyverse)
library(RMySQL)
library(lubridate)

```


#DB connection

```{r data and functions}

#extract relevant info from database
#Only remove stuff from the original that can be found in Ratop
#All additions or changes must be done on the Rfile in Ratop, then copy pasted here
#don't run the new behaviour import if not necessary because it takes for ages
source("C:/Users/Philippe/Dropbox/PhD_20150515/Research projects/DMR_HelperBreedingOpp/DC/DC_Analyses/Database_Extract_DC_20230116.R")


#Load relevant functions
source("C:/Users/Philippe/Dropbox/PhD_20150515/Research projects/DMR_Ratop/DMRfunctions_20211109.R")


#Life History information 
source("C:/Users/Philippe/Dropbox/PhD_20150515/Research projects/DMR_Ratop/DMRfunctions_20211109.R")

```


#Experiment info 

##AnimalID

It looks like all the animals from the last round of pairing are missing. Asked Channen to fill the information on the 14/03/2023


```{r AnimalID}

#DC animals
#Could be used to query experiment start. The alternative is to use pairing date (currently used)
DC_AnimalID <- con %>%
  dbGetQuery ("SELECT AnimalID,
DATE(DateStart) AS StartDate
FROM Moleratdatabase.tblExperiments
WHERE Experiment = '49'") %>% 
  mutate(StartDate = ymd(StartDate)) %>%
  
  #REMOVE PUPS BORN OF DC 
  left_join(.,qry_BirthDate) %>% 
  filter(BirthDate < "2021/12/31") %>% 
  
  #DISTINCT 
  distinct(AnimalID)
View(DC_AnimalID)
#61 animals

#Check for duplicates
View(DC_AnimalID %>% 
       count(AnimalID))
#No duplicates 


#Males
DC_Males <- DC_AnimalID %>% 
  left_join(.,tblSex) %>% 
  filter(Sex == "M") %>% 
  distinct(AnimalID)
View(DC_Males)
#19 males 
#2 male are probably missing


#Females
DC_Females <- DC_AnimalID %>% 
  left_join(.,tblSex) %>% 
  filter(Sex == "F") %>% 
  distinct(AnimalID)
View(DC_Females)
#42 females
#That would be 21 groups

```


##Static 

```{r}

DC_AnimalID_Static <- DC_AnimalID %>% 
  idinfo_static()

names(DC_AnimalID_Static)

```

##Membership 


```{r Membership}

#Membership of DC animals
DC_Membership <- DC_AnimalID %>% 
  left_join(.,MembershipBetweenV2)
View(DC_Membership)

```

##Pairing info

Will be used to:
i) Pairing date = Start of experiment 
ii) Experimental group 


```{r Pairing info}

#Pairing info 
DC_PairingInfo <- DC_AnimalID %>% 
  left_join(., Pairing_Info) %>% 
  
  #RETAIN PAIRING OF INTEREST
  #After start of experiment
  filter(PairingDate > 	"2021-12-01") %>% 
  
  #MANUAL CORRECTION 
  mutate(AnimalID = case_when(AnimalID == "PPF008" & PairingID == 362 ~ "PPF009",
                              TRUE ~ AnimalID))
  
View(DC_PairingInfo)


##################################################DC

#Animals with multiple pairing 
#Check for duplicates
C_MutiplePairing <- DC_PairingInfo %>% 
  count(AnimalID) %>% 
  filter(n>1)
View(C_MutiplePairing)
#DRM006 is entered 2x 
#In Firestone and Kasteel

#Entries from animals that have been paired more than once
C_MutiplePairing_Info <- DC_PairingInfo %>% 
  filter(AnimalID %in% C_MutiplePairing$AnimalID)
View(C_MutiplePairing_Info)
#PPF008 is paired in both Chouffe and Delirium on the same date. To be corrected 


#AnimalID without pairing
View(anti_join(DC_AnimalID,DC_PairingInfo))


#Groups that do not have 3 animals as they should
C_WrongGroupSize <- DC_PairingInfo %>% 
  group_by(PairingColony) %>% 
  mutate(GroupSize = n()) %>% 
  ungroup() %>% 
  filter(GroupSize !=3)
View(C_WrongGroupSize)
#Delirium is missing its male

```


```{r ExperimentalGroup}

#ExperimentalGroup 
DC_ExperimentalGroup <- DC_PairingInfo %>% 
  select(AnimalID,
         PairingColony) %>% 
  rename(ExperimentalGroup = PairingColony)
View(DC_ExperimentalGroup)

```


```{r PairingDate}

#StartDate = PairingDate
DC_PairingDates <- DC_PairingInfo %>% 
  select(AnimalID,
         PairingDate)
View(DC_PairingDates)

```


##Pre-Pairing info

Will be used to:
i) Isolation date: Date at which they were removed from the group to go to isolation group
ii) Original group: queried as group they belonged to 6 months before the experiment started  

```{r Pre-Pairing Group}

DC_PrePairingGroup <- DC_PairingDates %>% 
  mutate(Date = PairingDate - 180) %>% 
  membership() %>% 
  select(AnimalID,
         Colony) %>% 
  rename(OriginalGroup = Colony)
View(DC_PrePairingGroup)


```


```{r IsolationDates}
names(MembershipBetweenV2)
#When they were removed from their original group 


#OriginalGroup
DC_OriginalGroup_Membership <- DC_PrePairingGroup %>% 
  left_join(.,MembershipBetweenV2, by = c("OriginalGroup" = "Colony", "AnimalID" = "AnimalID")) %>%
  
  #DISTINCT
  distinct()
View(DC_OriginalGroup_Membership)

#Duplicate
# DC_OriginalGroup_Membership_Duplicate <- DC_OriginalGroup_Membership %>% 
#   count(AnimalID)
# View(DC_OriginalGroup_Membership_Duplicate)


#Last stay in OriginalGroup
DC_OriginalGroup_LastMembership <-  DC_OriginalGroup_Membership %>% 
  
  #RETAIN LAST MEMBERSHIP
  #If not done, duplicated rows of animals ID (in and out of their group)
  group_by(AnimalID) %>% 
  slice_max(MemberTo) %>% 
  ungroup()
  
View(DC_OriginalGroup_LastMembership)
#1 row less than DC animals


################################################### DC 
#Animals missing from membership
MissingOriginalGroup <- anti_join(DC_AnimalID, DC_OriginalGroup_Membership)
#PPF009 but it is because it is missing from tblPairings. Once it is corrected, it will cascade here

#Info of missing animals
MissingOriginalGroup_MembershipInfo <- MembershipBetweenV2 %>% filter(AnimalID %in% MissingOriginalGroup$AnimalID) 
View(MissingOriginalGroup_MembershipInfo)

################################################### DC 

DC_IsolationDates <- DC_OriginalGroup_LastMembership %>% 
  select(AnimalID, 
         MemberTo) %>% 
  rename(IsolationDate = MemberTo)
View(DC_IsolationDates)
```


## Treatment 


```{r Treatment}

#Original BS 
DC_Females_OriginalBS <- DC_Females %>% 
  
  #ADD FIRST PARTURITION DATE
  left_join(., DC_AnimalID_Static %>% 
              select(AnimalID,
                     FirstParturitionDate) %>% 
              filter(FirstParturitionDate < "2022-01-01")) %>% 
  
  #ADD BREEDINGSTATUS
  mutate(BS_Original = case_when(is.na(FirstParturitionDate) ~ "Helper", 
                                 TRUE ~ "Breeder")) %>% 
  select(AnimalID, 
         BS_Original)
View(DC_Females_OriginalBS)

#Treatment
DC_Treatment <- DC_Females %>% 
  
  #ADD EXPERIMENTAL GROUP 
  left_join(., DC_ExperimentalGroup) %>% 
  
  #ADD ORIGINAL BS 
  left_join(DC_Females_OriginalBS) %>% 
  
  #ADD BREED
  group_by(ExperimentalGroup) %>% 
  mutate(BF_Count = sum(BS_Original == "Breeder")) %>% 
  ungroup() %>% 
  
  #ADD TREATMENT 
  mutate(Treatment = case_when(BF_Count == 1 ~ "Queen",
                               BF_Count == 0 ~ "Sub", 
                               TRUE ~ "Problem")) %>% 
  
  #DISTINCT 
  #treatment is a group identity 
  distinct(ExperimentalGroup, 
           Treatment) %>% 
  filter(!is.na(ExperimentalGroup))
View(DC_Treatment)
#PPF009 has no treatment but that should eb solved after Channen has corrected table pairings 

#Duplicate
View(DC_Treatment %>% 
       count(AnimalID))
#PPF008 appears 2x because it appears in 2x Experimental group. Will be solved once Channen has corrected what I asked her to 



```


## Eviction 

```{r}

tblevictions_Corrected <- tblevictions %>% 
  mutate(AnimalID = case_when(EvictionRef == 166 ~ "DRF015", 
                              TRUE ~ AnimalID))

#Evictor 
DC_Evictor <- DC_AnimalID %>% 
  inner_join(., tblevictions_Corrected, by=c("AnimalID" = "EvictorID")) %>%
  #RETAIN ONLY EVICTOR AFTER EXPERIMENT START 
  filter(DateOfEviction > "2022-01-01") %>% 
  mutate(EvictionStatus = "Evictor") %>% 
  select(AnimalID, 
         DateOfEviction, 
         EvictionStatus) %>% 
  rename(EvictionDate = DateOfEviction) 


#Evictee 
DC_Evictee <- DC_AnimalID %>% 
  inner_join(., tblevictions_Corrected , by=c("AnimalID" = "AnimalID")) %>%
  mutate(EvictionStatus = "Evictee") %>% 
  select(AnimalID, 
         DateOfEviction, 
         EvictionStatus) %>% 
  rename(EvictionDate = DateOfEviction) 



#Join Evictor and Evictee
DC_EvictionInfo <- bind_rows(DC_Evictee, 
                         DC_Evictor) %>% 
  mutate(EvictionDate = ymd_hms(EvictionDate)) %>% 
  mutate(EvictionDate = ymd(EvictionDate))
str(DC_EvictionInfo)

```


#Parturition info 

The two experimental females gave birth in Tusker, Licher and Black Label. Co-breeding only occured in  

```{r Individual level}

#Females 
#Males would need the parentage to be updates

#Parturition info of DC females
DC_Parturition_Info_All <- DC_Females %>% 
  left_join(., Litter_Info)


#Parturition post experiment start 
DC_Parturition_Info_DC <- DC_Parturition_Info_All %>% 
  left_join(., DC_PairingDates, by=c("AnimalID" = "AnimalID")) %>% 
  filter(ParturitionDate > PairingDate.y) %>% 
  distinct()
View(DC_Parturition_Info_DC)


#First Parturition post experiment start
#Would it be of any use to 
DC_Parturition_Info_DCFirst <- DC_Parturition_Info_DC %>% 
  group_by(AnimalID) %>% 
  arrange(ParturitionDate) %>% 
  slice_min(ParturitionDate) %>% 
  ungroup()
View(DC_Parturition_Info_DCFirst)


```


```{r Group level}


#Groups in which 2 experimental females bred
DC_MultipleBreeding <- DC_Parturition_Info_DCFirst %>% 
  group_by(PairingColony) %>% 
  mutate(BF_Count = n_distinct(AnimalID),
         BF_SameGroup_Count = sum(PairingColony == ParturitionColony)) %>% 
  ungroup() %>% 
  filter(BF_Count > 1)
View(DC_MultipleBreeding)


#Gave birth in same group
DC_Breeding_SameGroup <- DC_MultipleBreeding %>% 
  filter(BF_SameGroup_Count == 2) %>% 
  select(AnimalID) %>% 
  left_join(., DC_Parturition_Info_DC)
View(DC_Breeding_SameGroup)
#Tusker, no eviction yet
#Apparently co-breeding is possible

  
#Gave birth in different group 
DC_Breeding_DifferentGroup <- DC_MultipleBreeding %>% 
  filter(BF_SameGroup_Count == 1) %>% 
    select(AnimalID) %>% 
  left_join(., DC_Parturition_Info_DC)
View(DC_Breeding_DifferentGroup)
#Licher and Black Label 
#But the second female gave birth in her eviction group 

```


# Abortion 

I am not sure yet how I will incorporate these data 
```{r Abortion}

#Get abortion event from DB 
Abortion <- con %>%
  dbGetQuery ("SELECT * FROM user_philippev.LH_Abortion") %>% 
  mutate(AbortionDate = ymd(AbortionDate))
View(Abortion)


#Abortion from DC females after start of experiment 
DC_Abortion <- DC_Females %>%
  left_join(., DC_PairingDates) %>% 
  inner_join(.,Abortion) %>% 
  #RETAIN ABORTION AFTER EXP START 
  filter(AbortionDate > PairingDate) %>% 
  rename(AbortionGroup = Colony)
View(DC_Abortion)
#Not sure what happened with RSF008, perhaps I need to integrate the preg check info


# #Group where the abortion occured 
# DC_Abortion_Membership <- DC_Abortion %>% 
#   select(-Colony) %>% 
#   membership(date = AbortionDate) %>% 
#   rename(AbortionGroup = Colony)

View(DC_Abortion_Membership)

```

#Death 

```{r Date}
names(DC_AnimalID_Static)

DC_DeathDates <- DC_AnimalID %>% 
  left_join(.,DC_AnimalID_Static %>% 
              select(AnimalID,
                     DeathDate))

```

#All relevant info 

AnimalID
Sex
OriginalGroup
IsolationDate
PairingDate
ExperimentalGroup
ExperimentalUnit
Treatment
BreedingStatus
EvictionStatus 
EvictionDate 
First Parturition Date
First Parturition Group 
Death date
ADD the ones I have not added yet


Some info should really be put in group info
i) group info should be done first 
ii) then add info that are really bound to the individual 

```{r Individual}

#add whether individual conceived in group  
#add whether individual bred in group
#In case two conceived add whether first conceiver
#In case two bred add first breeder 
#With this I can see whether the first breeder in the group was evicted 

DC_Info <- 
  #ADD ANIMALID 
  DC_AnimalID %>% 
  
  #ADD SEX AND DOB
  left_join(., DC_AnimalID_Static %>% 
              select(AnimalID, 
                     Sex, 
                     BirthDate)) %>% 
  
  #ADD PRE-ISOLATION GROUP 
  left_join(., DC_PrePairingGroup) %>% 
  
  #ADD ISOLATION DATE
  left_join(.,DC_IsolationDates) %>%
  
  #ADD PAIRING DATE
  left_join(., DC_PairingDates) %>%

  #ADD DEATHDATE
  left_join(., DC_DeathDates) %>%
  
  #ADD LAST DATE
  left_join(., LastDate %>% 
              select(AnimalID,
                     LastDate)) %>% 
  
  #ADD EXP GROUP
  left_join(.,DC_ExperimentalGroup) %>%
  
  #ADD EXPERIMENTAL UNIT 
  arrange(PairingDate,
          ExperimentalGroup,
          Sex) %>% 
  
  #ADD GROUP INDICES
  #Using match and unique https://stackoverflow.com/questions/72574649/dplyrcur-group-id-by-order-of-appearance-rather-than-alphabetical-order; otherwise cur_group_id or group_indices put them in the alphabetic order.
  mutate(ExperimentalUnit = match(ExperimentalGroup,
                                  unique(ExperimentalGroup))) %>%
  
  #ADD TREATMENT
  left_join(., DC_Treatment) %>%
  
  #ADD AGE AT ISOLATION 
  mutate(Age = IsolationDate - BirthDate) %>% 
  
  #ADD BREEDING STATUS
  #Only gives females, males are all breeders
  left_join(.,DC_Females_OriginalBS) %>%
  
  #ADD FIRST PARTURITION DATE AND GROUP 
  left_join(., DC_Parturition_Info_DCFirst %>% 
              select(AnimalID, 
                     ParturitionDate,
                     ParturitionColony) %>% 
              rename(FirstParturitionDate = ParturitionDate)) %>% 
  
    
  #ADD CONCEPTION DATE 
  #Take 88 days to make sure females are pregnant
  mutate(ConceptionDate = FirstParturitionDate - 88) %>% 
  
  #ADD FINAL BS
  #Watch out can be a breeder and evictee
  mutate(BS_Final = case_when(Sex == "M" ~ "Breeder",
                              Sex == "F" & !is.na(FirstParturitionDate) ~ "Breeder",
                               Sex == "F" & is.na(FirstParturitionDate) ~ "NonBreeder")) %>% 

  #ADD EVICTION STATUS AND DATE
  left_join(., DC_EvictionInfo) %>% 
  
    #ADD CONCEPTION CATEGORY 
  mutate(ConceptionCategory = case_when(ConceptionDate <= EvictionDate ~ "Conceived",
                                        !is.na(ConceptionDate) & is.na(EvictionDate) ~ "Conceived",
                                        TRUE ~ "NotConceived")) %>% 
  
  #REPLACE NA
  replace_na(list(EvictionStatus = "InGroup")) %>% 
  
  #ASSIGN STATUS TO MALE
  mutate(BS_Original = case_when(Sex == "M" ~ "Breeder",
                                 TRUE ~ BS_Original)) %>% 
  
  #RELEVEL 
  mutate(Treatment = fct_relevel(Treatment, "Sub", "Queen"),
         BS_Original = fct_relevel(BS_Original, "Helper", "Breeder"),
         BS_Original2 = fct_relevel(BS_Original, "Breeder", "Helper"),
         EvictionStatus = fct_relevel(EvictionStatus, "Evictor", "Evictee", "InGroup"),
         EvictionStatus2 = fct_relevel(EvictionStatus, "Evictee", "Evictor", "InGroup")) %>% 
  
  #ADD ISOLATION PERIOD
  mutate(IsolationPeriod = PairingDate - IsolationDate) %>% 
  
  #ADD EVICTION-PAIRING DELAY 
  mutate(EvictionPairingDayDiff = EvictionDate - PairingDate) %>%
  
  #ADD CONCEPTION-PAIRING DELAY  
  mutate(ConceptionPairingDayDiff = ConceptionDate - PairingDate) %>%
  
  #ADD CONCEPTION-EVICTION DELAY
  mutate(ConceptionEvictionDayDiff = ConceptionDate - EvictionDate) %>% 
  
  #ADD PARTURITION-PAIRING DELAY
  mutate(ParturitionPairingDayDiff = FirstParturitionDate - PairingDate) %>% 
  
  #ADD PARTURITION-EVICTION DELAY
  mutate(ParturitionEvictionDayDiff = FirstParturitionDate - EvictionDate)
  
  
  

write.csv(DC_Info,"DC_Info_20230329.csv",row.names = FALSE)

View(DC_Info)



###########################################Females
DC_Info_F <- DC_Info %>% 
  filter(Sex == "F") %>% 
  
  #ADD 
  
  #ADD A CATEGORY FOR PLOTTING THAT SEPARATE Q AND SUB
  mutate(BS_PlotCategory = case_when(BS_Original == "Helper" & Treatment == "Queen" ~ "Sub_Q",
                                  BS_Original == "Helper" & Treatment == "Sub" ~ "Sub_S", 
                                  TRUE ~ as.character(BS_Original))) %>% 
  mutate(BS_PlotCategory = fct_relevel(BS_PlotCategory, "Sub_S", "Sub_Q", "Breeder")) %>% 
  
  #ADD PARTNER ID 
  group_by(ExperimentalUnit) %>% 
  mutate(PartnerID1 = lead(AnimalID),
         PartnerID2 = lag(AnimalID)) %>%
  ungroup() %>%
  mutate(PartnerID = case_when(!is.na(PartnerID1) ~ PartnerID1,
                               !is.na(PartnerID2) ~ PartnerID2,
                               TRUE ~ "ToCheck")) %>% 
  select(-PartnerID1,
         -PartnerID2) %>% 
  
  #ADD PARTNER AGE
  left_join(., DC_Info %>% 
                select(AnimalID,
                       Age) %>% 
                rename(PartnerAge = Age), by =c("PartnerID" = "AnimalID")) %>% 
  
  
  #ADD AGE DIFFERENCE 
  mutate(AgeDiff = Age - PartnerAge) %>% 
  
  #ADD AGE DIFFERENCE CATEGORY 
  mutate(AgeDiff_Cat = case_when(AgeDiff > 0 ~ "Older",
                                 AgeDiff < 0 ~ "Younger")) 

View(DC_Info_F %>% 
       filter(EvictionStatus == "Evictor"))
unique()

View(DC_Info_F)

#write csv
write.csv(DC_Info_F,"DC_Info_F_20230329.csv",row.names = FALSE)

###########################################Males
DC_Info_M <- DC_Info %>% 
  filter(Sex == "M")
```


For group, I could add 
1) Evictor BS_Original 
2) Evictor ID?
3) Evictee ID?

```{r Group}

names(DC_Info_F)
#add whether an individual that bred in the group was evicted

#Could add a column in DC_Info_F: Conceived in group Y/N; Produced litter in group Y/N

DC_Info_Group <- DC_Info_F %>%
  
  #GROUP BY 
  group_by(ExperimentalGroup) %>% 
  
  #ADD GROUP EVICTION STATUS
  mutate(EvictionStatus_Group = case_when(sum(EvictionStatus == "Evictor") == 1 ~ "Eviction", 
                                 sum(EvictionStatus == "Evictor") == 0 ~ "NoEviction",
                                 TRUE ~ "Problem")) %>%
  
    #ADD GROUP BREEDING STATUS
    #Doesnt tell if co-breeding in same group
  mutate(BreederCount = sum(!is.na(FirstParturitionDate))) %>%
  
  mutate(CoBreeding = sum(!is.na(FirstParturitionDate) & ParturitionColony == ExperimentalGroup)) %>% 
    
    #ADD EARLIER FIRST PARTURITION 
    mutate(Earliest_FirstParturitionDate = min(FirstParturitionDate, na.rm = TRUE)) %>% 
    
    #ADD LATEST FIRST PARTURITION 
    mutate(Latest_FirstParturitionDate = max(FirstParturitionDate, na.rm = TRUE)) %>% 
    mutate(Latest_FirstParturitionDate = case_when(Earliest_FirstParturitionDate != Latest_FirstParturitionDate ~ Latest_FirstParturitionDate)) %>% 
  
  #ADD CONCEPTION DATE
  #mutate(ConceptionDate = Earliest_FirstParturitionDate - 88) %>% 
  
  #ADD EVICTION-PAIRING DELAY
  mutate(EvictionPairingDayDiff = EvictionDate - PairingDate) %>% 
  
  #ADD CONCEPTION-PAIRING DELAY 
  #mutate(ConceptionDelay = ConceptionDate -PairingDate) %>%
  
  #ADD CONCEPTION-EVICTION DELAY 
  
  
    #UNGROUP
  ungroup() %>% 
    
    #SELECT 
    select(ExperimentalGroup,
         Treatment,
         IsolationDate, 
         PairingDate, 
         #ConceptionDate,
         #ConceptionDelay,
         EvictionDate, 
         EvictionStatus_Group,
         BreederCount,
         CoBreeding,
         Earliest_FirstParturitionDate,
         Latest_FirstParturitionDate,
         EvictionPairingDayDiff) %>% 
    distinct()
View(DC_Info_Group)
#Guiness and Devils Peak give problem

write.csv(DC_Info_Group,"DC_Info_Group_20230329.csv",row.names = FALSE)

```




#Weight data 

```{r Weight}

#Male weight
DC_Weight <- DC_AnimalID %>% 
  left_join(.,tblWeights) %>% 
  left_join(., DC_Info %>%
              select(AnimalID, 
                     IsolationDate)) %>%
  #REMOVE WEIGHT MORE THAN 3 MONTHS BEFORE ISOLATION
  filter(WeightDate > IsolationDate - 90) %>% 
  select(-IsolationDate)
View(DC_Weight)

#Female weight
DC_Weight_F <- DC_Weight %>% 
  left_join(.,tblSex) %>% 
  filter(Sex == "F")
View(DC_Weight_F)


#Male weight 
DC_Weight_M <- DC_Weight %>% 
 left_join(.,tblSex) %>% 
  filter(Sex == "M")

```



#Focal data 
Should all be stored new import way. 
Should be gotten out of focal pipeline. This pipeline must be finalized 

#Scan data 
Should all be stored new import way. 
Should be gotten out of scan pipeline. This pipeline must be finalized 

#Urine samples 

```{r Raw}

View(DC_Info)

#DC info to join to urine 
DC_Info_UrineJoin <- DC_Info %>% 
  select(ExperimentalGroup,
         AnimalID,
         Sex,
         Treatment,
         IsolationDate,
         IsolationPeriod,
         PairingDate,
         InGroupPeriod) %>% 
  left_join(.,DC_Info_Group %>% 
              select(ExperimentalGroup,
                     EvictionDate))

#All Urine 
#Collected within 3 months of isolation
DC_Urine <- DC_Info_UrineJoin %>% 
  left_join(.,Urine_Collected) %>% 
  filter(UrineDate > IsolationDate - 90)
View(DC_Urine)
#2229

#Female Urine
DC_Urine_F <- DC_Urine %>% 
  filter(Sex == "F")
View(DC_Urine_F)
#1941 samples 
names(DC_Urine_F)

#Male Urine 
DC_Urine_M <- DC_Urine %>% 
  left_join(., tblSex) %>% 
  filter(Sex == "M")

View()

 
```


```{r Data Prep}

```


#Plasma samples

```{r Raw}

#All Plasma 
#Collected within 3 months of isolation
DC_Plasma <- DC_AnimalID %>% 
  left_join(.,Plasma_Collected) %>% 
  left_join(., DC_IsolationDates) %>% 
  filter(PlasmaDate > IsolationDate - 90)
View(DC_Plasma)

#Female Plasma
DC_Plasma_F <- DC_Plasma %>% 
  left_join(., tblSex) %>% 
  filter(Sex == "F")

#Male Plasma 
DC_Plasma_M <- DC_Plasma %>% 
  left_join(., tblSex) %>% 
  filter(Sex == "M")
```
```{r Data Prep}

```

#Dates of interest

Done 

Isolation Dates: DONE
Pairing Dates: DONE
Eviction Dates: DONE 
Urine Dates: DONE
Plasma Date: DONE

Focal Dates
Scan Dates




```{r Reformatting}

#Isolation Dates 
Date_Isolation_ToAdd <- DC_IsolationDates %>% 
  mutate(DateType = "Isolation") %>% 
  rename(Date = IsolationDate)


#Pairing Dates
Date_Pairing_ToAdd <- DC_PairingDates %>% 
  mutate(DateType = "Pairing") %>% 
  rename(Date = PairingDate)

#Eviction Dates 
Date_Eviction_ToAdd <- DC_EvictionInfo %>%
  select(-EvictionStatus) %>% 
  mutate(DateType = "Eviction") %>% 
  rename(Date = EvictionDate)

#Urine Dates 
Date_Urine_ToAdd <- DC_Urine %>%
  select(AnimalID,
         UrineDate) %>% 
  mutate(DateType = "Urine") %>% 
  rename(Date = UrineDate)

#Plasma Dates 
Date_Plasma_ToAdd <- DC_Plasma %>%
  select(AnimalID,
         PlasmaDate) %>% 
  mutate(DateType = "Plasma") %>% 
  rename(Date = PlasmaDate)
```

```{r Merge }

DC_Dates <- bind_rows(Date_Isolation_ToAdd,
                      Date_Pairing_ToAdd,
                      Date_Eviction_ToAdd,
                      Date_Urine_ToAdd,
                      Date_Plasma_ToAdd) %>% 
  distinct()
View(DC_Dates)
#2085 dates with distinct 
#2156 if distinct is not run 

#Females dates
DC_Dates_F <- DC_Dates %>% 
  filter(AnimalID %in% DC_Info_F$AnimalID)

```


## Activation status 

```{r}

```



## Gestation status

```{r gestation status}

names(DC_Dates)
#run next parturition info. Only give info for females that gave birth 
DC_NextParturition_F <- DC_Dates_F %>% 
  
  #ADD STATIC 
  #INCLUDES INFO THAT WILL BE REQUIRED FOR FUNCTION 
  left_join(.,DC_AnimalID_Static) %>% 
  
  next_parturitioninfo() 
View(DC_NextParturition)
#only gets info for females that gave birth 
#1162 dates


names(DC_Dates_F)
#Get gestation status
IB_GestationStatus_Trimester <- 
  
  DC_NextParturition %>% 
  
  #GESTATION STATUS SEMESTER
  gestationstatus(date = Date,gestationsplit = "trimester") %>% 
  
  select(AnimalID,
         DateType,
         Date,
         NextParturition_ParturitionDayDiff,
         GestationStatus_Trimester)
View(IB_GestationStatus_Trimester)


#DC_Dates with gestation status
DC_Dates_F_GestStat <- DC_Dates_F %>% 
  left_join(.,IB_GestationStatus_Trimester) %>% 
  replace_na(list(GestationStatus_Trimester = "NotPregnant"))


args(gestationstatus)


  
#SELECT
  select(AnimalID,
         Date,
         DateType,
         FirstParturitionDate,
         NextParturition_ParturitionDayDiff) %>% 
  gestationstatus(gestationsplit = "trimester")

names(GestationStatus_DF)

args(gestationstatus)


```


#Age difference 

#Closest weight

I must have a look whether closest weight before takes into account weight that were collected on the date of interest. In our case (Isol, Pair, Eviction), that would be perfectly fine, even better. Tweak the functions accordingly (DC_DMRfunctions)


```{r}

DC_ClosestWeight_B <- DC_Dates %>% 
  add_closestweight_before() %>% 
  mutate(WeightDiff_Type = "Before") %>% 
  rename(Weight_DayDiff = ClosestWeightDayDiff_Before,
         Weight = ClosestWeight_Before)
names(DC_ClosestWeight_B)


DC_ClosestWeight_BA <- DC_Dates %>% 
  add_closestweight() %>% 
  mutate(WeightDiff_Type = "BeforeAfter") %>% 
  rename(Weight_DayDiff = ClosestWeightDayDiff,
         Weight = ClosestWeight)


DC_ClosestWeight_A <- DC_Dates %>% 
  add_closestweight_after() %>% 
  mutate(WeightDiff_Type = "After") %>% 
  rename(Weight_DayDiff = ClosestWeightDayDiff_After,
         Weight = ClosestWeight_After)

#Merge all weight 

DC_ClosestWeight <- bind_rows(DC_ClosestWeight_B,
                              DC_ClosestWeight_BA,
                              DC_ClosestWeight_A)

View(DC_ClosestWeight)


#write csv
write.csv(DC_ClosestWeight,"DC_ClosestWeight_20230329.csv",row.names = FALSE)



####################################################DC 

#Dates in DC_Dates without weight

#Should check weight that are not taken on time 

#Pivot longer

```

#Gestation status 
Would be good to add the gestation status at every time point 

#Urine status pipeline

#Plasma satus pipeline

#Hormone levels pipeline






