---
title: "Untitled"
output: html_document
date: '2023-03-15'
editor_options: 
  chunk_output_type: console
---

#Package

```{r}

library(DHARMa)
library(broom.mixed)

```


#General 

i) Perhaps the difference in BM shoudl be expressed as % of lighter individual BM instread as in absolute BM

ii) I guess some bits could be moved to data prep but the aim here is to tweak the data to visualize what is going on. Perhaps once it is consolidated and also used for models I can move to dataprep

#CSV 

```{r}

#DC info
#If brought as csv I need to do all the relabelling and reformatting
#Usually I won't work with the csv, but in case I have it if R crashes
DC_Info_F <- read.csv("DC_Info_F_20230329.csv") %>% 
  
  #REFORMAT DATE
  mutate(BirthDate = ymd(BirthDate),
         IsolationDate = ymd(IsolationDate),
         PairingDate = ymd(PairingDate)) %>%
  
  #RELEVEL FACTOR
  mutate(Treatment = fct_relevel(Treatment, "Sub", "Queen"),
         BS_Original = fct_relevel(BS_Original, "Helper", "Breeder"),
         BS_Original2 = fct_relevel(BS_Original, "Breeder", "Helper"),
         EvictionStatus = fct_relevel(EvictionStatus, "Evictor", "Evictee", "InGroup"),
         EvictionStatus2 = fct_relevel(EvictionStatus, "Evictee", "Evictor", "InGroup")) 

names(DC_Info_F)
  

#Relevant weight
DC_ClosestWeight <- read.csv("DC_ClosestWeight_20230329.csv")
names()


```

#Data 

The next section could be moved to data prep.

```{r DC}

#Join DC_Info with closest weight
#So far done for female only 
DC_Info_ClosestWeight <- DC_Info_F %>% 
  left_join(., DC_ClosestWeight) %>% 
  filter(WeightDiff_Type == "Before")
View(DC_Info_ClosestWeight)



#Assign a reference for heavier animal at isolation 
HeavierIsolation <- DC_Info_ClosestWeight%>%
  filter(DateType == "Isolation") %>%
  #ADD HEAVIER REF 
  group_by(ExperimentalGroup) %>% 
  arrange(desc(Weight)) %>% 
  mutate(Isolation_HeavierRef = row_number()) %>% 
  ungroup() %>% 
  #ARRANGE
  arrange(ExperimentalGroup, 
          Isolation_HeavierRef) %>% 
  distinct(AnimalID,
           Isolation_HeavierRef)
View(HeavierIsolation)


#Select relevant Date type of weight
ClosestWeight_Milestone <- DC_Info_ClosestWeight %>% 
  
  #RETAIN RELEVANT WEIGHT DATES
  filter(DateType %in% c("Isolation", "Pairing", "Eviction"), 
         WeightDiff_Type == "Before") %>% 
  
  #ADD HEAVIER REF 
  left_join(.,HeavierIsolation) %>% 
  
  #ADD EVICTION STATUS FOR PLOTTING INGROUP ASSIGN EVICTOR AND EVICTEE
  mutate(EvictionStatus_Plot = case_when(EvictionStatus == "InGroup" & Isolation_HeavierRef == 1 ~ "Evictor", 
                                        EvictionStatus == "InGroup" & Isolation_HeavierRef == 2 ~ "Evictee", 
                                        TRUE ~ as.character(EvictionStatus))) %>% 
  
  mutate(EvictionStatus_Plot = fct_relevel(EvictionStatus_Plot, "Evictor", "Evictee")) %>% 
  
  #RELEVEL DATE TYPE
  mutate(DateType = fct_relevel(DateType, "Isolation", "Pairing", "Eviction")) %>% 
  
  #ARRANGE
  #Heavier animal first 
  arrange(ExperimentalUnit,
          DateType,
          desc(Weight))
names(ClosestWeight_Milestone)



###################################################DC 

#Count of weigth per experimental group and Date Type
#Should be = 2
C_WeightDiff_Count <- ClosestWeight_Milestone %>% 
       group_by(ExperimentalGroup, 
                DateType) %>% 
       mutate(n = n())
names(C_WeightDiff_Count)

#Not equal to 2
C_WeightDiff_WrongCount <- C_WeightDiff_Count %>% 
       filter(n !=2)
View(C_WeightDiff_WrongCount)
#All good 2 weights per category

# View(ClosestWeight_Milestone %>% 
#   filter(AnimalID %in% c ("PF009", "DRF015")))

#Same weight
SameWeight <- ClosestWeight_Milestone %>% 
  group_by(ExperimentalGroup,
           DateType) %>% 
  mutate(WeightDiff = Weight - lead(Weight)) %>% 
  filter(WeightDiff == 0)
View(SameWeight)
#No weight difference of 0
#Heavier animals always first 


#Min
#Max
#Avg 
#Median 
#Off day difference for each categor

#Percentage of data that was not collected on the day of isolation, pairing or eviction 

```

Weight diff contains all information from DC_Info_F, with weight difference. It could be moved to data prep

```{r WeightDiff}

WeightDiff <- ClosestWeight_Milestone %>% 
  
  #ADD PARTNER WEIGHT INFO
  left_join(ClosestWeight_Milestone %>% 
              select(AnimalID, 
                     DateType,
                     Weight) %>% 
              rename(PartnerWeight = Weight), by=c("PartnerID" = "AnimalID", "DateType" = "DateType")) %>% 
  
  #ADD WEIGHT DIFF 
  mutate(WeightDiff = Weight - PartnerWeight) %>% 
  
  #ADD HEAVIER CATEGORY 
  group_by(ExperimentalGroup,
           DateType) %>% 
  mutate(WeightDiff_Cat = case_when(WeightDiff > 0 ~ "Heavier",
                                    WeightDiff == 0 ~ "Same",
                                    WeightDiff < 0 ~ "Lighter"))
View(WeightDiff)

```


```{r Focal}

#Heavier animal as focal 
Heavier <- WeightDiff %>% 
  filter(WeightDiff > 0)
View(HeavierFocal)

#Lighter animal as focal
Lighter <- WeightDiff %>% 
  filter(WeightDiff < 0)

#Remove info of lighter individual at isolation
HeavierIsol <- WeightDiff  %>% 
  filter(Isolation_HeavierRef == 1)
View(HeavierIsol)

#Could add heavier pairing 
#Could add heavier eviction

#Evictor as focal
#InGroup have been assigned a status 
Evictor <- WeightDiff  %>% 
  filter(EvictionStatus_Plot == "Evictor")

#Evictee as focal
#InGroup have been assigned a status 
Evictee <- WeightDiff  %>% 
  filter(EvictionStatus_Plot == "Evictee")

#Older as focal 
Older <- WeightDiff  %>% 
  filter(AgeDiff > 0)

#Younger as focal 
Younger <- WeightDiff  %>% 
  filter(AgeDiff < 0)

```



#Sample size 

10x sub treatment 
11x queen treatment; 2 queens are lighter and could be excluded from analyses

```{r Treatment} 

SampleSize <- DC_Info %>% 
  group_by(Treatment) %>% 
  summarize(SampleSize = n_distinct(ExperimentalGroup)) %>% 
  ungroup()
View(SampleSize)

```


#Experimental design 

##BM absolute

At isolation body-mass and variance in body-mass is greater in the sub treatment.

For the next round, it would be useful to use heavier BF (>150-160). See BM differences section for further info on BM differences.

In the queen treatment, Queen are relatively heavier than NBF, but we have decided to constrain this by design. 

```{r Summary}

names(ClosestWeight_Milestone )

#Without distinction Sub-Queen 
BM_Summary <- ClosestWeight_Milestone %>% 
  group_by(Treatment) %>% 
  summarize(Min = min(Weight),
         Max = max(Weight),
         Median = median(Weight),
         Avg = mean(Weight),
         FirstQuartile = quantile(Weight, probs = 0.25),
         ThirdQuartile = quantile(Weight, probs = 0.75),
         SD = sd(Weight)) %>% 
  ungroup()
View(BM_Summary)

#With Distinction Sub-Queen
BM_Summary_SubQueen <- ClosestWeight_Milestone %>% 
  group_by(Treatment, 
           BS_Original) %>% 
  summarize(Min = min(Weight),
         Max = max(Weight),
         Median = median(Weight),
         Avg = mean(Weight),
         FirstQuartile = quantile(Weight, probs = 0.25),
         ThirdQuartile = quantile(Weight, probs = 0.75)) %>% 
  ungroup()
View(BM_Summary_SubQueen)
         

```

Linear models show no difference in body mass at both idolation and pairing 

```{r LM}

#At isolation 
#Already moved into analyses (No model validation done yet)
LM_BMIsol <- lm(Weight ~ Treatment, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Isolation"))
summary(LM_BMIsol)


#At pairing
#Already moved into analyses (No model validation done yet)
LM_BMPairing <- lm(lm(Weight ~ Treatment, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Pairing"))) 
summary(LM_BMPairing)

#Are queen heavier than sub from both treatment
LM_BMIsol_QueenSub <- lm(lm(Weight ~ BS_Original, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Isolation"))) 
summary(LM_BMIsol_QueenSub)


#Are queen heavier than sub from queen treatment 
LM_BMPairing_QueenSub <- lm(lm(Weight ~ BS_Original, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Pairing"))) 
summary(LM_BMPairing_QueenSub)


#Are queen heavier than sub from both treatment
LM_BMIsol_QueenSub_QT <- lm(lm(Weight ~ BS_Original, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Isolation",
                       Treatment == "Queen"))) 
summary(LM_BMIsol_QueenSub_QT)


#Are queen heavier than sub from queen treatment 
LM_BMPairing_QueenSub_QT <- lm(lm(Weight ~ BS_Original, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Pairing",
                       Treatment == "Queen"))) 
summary(LM_BMPairing_QueenSub_QT)

```


```{r Plot}

#By treatment
ggplot(ClosestWeight_Milestone %>% 
         filter(DateType == "Isolation"),
       aes(x=Treatment,y=Weight)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col = BS_Original)) +

  theme_classic()

#Plot separating sub_Q and Queen 
ggplot(ClosestWeight_Milestone  %>% 
         filter(DateType == "Isolation"),
       aes(x=PlotCategory,y=Weight)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5) +

  theme_classic()

```

##BM Differences

At the start of the experiment, differences in body mass between the heavier animals and the lighter animals are greater in the sub treatment. Also variance in differences in BM is greater in the sub treatment that in the queen treatment. 

For the next round 

In the queen treatment:
Use queens that are as heavy as possible (> 160g) with BM difference > 20g

In the sub treatment:
Use Have a few sub with small BM difference (about 10g)

In the queen treatment, queens were heavier than subordinate in all but two experimental pair:
i) Chouffe: NBF was 3 grams heavier 
ii) BitBurger: NBF was 8 grams heavier

These two groups could be removed from analyses, which would bring the sample size to 9 instead of 11. In doing so, we would also minimize differences in BM and differences in BM across treatments 

```{r Summary}

BMdiff_Summary <- HeavierIsol %>% 
  filter(DateType == "Isolation") %>% 
  group_by(Treatment) %>% 
  summarize(Min = min(WeightDiff),
         Max = max(WeightDiff),
         Median = median(WeightDiff),
         Avg = mean(WeightDiff),
         FirstQuartile = quantile(WeightDiff, probs = 0.25),
         ThirdQuartile = quantile(WeightDiff, probs = 0.75),
         SD = sd(WeightDiff)) %>% 
  ungroup()
View(BMdiff_Summary)

```


```{r Details}

#Sub heavier than queen at isolation 
View(HeavierIsol %>% 
       filter(Treatment == "Queen",
              HeavierRef == 1, 
              BS_Original == "Helper"))
```

```{r Models}

View(WeightDiff)

#At isolation 
#Will this be changed after the addition of the last round?
LM_BMDiff_Isol <- lm(WeightDiff ~ Treatment, 
              data = WeightDiff %>% 
                filter(DateType == "Isolation",
                       WeightDiff_Cat == "Heavier"))
summary(LM_BMDiff_Isol)

#At pairing
LM_BMDiff_Pairing <- lm(WeightDiff ~ Treatment, 
              data = WeightDiff %>% 
                filter(DateType == "Pairing",
                       WeightDiff_Cat == "Heavier"))
summary(LM_BMDiff_Pairing)

```

```{r Plot}

#Heavier as focal 
ggplot(HeavierFocal %>% 
         filter(DateType == "Isolation"),
       aes(x=Treatment,y=WeightDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col=BS_Original)) +

  theme_classic()


```

## Age absolute

Females from the queen treatment are on average 3 times older than females from the sub treatment. This is due to queens being much older than sub.

For the next round:

Queen treatment: 
i) Use younger queen and older sub. That will also contribute to lower age difference 

Sub treatment 
ii) Use subordinate that are 5.5 years at least. 

```{r Summary}
names(DC_Info)

#Age summary 
Age_Summary <- DC_Info_F %>% 
  
  #SUMMARY
  group_by(Treatment) %>% 
  summarize(Min = min(Age),
         Max = max(Age),
         Median = median(Age),
         Avg = mean(Age),
         FirstQuartile = quantile(Age, probs = 0.25),
         ThirdQuartile = quantile(Age, probs = 0.75),
         SD = sd(Age)) %>% 
  ungroup()
View(Age_Summary)


#Age summary, separating queen and sub in queen treatment
Age_SubQueen_Summary <- DC_Info_F %>% 
  #AGE AT ISOL
  mutate(Age = IsolationDate - BirthDate) %>% 
  
  #SUMMARY
  group_by(Treatment,
           BS_Original) %>% 
  summarize(Min = min(Age),
         Max = max(Age),
         Median = median(Age),
         Avg = mean(Age),
         FirstQuartile = quantile(Age, probs = 0.25),
         ThirdQuartile = quantile(Age, probs = 0.75),
         SD = sd(Age)) %>% 
  ungroup()
View(Age_SubQueen_Summary)

```

```{r Models}


LM_Age <- lm(as.integer(Age) ~ Treatment, 
              data = DC_Info_F)
summary(LM_AgeDiff)


```


```{r Plot}

#By treatment
ggplot(DC_Info_F,
       aes(x=Treatment,y=Age)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col = BS_Original)) +

  theme_classic()


#By treatment, separating queen and 
ggplot(DC_Info_F,
       aes(x=Treatment,y=Age)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col = BS_Original)) +

  theme_classic()

names(DC_Info_F)

#By treatment + separating sub_Q and Queen 
ggplot(DC_Info_F,
       aes(x=PlotCategory,y=Age/365)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5) +

  theme_classic()





```


## Age difference

The average age difference between females is 300 days in the sub treatment and over 3 years in the Queen treatment 

For the next round 

Queen treatment:
i) Minimize age difference 
ii) Use younger queen and older sub

Sub treatment: 
i) Maximize age difference (should try to have difference of at least 1200 days)
ii) Use one very old sub within the pair 

```{r Summary}

AgeDiff_Summary <- OlderFocal %>% 

  #SUMMARY
  group_by(Treatment) %>% 
  summarize(Min = min(AgeDiff),
         Max = max(AgeDiff),
         Median = median(AgeDiff),
         Avg = mean(AgeDiff),
         FirstQuartile = quantile(AgeDiff, probs = 0.25),
         ThirdQuartile = quantile(AgeDiff, probs = 0.75),
         SD = sd(AgeDiff)) %>% 
  ungroup()
View(AgeDiff_Summary)


```

```{r Model}

View(DC_Info_F)

LM_AgeDiff <- lm(as.integer(AgeDiff) ~ Treatment, 
              data = DC_Info_F %>% 
                filter(AgeDiff_Cat == "Older"))
summary(LM_AgeDiff)

```

```{r Plot}

ggplot(OlderFocal,
       aes(x=Treatment,y=AgeDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col=BS_Original)) +

  theme_classic()

```

##Correlation BM and Age Diff 

```{r Data}

#Prepare data 
#Center difference in Age, Note that this won't affect the slopes estimates. So it is not absolutely necessary, but makes Treatment ieffect interpretatble
BMDiff_LMdata <- WeightDiff %>% 
  filter(WeightDiff_Cat == "Heavier") %>% 
  group_by(Treatment,
           DateType) %>% 
  mutate(CentredBM = WeightDiff - mean(WeightDiff),
         CentredAgeDiff = AgeDiff - mean(AgeDiff)) %>% 
  ungroup()

```


```{r Model}

#All data
LM_BMAgeDiff <- lm(WeightDiff ~ CentredAgeDiff * Treatment, 
                   data = BMDiff_LMdata  %>% 
                     filter(DateType == "Isolation"))
summary(LM_BMAgeDiff)


#Sub treatment
LM_BMAgeDiff_ST <- lm(WeightDiff ~ CentredAgeDiff, 
                   data = BMDiff_LMdata %>% 
                     filter(DateType == "Isolation",
                            Treatment == "Sub"))
summary(LM_BMAgeDiff_ST)
#No correlation 


#Queen treatment 
LM_BMAgeDiff_QT <- lm(WeightDiff ~ CentredAgeDiff, 
                   data = BMDiff_LMdata %>% 
                     filter(DateType == "Isolation",
                            Treatment == "Queen"))
summary(LM_BMAgeDiff_QT)
#No correlation 

```

```{r}


#All data
LM_BMAgeDiff <- lm(WeightDiff ~ CentredAgeDiff * Treatment, 
                   data = BMDiff_LMdata  %>% 
                     filter(DateType == "Isolation"))
summary(LM_BMAgeDiff)


#Sub treatment
LM_BMAgeDiff_ST <- lm(WeightDiff ~ CentredAgeDiff, 
                   data = BMDiff_LMdata %>% 
                     filter(DateType == "Isolation",
                            Treatment == "Sub"))
summary(LM_BMAgeDiff_ST)
#No correlation 


#Queen treatment 
LM_BMAgeDiff_QT <- lm(WeightDiff ~ CentredAgeDiff, 
                   data = BMDiff_LMdata %>% 
                     filter(DateType == "Isolation",
                            Treatment == "Queen"))
summary(LM_BMAgeDiff_QT)
#Strong correlation 



```

```{r Plot}
#Older as reference 

#Correlation by breeding status
#Though there is no significant effect of breeding status  
ggplot(Older %>% filter(DateType == "Isolation"), aes(x = AgeDiff, y = WeightDiff, color = Treatment)) +
  
  #facet_grid(~DateType) +
  geom_hline(yintercept = 0) +
  
  geom_point(aes(shape = BS_Original)) + 
  
  geom_smooth(method = "lm") +
  
  theme_classic() +
  
  theme(legend.position = "none")

```


#Eviction

Eviction occurred in all but one group from the sub treatment (DevilsPeak, DOS = 18/07/2022) and in all but two group from the queen treatment (Tusker, DOS = 18/01/2022; WicklowWolf = 02/03/2023).

It is worth noticing (see later plots) that groups where there is no eviction are characterized by relatively larger BM and Age difference 

## Occurence
```{r No eviction}

#Groups without eviction
View(DC_Info_F %>% 
       filter(EvictionStatus == "InGroup"))

```


## Timing 

### Eviction delay

```{r Summary}


#Eviction delay
EvictionDelay_Summary <- DC_Info %>% 
  group_by(Treatment) %>% 
  summarize(Min = min(EvictionPairingDayDiff, na.rm = T),
         Max = max(EvictionPairingDayDiff, na.rm = T),
         Median = median(EvictionPairingDayDiff, na.rm = T),
         Avg = mean(EvictionPairingDayDiff, na.rm = T),
         FirstQuartile = quantile(EvictionPairingDayDiff, probs = 0.25, na.rm = T),
         ThirdQuartile = quantile(EvictionPairingDayDiff, probs = 0.75, na.rm = T),
         SD = sd(EvictionPairingDayDiff, na.rm = T))
View(EvictionDelay_Summary)

#All evictions occured within 21 days except in 4 groups 
#All groups where evictions occurred after 21 days are from the queen treatment 

#Isolation delay
#Must be added in DC_Info
# IsolationDelay_Summary <- DC_Info_F %>% 
#   group_by(Treatment) %>% 
#   summarize(Min = min(IsolationPeriod),
#          Max = max(IsolationPeriod),
#          Median = median(IsolationPeriod),
#          Avg = mean(IsolationPeriod),
#          FirstQuartile = quantile(IsolationPeriod, probs = 0.25),
#          ThirdQuartile = quantile(IsolationPeriod, probs = 0.75),
#          SD = sd(IsolationPeriod))
# View(IsolationDelay_Summary)

#Conception delay
# View(DC_Info_Group %>% 
#        select(ExperimentalGroup,
#               Treatment,
#               PairingDate,
#               ConceptionDelay) %>% 
#        arrange(Treatment,
#                ConceptionDelay))

```


```{r Model function}


#Lm 
evictiondelay_lm <- function(df) {
  glmmTMB( EvictionPairingDayDiff ~ Treatment, data = df)
}


#Poisson
evictiondelay_poiss <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, family = poisson, data = df)
}

#Generalized poisson
evictiondelay_genpoiss <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, family = genpois, data = df)
}
#Not tried yet

#Gamma models
evictiondelay_gamma <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, family = "Gamma", data = df)
}

#Gamma models
evictiondelay_gammalog <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, family = Gamma(link="log"), data = df)
}

#Not tried yet
#Negative binomial 1
evictiondelay_nb1 <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, family = nbinom1, data = df)
}

#Negative binomial 2
evictiondelay_nb2 <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, family = nbinom2, data = df)
}

evictiondelay_tweedie <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, data = df, family = "tweedie")
}

#Does not work, I ma not sure why. Perhaps because there is no random effect? 
evictiondelay_tweedieD <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, data = df, dispformula = ~Treatment, family = tweedie)
}



```

```{r Model dataset}

#Nested dataset
EvictionDelay_Nested <- DC_Info_Group %>% 
  select(ExperimentalGroup,
         Treatment,
         EvictionPairingDayDiff) %>% 
  mutate(EvictionPairingDayDiff = as.integer(EvictionPairingDayDiff)) %>% 
  nest()
View(EvictionDelay)

```



```{r Run Model}

EvictionDelay_Models_Wide <- EvictionDelay_Nested %>%
  
  #RUN MODEL OVER EACH ROWS
  #How could I automate this in one line of code 
  #To learn
  mutate(LM = map(data, evictiondelay_lm),
         P = map(data, evictiondelay_poiss),
         GP = map(data, evictiondelay_genpoiss),
         G = map(data, evictiondelay_gamma),
         GLog = map(data,evictiondelay_gammalog),
         NB1 = map(data, evictiondelay_nb1),
         NB2 = map(data, evictiondelay_nb2),
         Tw = map(data, evictiondelay_tweedie),
         TwD = map(data, evictiondelay_tweedieD))


#Long format
EvictionDelay_Models <- EvictionDelay_Models_Wide %>% 
  
  pivot_longer(cols = LM:TwD, names_to = "ModelType", values_to = "Model")

View(EvictionDelay_Models)

```

```{r MOdel info}


#Model info 
#Treatment to be used in predict function
pdata <- data.frame(Treatment = c("Sub", "Queen"))


#Put all model info together
EvictionDelay_Models_Info <- EvictionDelay_Models %>%
  
  #MODEL INFO 
  #Returned as list 
  mutate(Info = purrr::map(Model, ~family(.x))) %>% 
  
  #ADD FAMILY
  mutate(Family = purrr::map(Info, ~ pluck(.x$family))) %>% 
  
  #ADD LINK 
  mutate(Link = purrr::map(Info, ~ pluck(.x$link))) %>% 
  
  #ADD LINK INVERSE 
  mutate(LinkInv = purrr::map(Info, ~ pluck(.x$linkinv))) %>% 
  
  #ADD AIC 
  mutate(AIC = purrr::map_dbl(Model,~AIC(.x))) %>% 
  
  #ADD SIMULATED RESIDUALS
  mutate(SimResid = map(Model, ~simulateResiduals(fittedModel = .x, plot = F))) %>% 
  
  # #GGPREDICT 
  # mutate(Effect = map(Model, ~ Effect(mod = .x, term = "Treatment"))) %>% 
  # 
    #ADD MODEL PREDICTION
  mutate(Predict = map(Model, ~ predict(.x, newdata = pdata, type = "link", se.fit = TRUE))) %>% 
  
  #ADD MODEL PREDICTION
  mutate(Predict_R = map(Model, ~ predict(.x, newdata = pdata, type = "response", se.fit = TRUE))) 
View(EvictionDelay_Models_Info)

```

```{r Model output}

#EffectSize
EvictionDelay_ModelOutput_Link <- EvictionDelay_Models_Info %>% 
  
  #ADD COEFF
  mutate(Coeff = map(Model, ~tidy(.x))) %>%
  
  #UNNEST MODEL COEFF 
  unnest(Coeff) %>% 

  #ADD CI
  #The std.error are the std.error of the contrast, not of the predicted values, except for the intercept (because the intercept is the predicted value in relation to which the contrasts are expressed)
  mutate(Lower = estimate - (1.96*std.error),
         Upper = estimate + (1.96*std.error)) %>% 
  
  mutate_if(is.numeric, round, 5) %>% 
  
  #SELECT 
  select(
         ModelType,
         term,
         estimate,
         std.error,
         statistic,
         p.value,
         Lower,
         Upper)
  
View(EvictionDelay_ModelOutput_Link)


```

```{r Best models}
#Based on AIC 
#All 3 give warning 
#would need to ask Jacky what they mena and what shoudl be chosen


#There are 3 models with AIC of 141
#Glog
#G
#Tweedie Dispersion


#GLog 
Model_ValidationPlot_GLog <-  EvictionDelay_Models_Info %>% 
  select(
         ModelType,
         SimResid) %>% 
  
  filter(ModelType == "GLog") %>% 
  
  #PLOT MODEL 
  mutate(ModelPlot = purrr::map(SimResid, ~plot(.x))) 


#Gamma
Model_ValidationPlot_G <-  EvictionDelay_Models_Info %>% 
  select(ModelType,
         SimResid) %>% 
  
  filter(ModelType == "G") %>% 
  
  #PLOT MODEL 
  mutate(ModelPlot = purrr::map(SimResid, ~plot(.x))) 

#Tweedie dispersion 
Model_ValidationPlot_G <-  EvictionDelay_Models_Info %>% 
  select(ModelType,
         SimResid) %>% 
  
  filter(ModelType == "TwD") %>% 
  
  #PLOT MODEL 
  mutate(ModelPlot = purrr::map(SimResid, ~plot(.x))) 


```


```{r Plot}

#Data
EvictionDelay <- DC_Info_Group %>% 
  left_join(.,DC_Info_F %>% 
              filter(EvictionStatus == "Evictor") %>% 
              select(ExperimentalGroup, 
                     BS_Original))

View(EvictionDelay)

#Plot
#Remove group without eviction
ggplot(EvictionDelay %>% 
         filter(!is.na(BS_Original)),
       aes(x=Treatment,y=as.integer(EvictionPairingDayDiff))) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col = BS_Original)) +

  theme_classic()

```

###Eviction trigger 

Is eviction triggered by activation, pregnancies or parturition of Evictor? Evictee? Both? 

Activation will be determined through hormone analyses and can for now only be backtracked for animal that successfully gave birth.  

Pregnancies can be determined through LH, but hormone analyses could point detect undetected pregnancies .


4 females that were evicted produced a litter (Licher, Corbeau, Black Label, Guiness).

Corbeau (129 days) and Guiness (12 days) gave birth before they were evicted.   

Licher (43 days) and Black label (23 days) gave birth after they were evicted. Thus both were pregnant at the time of eviction


```{r}

names(DC_Info)

#Evicted females that gave birth 
Parturition_Evictee <- DC_Info %>% 
  filter(EvictionStatus == "Evictee" & !is.na(FirstParturitionDate))
View(Parturition_Evictee)

#Evicted female that gave birth before eviction 
Parturition_Evictee_Before <- Parturition_Evictee %>% 
  filter(EvictionDate > FirstParturitionDate)
View(Parturition_Evictee_Before)


#Evicted females that gave birth after eviction
Parturition_Evictee_After <- Parturition_Evictee %>% 
  filter(EvictionDate < FirstParturitionDate)
View(Parturition_Evictee_After)

```



#Relationship BM and Age

We had decided to constrain queen (which are also older) to be heavier. Thus in the queen treatment, Age and BM will be confounded. Perhaps, it would be good to add 4 queens that are lighter than sub?

Are age and BM confounded?

##Absolute

At the individual level, it does not seem. But what is most relevant is to have a look at:
i)queen treatment where queens are consistently older but also heavier by design => we would need queen lighter than sub

ii) sub treatment: Are heavier animals consistently older 

```{r Corvif}

```

```{r Plot}

#Correlation by breeding status 
#Points may be pulled by extreme points
ggplot(ClosestWeight_Milestone, aes(x = Age, y = Weight, color = BS_Original)) +
                           geom_point() + 
  geom_smooth(method = "lm")


#Correlation by breeding status and treatment 
#Points may be pulled by extreme points
ggplot(ClosestWeight_Milestone, aes(x = Age, y = Weight, color = PlotCategory)) +
                           geom_point() + 
  geom_smooth(method = "lm")


#Boxplot
ggplot(ClosestWeight_Milestone,
       aes(x=PlotCategory,y=Age/365)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 3, alpha = 0.8, aes(col = Weight)) +

  theme_classic()


```


#Relationship BM, Original BS and eviction

In the sub treatment, differences in body-mass are pretty consistent throughout the experiment. 

The heavier sub at isolation evicted the lighter sub in all but 2 groups (8/10).
i) Lighter animals (CUF031) evicted heavier (CUF012) in Trolls
ii) No eviction in Devils peak where DVF061 is >35g heavier than DVF048 

In the Queen treatment, differences in body-mass are pretty consistent throughout the experiment, though variance seems to increase

In contrast to the sub treatment, heavier females are consistently evicting lighter ones. In fact only 4/11 females that were heavier at isolation evicted, including the two sub that were heavier than the queen (Chouffe and BitBurger). 5/11 females, all queens, that were heavier at isolation and pairing (3/5 at eviction) were evicted by the lighter sub. 2/11 groups where the queen was heavier than then sub have had no eviction.  

Overall this highlight a different relationship between BM difference and likelihood of eviction in the Sub and the queen treatment. This is because despite being heavier, queen are more likely to be evicted than sub. Out of the 9 cases where there was eviction, the queen evicted 2x only and was evicted 7 times (2x it was lighter). 4 evicted queens were lighter than the sub at eviction (2 at isolation) whereas 3 were heavier (5 at isolation). That shows that among the 7 queens that were evicted, two did not maintain their BM advantage. 

Overall, it doesn't seem that the animals that evict have been gaining more BM throughout the experiment, relative to the evictor (sometimes the BM difference ecame more positive, sometimes more negative)

It is worth noticing that the three groups where there has been no eviction (Sub: DevilsPeak, DOS = 18/07/2022; Queen: Tusker, DOS = 18/01/2022; WicklowWolf = 02/03/2023) are characterized by the largest group difference (no competition?)

```{r Summary}

#SummaryTable Wide
SummaryTable_BMBS <- BM_EvictorFocal %>% 
   filter(EvictionStatus != "InGroup") %>% 
   group_by(DateType,
            Treatment,
            BS_Original) %>% 
   summarize(Heavier = sum(WeightDiff > 0),
          Lower = sum(WeightDiff <0)) %>% 
   ungroup()
View(SummaryTable_BMBS)
 

#Summary Long format
SummaryTable_BMBS_Long <- SummaryTable_BMBS %>% 
   pivot_longer(cols = Heavier:Lower,names_to = "BM",values_to = "Count")
View(SummaryTable_BMBS_Long)
 

#Plot 
ggplot(SummaryTable_BMBS_Long,
   aes(x = BS_Original, y = Count, fill = BM)) +
  facet_grid(DateType ~ Treatment) +
  geom_col(position = "stack")

```


```{r Details}

#No eviction 
View(EvictorFocal %>% 
       filter( EvictionStatus== "InGroup"))
#WicklowWolf in Q treatment
#Tusker in Q treatment 
#DevilsPeak in Sub treatment


#Lighter sub that evicted heavier sub
View(EvictorFocal %>% 
       filter(Treatment == "Sub",
              EvictionStatus != "Evictee",
              HeavierRef == 2))
View(EvictorFocal)
#1/10 CUF031 evicted CUF012 in Trolls


#Lighter sub at isolation that evicted heavier queen
View(EvictorFocal %>% 
       filter(Treatment == "Queen",
              BS_Original == "Helper",
              EvictionStatus == "Evictor",
              DateType == "Isolation",
              HeavierRef == 2))
#5 sub evicted queens that were lighter 


#Lighter sub at eviction that evicted heavier queen 
View(EvictorFocal %>% 
       filter(Treatment == "Queen",
              BS_Original == "Helper",
              EvictionStatus == "Evictor",
              DateType == "Eviction",
              WeightDiff <= 0))
#Licher
#Black Label 
#Corbeau 

```


##Focal heavier

In the queen treatment 3 evictee (4 until pairing) are heavier and all of these individuals are queens


```{r Plot}

#Heavier as focal 
ggplot(HeavierIsol,
       aes(x=DateType,y=WeightDiff)) + 
  
  facet_wrap(~ Treatment) +
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.2, height = 0, size = 2.5, aes(col=EvictionStatus, shape = BS_Original)) +
  #geom_point(size = 2, alpha = 0.7, aes(col=EvictionStatus, shape = BS_Original)) +
  
  geom_line(aes(group = AnimalID), alpha = 0.5) +
  
  geom_hline(yintercept = 0) +

  theme_classic()


```

## Focal evictor

```{r Plot}

#Heavier as focal 
ggplot(EvictorFocal,
       aes(x=DateType,y=WeightDiff)) + 
  
  facet_wrap(~ Treatment) +
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=BS_Original, shape = EvictionStatus)) +
  #geom_point(size = 2, alpha = 0.7, aes(col=EvictionStatus, shape = BS_Original)) +
  
  geom_line(aes(group = AnimalID), alpha = 0.5) +
  
  geom_hline(yintercept = 0) +

  theme_classic()


```

```{r Comparisons}

ggplot(ClosestWeight_Milestone,
       aes(x=EvictionStatus_Plot,y=Weight)) + 
  
  facet_grid(DateType ~ Treatment) +
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=BS_Original, shape = EvictionStatus)) +
  #geom_point(size = 2, alpha = 0.7, aes(col=EvictionStatus, shape = BS_Original)) +
  
  geom_line(aes(group = ExperimentalGroup), alpha = 0.5) +
  
  geom_hline(yintercept = 0) +
  
  ylim(90,200)+

  theme_classic()


```



##For Loop
I can try to replicate body mass of both females in the pair throughout the experiment for each experimental unit. It will be useful to see which of the body-mass are asscoiated with pregnancies (this would affect the difference in body mass between the two individuals)

The figure should show:

Vertical lines:
- Isolation
- Pairing
- Eviction 
- First parturition (of both animals? only one)

LineType:
- Original BS 

Colour:
- Final eviction status

This has been started but not finished. At this stage, I think it is unecessary

```{r DataPrep}

#I will use isolation day as the reference 


#Join DC_Info with weight 
Plot_BM <- DC_Info %>%
  
  #RETAIN FEMALES
  filter(Sex == "F") %>% 
  
  #ADD WEIGHT
  left_join(.,DC_Weight) %>% 
  
  #ARRANGE
  arrange(ExperimentalGroup,
          AnimalID,
          WeightDate) %>%
  
  #ADD WEIGHT - ISOLATION DAY DIFF 
  mutate(Isolation_DayDiff = WeightDate - IsolationDate) %>% 

  #ADD WEIGHT - PAIRING DAY DIFF
  mutate(Pairing_DayDiff = WeightDate - PairingDate) %>% 
  
  #ADD PAIRING DAY DIFF TO PLOT
  mutate(Pairing_DayDiff_ToPlot = case_when(Pairing_DayDiff >= 0 ~ Pairing_DayDiff))

View(Plot_BM)

```


```{r One colony}
unique(Plot_BM$ExperimentalGroup)


#################################################Vertical lines

Pairing <- DC_Info_F %>% 
  filter(ExperimentalGroup == "Trolls") %>%
  mutate(PairingIsolation_DayDiff = PairingDate - IsolationDate) %>% #Could be added in DC_Info 
  pull(PairingIsolation_DayDiff) %>% 
  unique()
Pairing


Eviction <- DC_Info_F %>% 
  filter(ExperimentalGroup == "Trolls") %>%
  mutate(EvictionIsolation_DayDiff = EvictionDate - IsolationDate) %>% #Could be added in DC_Info 
  pull(EvictionIsolation_DayDiff) %>% 
  unique()
Eviction
  


#################################################Plot single group
  
  


ggplot(Plot_BM %>% 
         filter(ExperimentalGroup == "Trolls"), aes(x=Isolation_DayDiff, y=Weight, colour = EvictionStatus)) + 
  
  #ADD POINTS 
  geom_point(size = 1.5) +
  
  #ADD LINE
  geom_line(aes(group = AnimalID, linetype = BS_Original)) +
  
  #ADD VERTICAL LINES 
  geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
  geom_vline(xintercept = Pairing, colour = "blue", linetype = "dashed") +
  geom_vline(xintercept = Eviction, colour = "red", linetype = "dashed") +
  
  #POINT LABLELS
  geom_text(aes(label=Pairing_DayDiff_ToPlot, vjust= -0.5), size = 3) 
  #check_overlap = TRUE
      
 


```

```{r For loop}

```


#Relationship Age, Original BS and eviction 

In the queen treatment, queens are obviously always older than the subordinate they were paired with. Thus when queen evicts (n=2) they are older and when sub evict (n=7) they are younger

In the sub treatment older evicted 7 times and younger evicted 2 times. In 

For future rounds we shall try to find younger sub that are heavier than older sub (while maximizing BM difference? )

```{r Summary}

#This section is not really menaingful 

View(AgeDiff_EvictorFocal)

#SummaryTable Wide
SummaryTable_AgeBS <- AgeDiff_EvictorFocal  %>% 
   filter(EvictionStatus != "InGroup") %>% 
   group_by(Treatment,
            BS_Original) %>% 
   summarize(Older = sum(AgeDiff > 0),
          Younger = sum(AgeDiff <0), 
          Same = sum(AgeDiff == 0)) %>% 
   ungroup()
View(SummaryTable_AgeBS)
 

#Summary Long format
SummaryTable_AgeBS_Long <- SummaryTable_AgeBS %>% 
   pivot_longer(cols = Older:Same,names_to = "Age",values_to = "Count")
View(SummaryTable_AgeBS_Long)
 

#Plot 
ggplot(SummaryTable_AgeBS_Long,
   aes(x = BS_Original, y = Count, fill = Age)) +
  facet_grid(~ Treatment) +
  geom_col(position = "stack")


```

```{r Details}

#Younger sub that evicted older sub 
View(AgeDiff_EvictorFocal %>% 
       filter(Treatment == "Sub",
              AgeDiff <0) %>% 
       left_join(.,BM_EvictorFocal,by=c("AnimalID" = "AnimalID")))
#CUF031 (Trolls), lighter than evictee
#SOF006 (Firestone), heavier than evictee
#MIF016 (DjuDju), heavier than evictee


```

##Older focal

```{r Plot}


#Older as focal 
ggplot(OlderFocal,
       aes(x=Treatment,y=AgeDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=EvictionStatus)) +
  #geom_point(size = 2, alpha = 0.7, aes(col=EvictionStatus, shape = BS_Original)) +

  theme_classic()



```


##Evictor focal

```{r Plot}


#Heavier as focal 
#With InGroup
ggplot(AgeDiff_EvictorFocal,
       aes(x=Treatment,y=AgeDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=BS_Original, shape = EvictionStatus)) +
  
  geom_hline(yintercept = 0) +

  theme_classic()



#Heavier as focal 
#With InGroup
ggplot(AgeDiff_EvictorFocal %>% 
         filter(EvictionStatus != "InGroup"),
       aes(x=Treatment,y=AgeDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=BS_Original, shape = EvictionStatus)) +
  
  geom_hline(yintercept = 0) +

  theme_classic()


```

```{r Comparisons}

```


#Timing of eviction

Relative to pairing 
Relative to Conception 
Relative to Parturition 
When the two females got pregant (Licher and Black Label)

#Taking into account the gestation status of both animals