---
title: "Untitled"
output: html_document
date: '2023-03-15'
---

#General 

i) Perhaps the difference in BM shoudl be expressed as % of lighter individual BM instread as in absolute BM


#Data 

##Body-Mass 


```{r Difference}

#Join DC_Info with closest weight
DC_Info_ClosestWeight <- DC_Info_F %>% 
  left_join(., DC_ClosestWeight)
View(DC_Info_ClosestWeight)


#Assign a reference for heavier animal at isolation 
HeavierIsolation <- ClosestWeight_RelevantDateType %>%
  filter(DateType == "Isolation") %>%
  #ADD HEAVIER REF 
  group_by(ExperimentalGroup) %>% 
  arrange(desc(Weight)) %>% 
  mutate(HeavierRef = row_number()) %>% 
  ungroup() %>% 
  #ARRANGE
  arrange(ExperimentalGroup, 
          HeavierRef) %>% 
  distinct(AnimalID,
            HeavierRef)
View(HeavierIsolation)


#Select relevant Date type of weight
ClosestWeight_RelevantDateType <- DC_Info_ClosestWeight %>% 
  
  #RETAIN RELEVANT WEIGHT DATES
  filter(DateType %in% c("Isolation", "Pairing", "Eviction"), 
         WeightDiff_Type == "Before") %>% 
  
  #ADD HEAVIER REF 
  left_join(.,HeavierIsolation) %>% 
  
  #ADD EVICTION STATUS FOR PLOTTING INGROUP ASSIGN EVICTOR AND EVICTEE
  mutate(EvictionStatus_Plot = case_when(EvictionStatus == "InGroup" & HeavierRef == 1 ~ "Evictor", 
                                        EvictionStatus == "InGroup" & HeavierRef == 2 ~ "Evictee", 
                                        TRUE ~ as.character(EvictionStatus))) %>% 
  
  mutate(EvictionStatus_Plot = fct_relevel(EvictionStatus_Plot, "Evictor", "Evictee")) %>% 
  
  #RELEVEL DATE TYPE
  mutate(DateType = fct_relevel(DateType, "Isolation", "Pairing", "Eviction")) %>% 
  
  #ARRANGE
  #Heavier animal first 
  arrange(ExperimentalUnit,
          DateType,
          desc(Weight))
View(ClosestWeight_RelevantDateType)
names(ClosestWeight_RelevantDateType)


###################################################DC 

#Count of weigth per experimental group and Date Type
#Should be = 2
C_WeightDiff_Count <- ClosestWeight_RelevantDateType %>% 
       group_by(ExperimentalGroup, 
                DateType) %>% 
       mutate(n = n())
names(C_WeightDiff_Count)

#Not equal to 2
C_WeightDiff_WrongCount <- C_WeightDiff_Count %>% 
       filter(n !=2)
View(C_WeightDiff_WrongCount)
#All good 2 weights per category

# View(ClosestWeight_RelevantDateType %>% 
#   filter(AnimalID %in% c ("PF009", "DRF015")))

#Same weight
SameWeight <- ClosestWeight_RelevantDateType %>% 
  group_by(ExperimentalGroup,
           DateType) %>% 
  mutate(WeightDiff = Weight - lead(Weight)) %>% 
  filter(WeightDiff == 0)
View(SameWeight)
#No weight difference of 0
#Heavier animals always first 


#Min
#Max
#Avg 
#Median 
#Off day difference for each categor

#Percentage of data that was not collected on the day of isolation, pairing or eviction 

```


```{r Heavier focal}

#The identity of the heavier animal can change through time 

#Compute weight difference 
HeavierFocal_WithNa <- ClosestWeight_RelevantDateType %>% 
  
  #ADD WEIGHT DIFF 
  #retain info of heavier animals for ploting 
  #Make sure there is no weight difference of 0
  group_by(ExperimentalGroup,
           DateType) %>% 
  mutate(WeightDiff = Weight - lead(Weight)) %>% 
  
  #ADD PARTNER 
  mutate(PartnerID = lead(AnimalID)) %>% 
  ungroup()
View(HeavierFocal_WithNa)

#Remove info of lighter individual
#Heavier animal as focal 
HeavierFocal <- HeavierFocal_WithNa %>% 
  filter(!is.na(WeightDiff))
View(HeavierFocal)

```

```{r Heavier isolation}

#Compute weight difference 
HeavierIsol_WithNa <- ClosestWeight_RelevantDateType %>% 
  
  #ARRANGE 
  group_by(ExperimentalGroup, 
           DateType) %>% 
  arrange(HeavierRef) %>% 
  #ADD WEIGHT DIFF 
  #retain info of heavier animals at isolation 
  mutate(WeightDiff = Weight - lead(Weight)) %>% 
  
  #ADD PARTNER 
  mutate(PartnerID = lead(AnimalID)) %>%
  ungroup()
View(HeavierIsol_WithNa)

#Remove info of lighter individual at isolation
HeavierIsol <- HeavierIsol_WithNa %>% 
  filter(!is.na(WeightDiff))


```

```{r Evictor focal}

#Compute weight difference 
BM_EvictorFocal_WithNa <- ClosestWeight_RelevantDateType %>% 
  
  #ASSIGN A STATUS TO INGROUP 
  #So they can be shwon in plot as well
  #Keep heavier animal as reference 
  group_by(ExperimentalGroup, 
           DateType) %>% 

  
  #ARRANGE EVICTOR STATUS
  arrange(EvictionStatus_Plot) %>% 
  
  #ADD WEIGHT DIFF 
  #retain info of heavier animals for ploting 
  #Make sure there is no weight difference of 0
  mutate(WeightDiff = Weight - lead(Weight)) %>%
  
  #ADD PARTNER 
  mutate(PartnerID = lead(AnimalID)) %>%
  ungroup()
View(EvictorFocal_WithNa)


#Remove NA
BM_EvictorFocal <- EvictorFocal_WithNa %>% 
  filter(!is.na(WeightDiff))

```


## Age

```{r Older focal}
  

OlderFocal_WithNa <- DC_Info_F %>% 
  
  #ARRANGE 
  arrange(ExperimentalUnit,
          BirthDate) %>% 
  
  #ADD AGE DIFF 
  #retain info of older animals for plotting 
  group_by(ExperimentalGroup) %>% 
  mutate(AgeDiff = -(BirthDate - lead(BirthDate)),
         PartnerID = lead(AnimalID)) %>% 
  ungroup()
View(AgeDiff)

#Remove NA
OlderFocal <- AgeDiff_OlderFocal_WithNa %>% 
  filter(!is.na(AgeDiff))

```

```{r Evictor focal}

#Age reference
OlderRef <- DC_Info_F %>% 
  group_by(ExperimentalUnit) %>% 
  arrange(desc(Age)) %>% 
  mutate(AgeRef = row_number()) %>% 
  ungroup() %>% 
  distinct(AnimalID, 
           AgeRef)


AgeDiff_EvictorFocal_WithNa <- DC_Info_F %>%
  
  #ADD AGE REF 
  left_join(., OlderRef) %>% 
  
  #ADD EVICTION STATUS FOR PLOTTING INGROUP ASSIGN EVICTOR AND EVICTEE
  mutate(ES_PlotCategory = case_when(EvictionStatus == "InGroup" & AgeRef == 1 ~ "Evictor", 
                                        EvictionStatus == "InGroup" & AgeRef == 2 ~ "Evictee", 
                                        TRUE ~ as.character(EvictionStatus))) %>%  
  
  mutate(ES_PlotCategory = fct_relevel(ES_PlotCategory, "Evictor", "Evictee")) %>% 
  
  
  #ARRANGE 
  arrange(ExperimentalUnit,
          ES_PlotCategory) %>% 
  
  #ADD AGE DIFF 
  #retain info of older animals for plotting 
  group_by(ExperimentalGroup) %>% 
  mutate(AgeDiff = -(BirthDate - lead(BirthDate)),
         PartnerID = lead(AnimalID)) %>% 
  ungroup()

View(AgeDiff_EvictorFocal_WithNa)

#Remove NA
AgeDiff_EvictorFocal <- AgeDiff_EvictorFocal_WithNa %>% 
  filter(!is.na(AgeDiff))
View(AgeDiff_EvictorFocal)

```


##Age and BM

who do I want as a reference? Age difference (Older focal) or BM difference (Heavier focal)

```{r Heavier focal}

HeavierFocal_AgeDiff <- HeavierFocal %>% 
  left_join(., DC_Info %>% 
              select(AnimalID, 
                     Age) %>% 
              rename(PartnerAge = Age), by=c("PartnerID" = "AnimalID")) %>% 
  #ADD AGE DIFFERENCE
  mutate(AgeDiff = Age - PartnerAge) %>% 
  #ADD AGE DIFFERENCE CATEGORY 
  mutate(AgeDiff_Cat = case_when(AgeDiff > 0 ~ "Older",
                                 AgeDiff < 0 ~ "Younger"))

```


```{r Older focal} 

OlderFocal_BMDiff <- OlderFocal %>% 
  
  #ADD FOCAL BM
  left_join(., ClosestWeight_RelevantDateType %>% 
              select(AnimalID,
                     DateType,
                     Weight), by=c("AnimalID" = "AnimalID")) %>% 
  
  #ADD PARTNER BM
  left_join(., ClosestWeight_RelevantDateType %>% 
              select(AnimalID,
                     DateType,
                     Weight) %>% 
              rename(PartnerWeight = Weight), by=c("PartnerID" = "AnimalID", "DateType" = "DateType")) %>% 
  
  #ADD AGE DIFFERENCE
  mutate(WeightDiff = Weight - PartnerWeight) %>% 
  #ADD AGE DIFFERENCE CATEGORY 
  mutate(WeightDiff_Cat = case_when(WeightDiff > 0 ~ "Heavier",
                                 WeightDiff < 0 ~ "Lighter"))

```








#Sample size 

10x sub treatment 
11x queen treatment; 2 queens are lighter and could be excluded from analyses

```{r Treatment} 

SampleSize <- DC_Info %>% 
  group_by(Treatment) %>% 
  summarize(SampleSize = n_distinct(ExperimentalGroup)) %>% 
  ungroup()
View(SampleSize)

```


#Experimental design 

##BM absolute

At isolation body-mass and variance in body-mass is greater in the sub treatment.

For the next round, it would be useful to use heavier BF (>150-160). See BM differences section for further info on BM differences.

In the queen treatment, Queen are relatively heavier than NBF, but we have decided to constrain this by design. 

```{r Summary}

names(ClosestWeight_RelevantDateType )

#Without distinction Sub-Queen 
BM_Summary <- ClosestWeight_RelevantDateType %>% 
  group_by(Treatment) %>% 
  summarize(Min = min(Weight),
         Max = max(Weight),
         Median = median(Weight),
         Avg = mean(Weight),
         FirstQuartile = quantile(Weight, probs = 0.25),
         ThirdQuartile = quantile(Weight, probs = 0.75)) %>% 
  ungroup()
View(BM_Summary)

#With Distinction Sub-Queen
BM_Summary_SubQueen <- ClosestWeight_RelevantDateType %>% 
  group_by(Treatment, 
           BS_Original) %>% 
  summarize(Min = min(Weight),
         Max = max(Weight),
         Median = median(Weight),
         Avg = mean(Weight),
         FirstQuartile = quantile(Weight, probs = 0.25),
         ThirdQuartile = quantile(Weight, probs = 0.75)) %>% 
  ungroup()
View(BM_Summary_SubQueen)
         

```


```{r Plot}

#By treatment
ggplot(ClosestWeight_RelevantDateType %>% 
         filter(DateType == "Isolation"),
       aes(x=Treatment,y=Weight)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col = BS_Original)) +

  theme_classic()


#Plot separating sub_Q and Queen 
ggplot(ClosestWeight_RelevantDateType  %>% 
         filter(DateType == "Isolation"),
       aes(x=PlotCategory,y=Weight)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5) +

  theme_classic()

```

##BM Differences

At the start of the experiment, differences in body mass between the heavier animals and the lighter animals are greater in the sub treatment. Also variance in differences in BM is greater in the sub treatment that in the queen treatment. 

For the next round 

In the queen treatment:
Use queens that are as heavy as possible (> 160g) with BM difference > 20g

In the sub treatment:
Use Have a few sub with small BM difference (about 10g)

In the queen treatment, queens were heavier than subordinate in all but two experimental pair:
i) Chouffe: NBF was 3 grams heavier 
ii) BitBurger: NBF was 8 grams heavier

These two groups could be removed from analyses, which would bring the sample size to 9 instead of 11. In doing so, we would also minimize differences in BM and differences in BM across treatments 

```{r Summary}

BMdiff_Summary <- HeavierIsol %>% 
  filter(DateType == "Isolation") %>% 
  group_by(Treatment) %>% 
  summarize(Min = min(WeightDiff),
         Max = max(WeightDiff),
         Median = median(WeightDiff),
         Avg = mean(WeightDiff),
         FirstQuartile = quantile(WeightDiff, probs = 0.25),
         ThirdQuartile = quantile(WeightDiff, probs = 0.75)) %>% 
  ungroup()
View(BMdiff_Summary)

```


```{r Details}

#Sub heavier than queen at isolation 
View(HeavierIsol %>% 
       filter(Treatment == "Queen",
              HeavierRef == 1, 
              BS_Original == "Helper"))
```


```{r Plot}

#Heavier as focal 
ggplot(HeavierFocal %>% 
         filter(DateType == "Isolation"),
       aes(x=Treatment,y=WeightDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col=BS_Original)) +

  theme_classic()


```

## Age absolute

Females from the queen treatment are on average 3 times older than females from the sub treatment. This is due to queens being much older than sub.

For the next round:

Queen treatment: 
i) Use younger queen and older sub. That will also contribute to lower age difference 

Sub treatment 
ii) Use subordinate that are 5.5 years at least. 

```{r Summary}
names(DC_Info)

#Age summary 
Age_Summary <- DC_Info_F %>% 
  
  #SUMMARY
  group_by(Treatment) %>% 
  summarize(Min = min(Age),
         Max = max(Age),
         Median = median(Age),
         Avg = mean(Age),
         FirstQuartile = quantile(Age, probs = 0.25),
         ThirdQuartile = quantile(Age, probs = 0.75)) %>% 
  ungroup()
View(Age_Summary)


#Age summary, separating queen and sub in queen treatment
Age_SubQueen_Summary <- DC_Info_F %>% 
  #AGE AT ISOL
  mutate(Age = IsolationDate - BirthDate) %>% 
  
  #SUMMARY
  group_by(Treatment,
           BS_Original) %>% 
  summarize(Min = min(Age),
         Max = max(Age),
         Median = median(Age),
         Avg = mean(Age),
         FirstQuartile = quantile(Age, probs = 0.25),
         ThirdQuartile = quantile(Age, probs = 0.75)) %>% 
  ungroup()
View(Age_SubQueen_Summary)

```


```{r Plot}


#By treatment
ggplot(DC_Info_F,
       aes(x=Treatment,y=Age)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col = BS_Original)) +

  theme_classic()


#By treatment, separating queen and 
ggplot(DC_Info_F,
       aes(x=Treatment,y=Age)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col = BS_Original)) +

  theme_classic()

names(DC_Info_F)

#By treatment + separating sub_Q and Queen 
ggplot(DC_Info_F,
       aes(x=PlotCategory,y=Age/365)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5) +

  theme_classic()





```


## Age difference

The average age difference between females is 300 days in the sub treatment and over 3 years in the Queen treatment 

For the next round 

Queen treatment:
i) Minimize age difference 
ii) Use younger queen and older sub

Sub treatment: 
i) Maximize age difference (should try to have difference of at least 1200 days)
ii) Use one very old sub within the pair 

```{r Summary}

AgeDiff_Summary <- AgeDiff_OlderFocal %>% 

  #SUMMARY
  group_by(Treatment) %>% 
  summarize(Min = min(AgeDiff),
         Max = max(AgeDiff),
         Median = median(AgeDiff),
         Avg = mean(AgeDiff),
         FirstQuartile = quantile(AgeDiff, probs = 0.25),
         ThirdQuartile = quantile(AgeDiff, probs = 0.75)) %>% 
  ungroup()
View(AgeDiff_Summary)


```


```{r Plot}

ggplot(AgeDiff_OlderFocal,
       aes(x=Treatment,y=AgeDiff/365)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col=BS_Original)) +

  theme_classic()

```

#Eviction

Eviction occurred in all but one group from the sub treatment (DevilsPeak, DOS = 18/07/2022) and in all but two group from the queen treatment (Tusker, DOS = 18/01/2022; WicklowWolf = 02/03/2023).

It is worth noticing (see later plots) that groups where there is no eviction are characterized by relatively larger BM and Age difference 

```{r No eviction}

#Groups without eviction
View(DC_Info_F %>% 
       filter(EvictionStatus == "InGroup"))

```

#Relationship BM and Age

We had decided to constrain queen (which are also older) to be heavier. Thus in the queen treatment, Age and BM will be confounded. Perhaps, it would be good to add 4 queens that are lighter than sub?

Are age and BM confounded?

At the individual level, it does not seem. But what is most relevant is to have a look at:
i)queen treatment where queens are consistently older but also heavier by design => we would need queen lighter than sub

ii) sub treatment: Are heavier animals consistently older 

```{r Corvif}

```

```{r Plot}

#Correlation by breeding status 
#Points may be pulled by extreme points
ggplot(ClosestWeight_RelevantDateType, aes(x = Age, y = Weight, color = BS_Original)) +
                           geom_point() + 
  geom_smooth(method = "lm")


#Correlation by breeding status and treatment 
#Points may be pulled by extreme points
ggplot(ClosestWeight_RelevantDateType, aes(x = Age, y = Weight, color = PlotCategory)) +
                           geom_point() + 
  geom_smooth(method = "lm")


#Boxplot
ggplot(ClosestWeight_RelevantDateType,
       aes(x=PlotCategory,y=Age/365)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 3, alpha = 0.8, aes(col = Weight)) +

  theme_classic()


```

## Relationship between difference in Age and difference in BM?

```{r Corvif}

```


```{r Plot}

#Correlation by breeding status 
#Points may be pulled by extreme points
ggplot(ClosestWeight_RelevantDateType, aes(x = Age, y = Weight, color = BS_Original)) +
                           geom_point() + 
  geom_smooth(method = "lm")


#Correlation by breeding status and treatment 
#Points may be pulled by extreme points
ggplot(ClosestWeight_RelevantDateType, aes(x = Age, y = Weight, color = PlotCategory)) +
                           geom_point() + 
  geom_smooth(method = "lm")




```



#Relationship BM, Original BS and eviction

In the sub treatment, differences in body-mass are pretty consistent throughout the experiment. 

The heavier sub at isolation evicted the lighter sub in all but 2 groups (8/10).
i) Lighter animals (CUF031) evicted heavier (CUF012) in Trolls
ii) No eviction in Devils peak where DVF061 is >35g heavier than DVF048 

In the Queen treatment, differences in body-mass are pretty consistent throughout the experiment, though variance seems to increase

In contrast to the sub treatment, heavier females are consistently evicting lighter ones. In fact only 4/11 females that were heavier at isolation evicted, including the two sub that were heavier than the queen (Chouffe and BitBurger). 5/11 females, all queens, that were heavier at isolation and pairing (3/5 at eviction) were evicted by the lighter sub. 2/11 groups where the queen was heavier than then sub have had no eviction.  

Overall this highlight a different relationship between BM difference and likelihood of eviction in the Sub and the queen treatment. This is because despite being heavier, queen are more likely to be evicted than sub. Out of the 9 cases where there was eviction, the queen evicted 2x only and was evicted 7 times (2x it was lighter). 4 evicted queens were lighter than the sub at eviction (2 at isolation) whereas 3 were heavier (5 at isolation). That shows that among the 7 queens that were evicted, two did not maintain their BM advantage. 

Overall, it doesn't seem that the animals that evict have been gaining more BM throughout the experiment, relative to the evictor (sometimes the BM difference ecame more positive, sometimes more negative)

It is worth noticing that the three groups where there has been no eviction (Sub: DevilsPeak, DOS = 18/07/2022; Queen: Tusker, DOS = 18/01/2022; WicklowWolf = 02/03/2023) are characterized by the largest group difference (no competition?)

```{r Summary}

#SummaryTable Wide
SummaryTable_BMBS <- EvictorFocal %>% 
   filter(EvictionStatus != "InGroup") %>% 
   group_by(DateType,
            Treatment,
            BS_Original) %>% 
   summarize(Heavier = sum(WeightDiff > 0),
          Lower = sum(WeightDiff <0)) %>% 
   ungroup()
View(SummaryTable_BMBS)
 

#Summary Long format
SummaryTable_BMBS_Long <- SummaryTable_BMBS %>% 
   pivot_longer(cols = Heavier:Lower,names_to = "BM",values_to = "Count")
View(SummaryTable_BMBS_Long)
 

#Plot 
ggplot(SummaryTable_BMBS_Long,
   aes(x = BS_Original, y = Count, fill = BM)) +
  facet_grid(DateType ~ Treatment) +
  geom_col(position = "stack")

```


```{r Details}

#No eviction 
View(EvictorFocal %>% 
       filter( EvictionStatus== "InGroup"))
#WicklowWolf in Q treatment
#Tusker in Q treatment 
#DevilsPeak in Sub treatment


#Lighter sub that evicted heavier sub
View(EvictorFocal %>% 
       filter(Treatment == "Sub",
              EvictionStatus != "Evictee",
              HeavierRef == 2))
View(EvictorFocal)
#1/10 CUF031 evicted CUF012 in Trolls


#Lighter sub at isolation that evicted heavier queen
View(EvictorFocal %>% 
       filter(Treatment == "Queen",
              BS_Original == "Helper",
              EvictionStatus == "Evictor",
              DateType == "Isolation",
              HeavierRef == 2))
#5 sub evicted queens that were lighter 


#Lighter sub at eviction that evicted heavier queen 
View(EvictorFocal %>% 
       filter(Treatment == "Queen",
              BS_Original == "Helper",
              EvictionStatus == "Evictor",
              DateType == "Eviction",
              WeightDiff <= 0))
#Licher
#Black Label 
#Corbeau 

```


##Focal heavier

In the queen treatment 3 evictee (4 until pairing) are heavier and all of these individuals are queens


```{r Plot}

#Heavier as focal 
ggplot(HeavierIsol,
       aes(x=DateType,y=WeightDiff)) + 
  
  facet_wrap(~ Treatment) +
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=EvictionStatus, shape = BS_Original)) +
  #geom_point(size = 2, alpha = 0.7, aes(col=EvictionStatus, shape = BS_Original)) +
  
  geom_line(aes(group = AnimalID), alpha = 0.5) +
  
  geom_hline(yintercept = 0) +

  theme_classic()


```

## Focal evictor

```{r Plot}

#Heavier as focal 
ggplot(EvictorFocal,
       aes(x=DateType,y=WeightDiff)) + 
  
  facet_wrap(~ Treatment) +
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=BS_Original, shape = EvictionStatus)) +
  #geom_point(size = 2, alpha = 0.7, aes(col=EvictionStatus, shape = BS_Original)) +
  
  geom_line(aes(group = AnimalID), alpha = 0.5) +
  
  geom_hline(yintercept = 0) +

  theme_classic()


```

```{r Comparisons}

ggplot(ClosestWeight_RelevantDateType,
       aes(x=EvictionStatus_Plot,y=Weight)) + 
  
  facet_grid(DateType ~ Treatment) +
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=BS_Original, shape = EvictionStatus)) +
  #geom_point(size = 2, alpha = 0.7, aes(col=EvictionStatus, shape = BS_Original)) +
  
  geom_line(aes(group = ExperimentalGroup), alpha = 0.5) +
  
  geom_hline(yintercept = 0) +
  
  ylim(90,200)+

  theme_classic()


```



##For Loop
I can try to replicate body mass of both females in the pair throughout the experiment for each experimental unit.

The figure should show:

Vertical lines:
- Isolation
- Pairing
- Eviction 
- First parturition (of both animals? only one)

LineType:
- Original BS 

Colour:
- Final eviction status

This has been started but not finished. At this stage, I think it is unecessary

```{r DataPrep}

#I will use isolation day as the reference 


#Join DC_Info with weight 
Plot_BM <- DC_Info %>%
  
  #RETAIN FEMALES
  filter(Sex == "F") %>% 
  
  #ADD WEIGHT
  left_join(.,DC_Weight) %>% 
  
  #ARRANGE
  arrange(ExperimentalGroup,
          AnimalID,
          WeightDate) %>%
  
  #ADD WEIGHT - ISOLATION DAY DIFF 
  mutate(Isolation_DayDiff = WeightDate - IsolationDate) %>% 

  #ADD WEIGHT - PAIRING DAY DIFF
  mutate(Pairing_DayDiff = WeightDate - PairingDate) %>% 
  
  #ADD PAIRING DAY DIFF TO PLOT
  mutate(Pairing_DayDiff_ToPlot = case_when(Pairing_DayDiff >= 0 ~ Pairing_DayDiff))

View(Plot_BM)

```


```{r One colony}
unique(Plot_BM$ExperimentalGroup)


#################################################Vertical lines

Pairing <- DC_Info_F %>% 
  filter(ExperimentalGroup == "Trolls") %>%
  mutate(PairingIsolation_DayDiff = PairingDate - IsolationDate) %>% #Could be added in DC_Info 
  pull(PairingIsolation_DayDiff) %>% 
  unique()
Pairing


Eviction <- DC_Info_F %>% 
  filter(ExperimentalGroup == "Trolls") %>%
  mutate(EvictionIsolation_DayDiff = EvictionDate - IsolationDate) %>% #Could be added in DC_Info 
  pull(EvictionIsolation_DayDiff) %>% 
  unique()
Eviction
  


#################################################Plot single group
  
  


ggplot(Plot_BM %>% 
         filter(ExperimentalGroup == "Trolls"), aes(x=Isolation_DayDiff, y=Weight, colour = EvictionStatus)) + 
  
  #ADD POINTS 
  geom_point(size = 1.5) +
  
  #ADD LINE
  geom_line(aes(group = AnimalID, linetype = BS_Original)) +
  
  #ADD VERTICAL LINES 
  geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
  geom_vline(xintercept = Pairing, colour = "blue", linetype = "dashed") +
  geom_vline(xintercept = Eviction, colour = "red", linetype = "dashed") +
  
  #POINT LABLELS
  geom_text(aes(label=Pairing_DayDiff_ToPlot, vjust= -0.5), size = 3) 
  #check_overlap = TRUE
      
 


```

```{r For loop}

```


#Relationship Age, Original BS and eviction 

In the queen treatment, queens are obviously always older than the subordinate they were paired with. Thus when queen evicts (n=2) they are older and when sub evict (n=7) they are younger

In the sub treatment older evicted 7 times and younger evicted 2 times. In 

For future rounds we shall try to find younger sub that are heavier than older sub (while maximizing BM difference? )

```{r Summary}

#This section is not really menaingful 

View(AgeDiff_EvictorFocal)

#SummaryTable Wide
SummaryTable_AgeBS <- AgeDiff_EvictorFocal  %>% 
   filter(EvictionStatus != "InGroup") %>% 
   group_by(Treatment,
            BS_Original) %>% 
   summarize(Older = sum(AgeDiff > 0),
          Younger = sum(AgeDiff <0), 
          Same = sum(AgeDiff == 0)) %>% 
   ungroup()
View(SummaryTable_AgeBS)
 

#Summary Long format
SummaryTable_AgeBS_Long <- SummaryTable_AgeBS %>% 
   pivot_longer(cols = Older:Same,names_to = "Age",values_to = "Count")
View(SummaryTable_AgeBS_Long)
 

#Plot 
ggplot(SummaryTable_AgeBS_Long,
   aes(x = BS_Original, y = Count, fill = Age)) +
  facet_grid(~ Treatment) +
  geom_col(position = "stack")


```

```{r Details}

#Younger sub that evicted older sub 
View(AgeDiff_EvictorFocal %>% 
       filter(Treatment == "Sub",
              AgeDiff <0) %>% 
       left_join(.,BM_EvictorFocal,by=c("AnimalID" = "AnimalID")))
#CUF031 (Trolls), lighter than evictee
#SOF006 (Firestone), heavier than evictee
#MIF016 (DjuDju), heavier than evictee


```

##Older focal

```{r Plot}


#Older as focal 
ggplot(OlderFocal,
       aes(x=Treatment,y=AgeDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=EvictionStatus)) +
  #geom_point(size = 2, alpha = 0.7, aes(col=EvictionStatus, shape = BS_Original)) +

  theme_classic()



```


##Evictor focal

```{r Plot}


#Heavier as focal 
#With InGroup
ggplot(AgeDiff_EvictorFocal,
       aes(x=Treatment,y=AgeDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=BS_Original, shape = EvictionStatus)) +
  
  geom_hline(yintercept = 0) +

  theme_classic()



#Heavier as focal 
#With InGroup
ggplot(AgeDiff_EvictorFocal %>% 
         filter(EvictionStatus != "InGroup"),
       aes(x=Treatment,y=AgeDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=BS_Original, shape = EvictionStatus)) +
  
  geom_hline(yintercept = 0) +

  theme_classic()


```

```{r Comparisons}

```


#Timing of eviction

Relative to pairing 
Relative to Conception 
Relative to Parturition 
When the two females got pregant (Licher and Black Label)