---
title: "Untitled"
output: html_document
date: "2024-07-02"
---

#Aim 

Generate the dataset of hormone concentration for the DC experiment. 



#General

Hormone [] are corrected for urine volume and specific gravity.

The data still need to be linked with the relevant info for modelling



#Package

```{r package}

library(tidyverse)

```


```{r wd}

Dir_DC <- "C:/Users/Philippe/Dropbox/PhD_20150515/Research projects/DMR_HelperBreedingOpp/DC/DC_Analyses"

#Directory of current tbl 
Dir_tbl <- "C:/Users/Philippe/Dropbox/PhD_20150515/Research projects/DMR_Database/tbl_Current"

```


#Get DB

```{r}


#Set wd
setwd(Dir_tbl)

#tbl_Extraction
tbl_Extraction <- read.csv("tbl_Extraction_20240626.csv") %>% 
  mutate(ExtractionDate = dmy(ExtractionDate))
View(tbl_Extraction)

#tbl_SG
tbl_SG <- read.csv("tbl_SG_20240625.csv") %>% 
  mutate(SGDate = ymd(SGDate))


#tbl_MSdata
tbl_MSdata <- read.csv("tbl_MSdata_20240710.csv")
names(tbl_MSdata)

#qry_MShormones 
qry_MShormones <- read.csv("qry_MShormones_20240710.csv")
names(qry_MShormones)

```



#SG summary 

These value are required to perform the correction for SG using the function sg_correction()

```{r}

#Run function sg_summary
#Generate SG_Day
#SampleID
#SG_Pop
#These objects are required to calculate SG correction
SG_Summary <- tbl_SG %>% 
  sg_summary ()

# Unpack the list into the global environment
list2env(SG_Summary , envir = .GlobalEnv) 

```


#Extracted samples

```{r}

DC_Samples <- qry_MShormones %>% 
  distinct(NPACID, 
           SampleID)
View(DC_Samples)
#There are 672 samples 
#includes 9 MF and 9MM 
#654 samples from DC experiment


```


#DC hormones

```{r data}

DC_qry_MShormones <- qry_MShormones %>% 
  filter(BatchID >= 44,
         BatchID <= 50)

```


```{r correction}

DC_Hormones_Corr <- DC_qry_MShormones %>% 
  #ADD CLOSEST SG 
  add_closestSG(df_extraction = tbl_Extraction, df_sg = SG_Day) %>% 
  #APPLY SG CORRECTION TO ALL
  sg_corr(col_conc = MS_Conc, col_sg = SG_Day) %>% 
  
  #APPLY URINE CORRECTION 
  urinevol_corr(df_extraction = tbl_Extraction, col_conc = MS_Conc_SG)

```


```{r DC}

#DC samples for which I have no SG
DC_NoSG <- DC_Hormones_Corr %>% 
  filter(is.na(SG_Day)) %>% 
  distinct(SampleID, NPACID, BatchID)
View(DC_NoSG)
#all 0 and 1 samples
#Indicates that the entry of these samples should be different in tbl_SG or that I had removed 0 and 1 samples from tbl_SG

#NA SampleID 
DC_NoSG <- DC_Hormones_All %>% 
  filter(is.na(SG_Day)) %>% 
  distinct(SampleID, NPACID, BatchID)
View(DC_NoSG)
#Only pooled samples

```


#Subsetting 

```{r }

DC_Hormones_Selected <- DC_Hormones_Corr %>% 
  conc_selection()#Require tbl_MSdata to be in the environment

View(DC_Hormones_Selected %>% 
       filter(Processed == "Yes",
              StdCurve_Range == "Low",
              QTcat == "ND"))
```


#Zero assignement 

I will create 3 datasets 

i) Conservative value: all values that are not Q are assigned 0 

ii) Semi-cons values: All values that are ND and D are assigned 0

iii) non cons values: all processed value == 0 are assigned their NP value 

```{r}

names(DC_Hormones_Selected)

#Conservative []
Conc_C <- DC_Hormones_Selected %>% 
  conc_zeroprocess(col_conc = MS_Conc_SG_U, threshold = "Q")
View(Conc_C)
#5372


#Semi conservative []
Conc_SC <- DC_Hormones_Selected %>% 
  conc_zeroprocess(col_conc = MS_Conc_SG_U, threshold = "D")
View(Conc_SC)
#5372


#Non conservative []
Conc_NC <- DC_Hormones_Selected %>% 
  conc_zeroprocess(col_conc = MS_Conc_SG_U, threshold = "ND")
View(Conc_NC)
#5372

View(Conc_NC %>% 
       filter(is.na(QTcat)))

unique(Conc_NC$QTcat)

#Conc all 
DC_Conc_All <- bind_rows(Conc_C,
                      Conc_SC,
                      Conc_NC) %>% 
  #RELEVEL HORMONES
  mutate(Hormone = fct_relevel(Hormone, "E2", "P4", "A4", "DHEA", "T", "11KT","Col", "Con"))


View(DC_Conc_All)
unique(DC_Conc_All$QTcat)

```


#Data check
Perhaps this can be moved into the different pipeline where they apply? However, easier to apply first here as it is easier for me to assess whether the data check codes are doing what I expect them to. Once yes, they could be moved to full pipelines


##Duplicated 

```{r}

#Are there samples ID that were done more than once and for which one would need to remove a duplicate
DC_Duplicated_SampleID <- Conc_All %>% 
  filter(!SampleID %in% c(0,1)) %>% 
  distinct(SampleID,NPACID) %>% 
  add_count(SampleID) %>% 
  filter(n>1) %>% 
  left_join(., tbl_Extraction)
View(DC_Duplicated_SampleID )

```


##Loss of samples

```{r}

#NB of extracted samples excluding pooled and contrast with how many samples I have per hormones

```


##Saturated samples

```{r}

```


#CSV 

```{r}

#set wd
setwd(Dir_DC)

#write csv
write.csv(DC_Conc_All, "DC_Conc_All_20240814.csv",row.names = FALSE)

```


