---
title: "Untitled"
output: html_document
date: '2023-03-15'
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

#Package

```{r}

library(DHARMa)
library(broom.mixed)
library(tidyverse)

```

#General

i)  Perhaps the difference in BM shoudl be expressed as % of lighter
    individual BM instread as in absolute BM

ii) I guess some bits could be moved to data prep but the aim here is to
    tweak the data to visualize what is going on. Perhaps once it is
    consolidated and also used for models I can move to dataprep

#CSV

```{r}

#DC info
#If brought as csv I need to do all the relabelling and reformatting
#Usually I won't work with the csv, but in case I have it if R crashes
DC_Info_F <- read.csv("DC_Info_F_20240206.csv") %>% 
  
  #REFORMAT DATE
  mutate(BirthDate = ymd(BirthDate),
         IsolationDate = ymd(IsolationDate),
         PairingDate = ymd(PairingDate)) %>%
  

View(DC_Info_F)



#Relevant weight
DC_ClosestWeight <- read.csv("DC_ClosestWeight_20240206.csv")
names()


#Urine info 
#check what info is there
DC_Info_Urine_F <- read.csv("DC_Info_Urine_F_20240206.csv")


```

#Data

The next section could be moved to data prep.

```{r DC}

#Join DC_Info with closest weight
#So far done for female only 
DC_Info_ClosestWeight <- DC_Info_F %>% 
  left_join(., DC_ClosestWeight) %>% 
  filter(WeightDiff_Type == "Before")
View(DC_Info_ClosestWeight)



#Assign a reference for heavier animal at isolation 
HeavierIsolation <- DC_Info_ClosestWeight%>%
  filter(DateType == "Isolation") %>%
  #ADD HEAVIER REF 
  group_by(ExperimentalGroup) %>% 
  arrange(desc(Weight)) %>% 
  mutate(Isolation_HeavierRef = row_number()) %>% 
  ungroup() %>% 
  #ARRANGE
  arrange(ExperimentalGroup, 
          Isolation_HeavierRef) %>% 
  distinct(AnimalID,
           Isolation_HeavierRef)
View(HeavierIsolation)


#Select relevant Date type of weight
ClosestWeight_Milestone <- DC_Info_ClosestWeight %>% 
  
  #RETAIN RELEVANT WEIGHT DATES
  filter(DateType %in% c("Isolation", "Pairing", "Eviction"), 
         WeightDiff_Type == "Before") %>% 
  
  #ADD HEAVIER REF 
  left_join(.,HeavierIsolation) %>% 
  
  #ADD EVICTION STATUS FOR PLOTTING INGROUP ASSIGN EVICTOR AND EVICTEE
  mutate(EvictionStatus_Plot = case_when(EvictionStatus == "InGroup" & Isolation_HeavierRef == 1 ~ "Evictor", 
                                        EvictionStatus == "InGroup" & Isolation_HeavierRef == 2 ~ "Evictee", 
                                        TRUE ~ as.character(EvictionStatus))) %>% 
  
  mutate(EvictionStatus_Plot = fct_relevel(EvictionStatus_Plot, "Evictor", "Evictee")) %>% 
  
  #RELEVEL DATE TYPE
  mutate(DateType = fct_relevel(DateType, "Isolation", "Pairing", "Eviction")) %>% 
  
  #ARRANGE
  #Heavier animal first 
  arrange(ExperimentalUnit,
          DateType,
          desc(Weight))
names(ClosestWeight_Milestone)



###################################################DC 

#Count of weigth per experimental group and Date Type
#Should be = 2
C_WeightDiff_Count <- ClosestWeight_Milestone %>% 
       group_by(ExperimentalGroup, 
                DateType) %>% 
       mutate(n = n())
names(C_WeightDiff_Count)

#Not equal to 2
C_WeightDiff_WrongCount <- C_WeightDiff_Count %>% 
       filter(n !=2)
View(C_WeightDiff_WrongCount)
#All good 2 weights per category

# View(ClosestWeight_Milestone %>% 
#   filter(AnimalID %in% c ("PF009", "DRF015")))

#Same weight
SameWeight <- ClosestWeight_Milestone %>% 
  group_by(ExperimentalGroup,
           DateType) %>% 
  mutate(WeightDiff = Weight - lead(Weight)) %>% 
  filter(WeightDiff == 0)
View(SameWeight)
#No weight difference of 0
#Heavier animals always first 


#Min
#Max
#Avg 
#Median 
#Off day difference for each categor

#Percentage of data that was not collected on the day of isolation, pairing or eviction 

```

Weight diff contains all information from DC_Info_F, with weight
difference. It could be moved to data prep

```{r WeightDiff}

WeightDiff <- ClosestWeight_Milestone %>% 
  
  #ADD PARTNER WEIGHT INFO
  left_join(ClosestWeight_Milestone %>% 
              select(AnimalID, 
                     DateType,
                     Weight) %>% 
              rename(PartnerWeight = Weight), by=c("PartnerID" = "AnimalID", "DateType" = "DateType")) %>% 
  
  #ADD WEIGHT DIFF 
  mutate(WeightDiff = Weight - PartnerWeight) %>% 
  
  #ADD HEAVIER CATEGORY 
  group_by(ExperimentalGroup,
           DateType) %>% 
  mutate(WeightDiff_Cat = case_when(WeightDiff > 0 ~ "Heavier",
                                    WeightDiff == 0 ~ "Same",
                                    WeightDiff < 0 ~ "Lighter"))
View(WeightDiff)

```

```{r Focal}

#Heavier animal as focal 
Heavier <- WeightDiff %>% 
  filter(WeightDiff > 0)
View(Heavier)

#Lighter animal as focal
Lighter <- WeightDiff %>% 
  filter(WeightDiff < 0)

#Remove info of lighter individual at isolation
HeavierIsol <- WeightDiff  %>% 
  filter(Isolation_HeavierRef == 1)
View(HeavierIsol)

#Could add heavier pairing 
#Could add heavier eviction

#Evictor as focal
#InGroup have been assigned a status 
Evictor <- WeightDiff  %>% 
  filter(EvictionStatus_Plot == "Evictor")

#Evictee as focal
#InGroup have been assigned a status 
Evictee <- WeightDiff  %>% 
  filter(EvictionStatus_Plot == "Evictee")

#Older as focal 
Older <- WeightDiff  %>% 
  filter(AgeDiff > 0)

#Younger as focal 
Younger <- WeightDiff  %>% 
  filter(AgeDiff < 0)

```

Using data exploration in the code below, one can create sampling
category. It is useful to add here at the beginning of the code for
subsequent filtering.

*Cat 1: Rapid Conception*

*Cat 2: Rapid Pre-Conception*

*Cat 3: Slow Conception*

*Cat 4: Slow Pre-Conception*

*Cat 5: No eviction*


#Sample size

10x sub treatment 11x queen treatment; 2 queens are lighter and could be
excluded from analyses

```{r Treatment}

SampleSize <- DC_Info %>% 
  group_by(Treatment) %>% 
  summarize(SampleSize = n_distinct(ExperimentalGroup)) %>% 
  ungroup()
View(SampleSize)

```

#Experimental design

##BM absolute

At isolation body-mass and variance in body-mass is greater in the sub
treatment.

For the next round, it would be useful to use heavier BF (\>150-160).
See BM differences section for further info on BM differences.

In the queen treatment, Queen are relatively heavier than NBF, but we
have decided to constrain this by design.

```{r Summary}

names(ClosestWeight_Milestone )

#Without distinction Sub-Queen 
BM_Summary <- ClosestWeight_Milestone %>% 
  group_by(Treatment) %>% 
  summarize(Min = min(Weight),
         Max = max(Weight),
         Median = median(Weight),
         Avg = mean(Weight),
         FirstQuartile = quantile(Weight, probs = 0.25),
         ThirdQuartile = quantile(Weight, probs = 0.75),
         SD = sd(Weight)) %>% 
  ungroup()
View(BM_Summary)

#With Distinction Sub-Queen
BM_Summary_SubQueen <- ClosestWeight_Milestone %>% 
  group_by(Treatment, 
           BS_Original) %>% 
  summarize(Min = min(Weight),
         Max = max(Weight),
         Median = median(Weight),
         Avg = mean(Weight),
         FirstQuartile = quantile(Weight, probs = 0.25),
         ThirdQuartile = quantile(Weight, probs = 0.75)) %>% 
  ungroup()
View(BM_Summary_SubQueen)
         

```

Linear models show no difference in body mass at both isolation and
pairing between treatments

Within the queen treatment, queen tend to be heavier at isolation and
are significantly heavier at pairing than sub

```{r LM}

#At isolation 
#Already moved into analyses (No model validation done yet)
LM_BMIsol <- lm(Weight ~ Treatment, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Isolation"))
summary(LM_BMIsol)


#At pairing
#Already moved into analyses (No model validation done yet)
LM_BMPairing <- lm(lm(Weight ~ Treatment, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Pairing"))) 
summary(LM_BMPairing)


#Are queen heavier than sub from both treatment at isolation
LM_BMIsol_QueenSub <- lm(lm(Weight ~ BS_Original, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Isolation"))) 
summary(LM_BMIsol_QueenSub)


#Are queen heavier than sub from both treatment at pairing
 LM_BMPairing_QueenSub <- lm(lm(Weight ~ BS_Original, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Pairing"))) 
summary(LM_BMPairing_QueenSub)


##Are queen heavier than sub from queen treatment
LM_BMIsol_QueenSub_QT <- lm(lm(Weight ~ BS_Original, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Isolation",
                       Treatment == "Queen"))) 
summary(LM_BMIsol_QueenSub_QT)
#There is a trend for queen to be heavier at isolation
#Despite this they are at a competitive disadvantage


#Are queen heavier than sub from queen treatment 
LM_BMPairing_QueenSub_QT <- lm(lm(Weight ~ BS_Original, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Pairing",
                       Treatment == "Queen"))) 
summary(LM_BMPairing_QueenSub_QT)
#Queen are significantlly heavier at pairing than Sub


#At isolation 
#Already moved into analyses (No model validation done yet)
LM_BMIsol_H <- lm(Weight ~ Treatment, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Isolation",
                       BS_Original != "Breeder"))
summary(LM_BMIsol_H)
#No diff


#At pairing
#Already moved into analyses (No model validation done yet)
LM_BMPairing_H <- lm(lm(Weight ~ Treatment, 
              data = ClosestWeight_Milestone %>% 
                filter(DateType == "Pairing",
                       BS_Original != "Breeder"))) 
summary(LM_BMPairing_H)
#No diff 

```

```{r Plot}

#By treatment at isolation
ggplot(ClosestWeight_Milestone %>% 
         filter(DateType == "Isolation"),
       aes(x=Treatment,y=Weight)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col = BS_Original)) +

  theme_classic()


names(ClosestWeight_Milestone)

#Plot separating sub_Q and Queen 
ggplot(ClosestWeight_Milestone  %>% 
         filter(DateType == "Isolation"),
       aes(x=BS_PlotCategory,y=Weight)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5) +

  theme_classic()

```

##BM Differences

Before the last round, I had recommended:

In the queen treatment: Use queens that are as heavy as possible (\>
160g) with BM difference \> 20g

In the sub treatment: Use Have a few sub with small BM difference (about
10g)

Because at that stage, differences in body mass between the heavier
animals and the lighter animals were greater in the sub treatment and
variance in differences in BM was greater in the sub treatment that in
the queen treatment.

I don't think this was followed, so how do things look like now? Models
suggest that there are no significant differences of delta BM across
treatment, and this is all what matters. But I am not sure how
appropriate the models are

In the queen treatment, queens were heavier than subordinate in all but
two experimental pair: i) Chouffe: NBF was 3 grams heavier ii)
BitBurger: NBF was 8 grams heavier iii) Leffe: NBF was 4g heavier at
isolation, same at pairing, lighter at eviction

One should perhaps do analyses with and without these groups.

```{r Summary}

BMdiff_Summary <- HeavierIsol %>% 
  filter(DateType == "Isolation") %>% 
  group_by(Treatment) %>% 
  summarize(Min = min(WeightDiff),
         Max = max(WeightDiff),
         Median = median(WeightDiff),
         Avg = mean(WeightDiff),
         FirstQuartile = quantile(WeightDiff, probs = 0.25),
         ThirdQuartile = quantile(WeightDiff, probs = 0.75),
         SD = sd(WeightDiff)) %>% 
  ungroup()
View(BMdiff_Summary)

```

```{r Details}

names(HeavierIsol)

#Sub heavier than queen at isolation 
View(HeavierIsol %>% 
       filter(Treatment == "Queen",
              Isolation_HeavierRef == 1, 
              BS_Original == "Helper"))
```

```{r Models}

#At isolation 
LM_BMDiff_Isol <- lm(WeightDiff ~ Treatment, 
              data = WeightDiff %>% 
                filter(DateType == "Isolation",
                       WeightDiff_Cat == "Heavier"))
summary(LM_BMDiff_Isol)
#No significant difference

#At pairing
LM_BMDiff_Pairing <- lm(WeightDiff ~ Treatment, 
              data = WeightDiff %>% 
                filter(DateType == "Pairing",
                       WeightDiff_Cat == "Heavier"))
summary(LM_BMDiff_Pairing)
#No significant difference

```

```{r Plot}

#Heavier as focal 
ggplot(Heavier %>% 
         filter(DateType == "Isolation"),
       aes(x=Treatment,y=WeightDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col=BS_Original)) +

  theme_classic()
#At isolation 3 helpers heavier than queen
#Model suggests the difference is not significant though I have not done model validation on it


```

## Age absolute

Before the last round, I had suggested that

Queen treatment: i) Use younger queen and older sub. That will also
contribute to lower age difference

Sub treatment ii) Use subordinate that are 5.5 years at least.

because before this round, females from the queen treatment are on
average 3 times older than females from the sub treatment. This is due
to queens being much older than sub.This was not taken into account

Q are significantly older than H No difference in age in helpers across
the two treatments

```{r Summary}
names(DC_Info)

#Age summary 
Age_Summary <- DC_Info_F %>% 
  
  #SUMMARY
  group_by(Treatment) %>% 
  summarize(Min = min(Age),
         Max = max(Age),
         Median = median(Age),
         Avg = mean(Age),
         FirstQuartile = quantile(Age, probs = 0.25),
         ThirdQuartile = quantile(Age, probs = 0.75),
         SD = sd(Age)) %>% 
  ungroup()
View(Age_Summary)


#Age summary, separating queen and sub in queen treatment
Age_SubQueen_Summary <- DC_Info_F %>% 
  #AGE AT ISOL
  mutate(Age = IsolationDate - BirthDate) %>% 
  
  #SUMMARY
  group_by(Treatment,
           BS_Original) %>% 
  summarize(Min = min(Age),
         Max = max(Age),
         Median = median(Age),
         Avg = mean(Age),
         FirstQuartile = quantile(Age, probs = 0.25),
         ThirdQuartile = quantile(Age, probs = 0.75),
         SD = sd(Age)) %>% 
  ungroup()
View(Age_SubQueen_Summary)

```

```{r Models}


LM_Age <- lm(as.integer(Age) ~ Treatment, 
              data = DC_Info_F)
summary(LM_Age)
#There is a trend for females to be older in the queen treatment 
#No model validation so it could be that the most appropriate model shows stg different


#Difference in age between Q and helper
LM_Age_ByStatus <- lm(as.integer(Age) ~ BS_Original, 
              data = DC_Info_F)
summary(LM_Age_ByStatus)
#BF are significantly older than helper 

#Difference in Age between sub of each treatment as graph suggest there may be a difference
LM_Age_Helper <- lm(as.integer(Age) ~ Treatment, 
              data = DC_Info_F %>% 
                filter(BS_Original != "Breeder"))
summary(LM_Age_Helper)
#No significant diff

names(DC_Info_F)
unique(DC_Info_F$BS_Original)


```

```{r Plot}

#By treatment
ggplot(DC_Info_F,
       aes(x=Treatment,y=Age)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col = BS_Original)) +

  theme_classic()


#By treatment, separating queen and 
ggplot(DC_Info_F,
       aes(x=Treatment,y=Age)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col = BS_Original)) +

  theme_classic()



#By treatment + separating sub_Q and Queen 
ggplot(DC_Info_F,
       aes(x=BS_PlotCategory,y=Age/365)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5) +

  theme_classic()
#LM suggest no significant diff in the age of sub across treatment







```

## Age difference

For the next round, I had suggested:

Queen treatment: i) Minimize age difference ii) Use younger queen and
older sub

Sub treatment: i) Maximize age difference (should try to have difference
of at least 1200 days) ii) Use one very old sub within the pair

because the average age difference between females is 300 days in the
sub treatment and over 3 years in the Queen treatment. This was not
followed

The consequence is that the age difference between experimental subjects
is significantly higher in the Q than in the Sub treatment

```{r Summary}

AgeDiff_Summary <- Older %>% 

  #SUMMARY
  group_by(Treatment) %>% 
  summarize(Min = min(AgeDiff),
         Max = max(AgeDiff),
         Median = median(AgeDiff),
         Avg = mean(AgeDiff),
         FirstQuartile = quantile(AgeDiff, probs = 0.25),
         ThirdQuartile = quantile(AgeDiff, probs = 0.75),
         SD = sd(AgeDiff)) %>% 
  ungroup()
View(AgeDiff_Summary)


```

```{r Model}

View(DC_Info_F)

LM_AgeDiff <- lm(as.integer(AgeDiff) ~ Treatment, 
              data = DC_Info_F %>% 
                filter(AgeDiff_Cat == "Older"))
summary(LM_AgeDiff)
#There is a super significant difference in Age 

```

```{r Plot}

ggplot(Older,
       aes(x=Treatment,y=AgeDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col=BS_Original)) +

  theme_classic()

```

##Correlation BM and Age Diff

```{r Data}

#Prepare data 
#Center difference in Age, Note that this won't affect the slopes estimates. So it is not absolutely necessary, but makes Treatment ieffect interpretatble
BMDiff_LMdata <- WeightDiff %>% 
  filter(WeightDiff_Cat == "Heavier") %>% 
  group_by(Treatment,
           DateType) %>% 
  mutate(CentredBM = WeightDiff - mean(WeightDiff),
         CentredAgeDiff = AgeDiff - mean(AgeDiff)) %>% 
  ungroup()

```

```{r Model Isolation}

#All data
LM_BMAgeDiff <- lm(WeightDiff ~ CentredAgeDiff * Treatment, 
                   data = BMDiff_LMdata  %>% 
                     filter(DateType == "Isolation"))
summary(LM_BMAgeDiff)
#Nothing significant


#Sub treatment
LM_BMAgeDiff_ST <- lm(WeightDiff ~ CentredAgeDiff, 
                   data = BMDiff_LMdata %>% 
                     filter(DateType == "Isolation",
                            Treatment == "Sub"))
summary(LM_BMAgeDiff_ST)
#No correlation 


#Queen treatment 
LM_BMAgeDiff_QT <- lm(WeightDiff ~ CentredAgeDiff, 
                   data = BMDiff_LMdata %>% 
                     filter(DateType == "Isolation",
                            Treatment == "Queen"))
summary(LM_BMAgeDiff_QT)
#No correlation 

```

```{r Model Pairing}

#All data
LM_BMAgeDiff_P <- lm(WeightDiff ~ CentredAgeDiff * Treatment, 
                   data = BMDiff_LMdata  %>% 
                     filter(DateType == "Pairing"))
summary(LM_BMAgeDiff_P)
#Nothing


#Sub treatment
LM_BMAgeDiff_ST_P <- lm(WeightDiff ~ CentredAgeDiff, 
                   data = BMDiff_LMdata %>% 
                     filter(DateType == "Pairing",
                            Treatment == "Sub"))
summary(LM_BMAgeDiff_ST_P)
#No correlation 


#Queen treatment 
LM_BMAgeDiff_QT_P <- lm(WeightDiff ~ CentredAgeDiff, 
                   data = BMDiff_LMdata %>% 
                     filter(DateType == "Pairing",
                            Treatment == "Queen"))
summary(LM_BMAgeDiff_QT_P)
#Strong correlation 



```

```{r Plot}
#Older as reference 

#Correlation by breeding status
#Though there is no significant effect of breeding status  
ggplot(Older %>% filter(DateType == "Isolation"), aes(x = AgeDiff, y = WeightDiff, color = Treatment)) +
  
  #facet_grid(~DateType) +
  geom_hline(yintercept = 0) +
  
  geom_point(aes(shape = BS_Original)) + 
  
  geom_smooth(method = "lm") +
  
  theme_classic() +
  
  theme(legend.position = "none")

```

#Eviction

Eviction occurred in all but two group from the sub treatment
(DevilsPeak, DOS = 18/07/2022, Lion = 02/03/2023) and in all but one
group from the queen treatment (Tusker, DOS = 18/01/2022).

Co-breeding only occur in Tusker from the queen treatment. Check that it
is the case

It is worth noticing (see later plots) that groups where there is no
eviction are characterized by relatively larger BM and Age difference

## Occurence

```{r No eviction}

#Groups without eviction
View(DC_Info_F %>% 
       filter(EvictionStatus == "InGroup"))
#3 groups without eviction, 1 in queen treatment, 2 in sub treatment
#Group from queen treatment is co-breeding

```

## Eviction delay

```{r Summary}


#Eviction delay by sampling category
EvictionDelay_Summary <- DC_Info %>% 
  left_join(., SamplingCat) %>% 
  group_by(Sampling_Cat) %>% 
  summarize(Min = min(EvictionPairingDayDiff, na.rm = T),
         Max = max(EvictionPairingDayDiff, na.rm = T),
         Median = median(EvictionPairingDayDiff, na.rm = T),
         Avg = mean(EvictionPairingDayDiff, na.rm = T),
         FirstQuartile = quantile(EvictionPairingDayDiff, probs = 0.25, na.rm = T),
         ThirdQuartile = quantile(EvictionPairingDayDiff, probs = 0.75, na.rm = T),
         SD = sd(EvictionPairingDayDiff, na.rm = T))
View(EvictionDelay_Summary)


#Eviction delay by sampling category and treatment
EvictionDelay_Summary <- DC_Info %>% 
  left_join(., SamplingCat) %>% 
  group_by(Treatment, EvictionCategory, Sampling_Cat) %>% 
  summarize(Min = min(EvictionPairingDayDiff, na.rm = T),
         Max = max(EvictionPairingDayDiff, na.rm = T),
         Median = median(EvictionPairingDayDiff, na.rm = T),
         Avg = mean(EvictionPairingDayDiff, na.rm = T),
         FirstQuartile = quantile(EvictionPairingDayDiff, probs = 0.25, na.rm = T),
         ThirdQuartile = quantile(EvictionPairingDayDiff, probs = 0.75, na.rm = T),
         SD = sd(EvictionPairingDayDiff, na.rm = T))
View(EvictionDelay_Summary)



#Isolation delay
#Must be added in DC_Info
# IsolationDelay_Summary <- DC_Info_F %>% 
#   group_by(Treatment) %>% 
#   summarize(Min = min(IsolationPeriod),
#          Max = max(IsolationPeriod),
#          Median = median(IsolationPeriod),
#          Avg = mean(IsolationPeriod),
#          FirstQuartile = quantile(IsolationPeriod, probs = 0.25),
#          ThirdQuartile = quantile(IsolationPeriod, probs = 0.75),
#          SD = sd(IsolationPeriod))
# View(IsolationDelay_Summary)

#Conception delay
# View(DC_Info_Group %>% 
#        select(ExperimentalGroup,
#               Treatment,
#               PairingDate,
#               ConceptionDelay) %>% 
#        arrange(Treatment,
#                ConceptionDelay))

```

16 evictions occured within 21 days (11S, 5 Q) 2 evictions occurred
between 51 and 100 days 1 eviction between 101 and 150 3 eviction after
151

All eviction after 21 days are in the queen treatment

```{r Category Count}

#Count of eviction based on delay between pairing and eviction
Eviction_DelayCat_Count <- DC_Info_F%>% 
  group_by(ExperimentalGroup) %>% 
  slice_head() %>% 
  ungroup() %>% 
  group_by(Treatment) %>% 
  summarize("21" = sum(EvictionPairingDayDiff <= 21, na.rm = TRUE),
            "22_50" = sum(EvictionPairingDayDiff > 21 & EvictionPairingDayDiff <= 50 , na.rm = TRUE),
            "51_100" = sum(EvictionPairingDayDiff > 50 & EvictionPairingDayDiff <= 100 , na.rm = TRUE),
            "101_150" = sum(EvictionPairingDayDiff > 100 & EvictionPairingDayDiff <= 150 , na.rm = TRUE), 
            "151_" = sum(EvictionPairingDayDiff > 150, na.rm = TRUE),
            No_Eviction = sum(is.na(EvictionPairingDayDiff))) %>% 
  ungroup()
View(Eviction_DelayCat_Count)
#All evictions occured within 21 days in the sub treatment 

#All groups where evictions occurred after 21 days are from the queen treatment (n=6).
#In these 6 groups, the queen was always evicted and the sub gave birth on average 104 days after eviction

#It makes sense to create two categories of eviction, Rapid (<= 21 days) and slow (+21 days, in reality always more than 50 days)
#I have implemented this in DC_Info_F at the beginning of the current code

```

###Detailed Category

```{r Data}

#Add sampling cat to DC_Info
DC_Info_F <- DC_Info_F %>% 
  left_join(., SamplingCat)

#Keep relevant data 
SamplingCat_Info <- DC_Info_F %>% 
  select(ExperimentalGroup, 
         AnimalID, 
         BS_Original,
         EvictionStatus,
         Treatment,
         Sampling_Cat, 
         EvictionPairingDayDiff,
         ParturitionPairingDayDiff,
         ParturitionEvictionDayDiff, 
         Eviction_GS) %>% 
  arrange(Treatment, EvictionPairingDayDiff)
View(SamplingCat_Info)

```

```{r Sample size}

#separating by treatment 
SamplingCat_Count <- SamplingCat_Info %>% 
  group_by(ExperimentalGroup) %>% 
  filter(EvictionStatus == "Evictor" | is.na(EvictionStatus)) %>%
  slice_head() %>% 
  ungroup() %>% 
  group_by(Treatment, Sampling_Cat) %>% 
  summarize(Count = n(), 
            Min = min(ParturitionEvictionDayDiff, na.rm = TRUE),
            Max = max(ParturitionEvictionDayDiff, na.rm = TRUE),
            Median = median(ParturitionEvictionDayDiff, na.rm = TRUE),
            Avg = mean(ParturitionEvictionDayDiff, na.rm = TRUE),
            FirstQuartile = quantile(ParturitionEvictionDayDiff, probs = 0.25, na.rm = TRUE),
            ThirdQuartile = quantile(ParturitionEvictionDayDiff, probs = 0.75, na.rm = TRUE),
            SD = sd(ParturitionEvictionDayDiff, na.rm = TRUE)
            ) %>% 
  ungroup()
View(SamplingCat_Count)

#not separating by treatment
SamplingCat_Count <- SamplingCat_Info %>% 
  group_by(ExperimentalGroup) %>% 
  filter(EvictionStatus == "Evictor" | is.na(EvictionStatus)) %>%
  slice_head() %>% 
  ungroup() %>% 
  group_by(Sampling_Cat) %>% 
  summarize(Count = n(), 
            Min = min(ParturitionEvictionDayDiff, na.rm = TRUE),
            Max = max(ParturitionEvictionDayDiff, na.rm = TRUE),
            Median = median(ParturitionEvictionDayDiff, na.rm = TRUE),
            Avg = mean(ParturitionEvictionDayDiff, na.rm = TRUE),
            FirstQuartile = quantile(ParturitionEvictionDayDiff, probs = 0.25, na.rm = TRUE),
            ThirdQuartile = quantile(ParturitionEvictionDayDiff, probs = 0.75, na.rm = TRUE),
            SD = sd(ParturitionEvictionDayDiff, na.rm = TRUE)
            ) %>% 
  ungroup()
View(SamplingCat_Count)




```

There are 12 groups where the evictor evicted within 21 days of pairing
and around the time it conceived 9x in Sub treatment 3x in Queen
treatment (2x queen, 1x sub evictor).

Question? i) Had the evictee activated their reproductive axis?

```{r Rapid Conception}

#Group
RapidConc <- SamplingCat_Info %>% 
  filter(Sampling_Cat == "Rapid_Conc")
View(RapidConc)

View(RapidConc %>% 
       filter(Treatment == "Queen"))



```

There are 3 groups where evictor evicteds shortly after eviction and
before their first successful gestation - 1X Sub (Darling Brew, 116
days). - 2X Queen treatment, evictor were sub in both cases (Chouffe -
140 days , BitBurger - 132 days).

Suggest no activation (Darling Brew?) prior to eviction or 1 luteal
phase (Chouffe, BitBurger)

Question? i) Had the evictor activated their reproductive axis? or did
they activate AFTER eviction when they succesfully conceived for the
first time. ii) Had the evictee activated their reproductive axis?

```{r Rapid pre-first}

RapidPre <- SamplingCat_Info %>% 
  filter(Sampling_Cat == "Rapid_PreFirst" | ExperimentalGroup == "Firestone")
View(RapidPre)

View(DC_Info_F)


```

Rapid eviction but absence of parturition

Firestone evictor died while giving birth 200 days post pairing. Thus
should really be put in Cat 2

```{r Rapid no parturition}

RapidNone <- SamplingCat_Info %>% 
  filter(Sampling_Cat == "Rapid_None")
View(RapidNone)

```

2 queen treatment where the sub evicted the queen preg of their first
litter long after pairing and around the time they conceived (Licher -
94 days, and Black label - 90 days pre-part).

Question? i) Had the evictee activated their reproductive axis?

```{r Slow conception}

SlowConc <- SamplingCat_Info %>% 
  filter(Sampling_Cat == "Slow_Conc")
View(SlowConc)

```

2x queen treatment where the sub evicted the queen long after pairing
and before they got pregnant (Guinness - 207 days , Corbeau - 129 days
prepart). In one case the queen was lactating.

```{r Slow pre-first}

SlowPre <- SamplingCat_Info %>% 
  filter(Sampling_Cat == "Slow_PreFirst")
View(SlowPre)

```

1x queen treatment (Wicklowolf) where the sub evicted the queen long
after pairing and did not give birth after. However, eviction occurred
on the 12th August 2023 and the evictor is likely to get pregnant soon
and the female to consequently change sampling category.

```{r Slow no eviction}

SlowNone <- SamplingCat_Info %>% 
  filter(Sampling_Cat == "Slow_None")
View(SlowNone)

View(DC_Info_F)

```

There are 3 groups where there was no eviction

2x sub (Devils Peak, Lion). 1x Q (Tusker)

Lion and Tusker have co-breeding. Lion is super recent and thus an
eviction is quite possible, which would make the group change sampling
category

In DevilsP, the 2 females bred 1x. But DVF061 did so after DVF048 died.
Evidence of suppression? self restraint?

```{r None}

None <- SamplingCat_Info %>% 
  filter(Sampling_Cat == "NoEviction")
View(None)

View(Litter_Info %>% 
       filter(AnimalID %in% c("DVF048","DVF061"))),
              ConceptionColony == "Licher"))




```

In cases where queens were evicted after a long time, how quickly did
they activate their reproductive axis

3 queens got pregnant immediately after pairing

3 queens got pregnant longer after pairing

```{r}


Queens_PartNoEvict <- SamplingCat_Info %>% 
  filter(Sampling_Cat %in% c("Slow_Conc", 
                             "Slow_PreFirst", 
                             "Slow_None"),
         BS_Original == "Breeder") %>% 
  
  #ADD PARTURITION DATE
  left_join(., DC_Info_F %>% 
              select(AnimalID, 
                     ConceptionPairingDayDiff))
View(Queens_PartNoEvict)

View(DC_Info_F)

View(Litter_Info)


```

What are the females that activated based their reproductive axis based
on LH but did not evict?

The list may grow once we have the results of hormone analyses

This can be used to ask whether eviction is associated with activation
more than expected by chance.

```{r Activation no eviction}

Activ_NoEviction <- DC_Info_F %>% 
  filter(ExperimentalGroup %in% c("Tusker", "Lion") | #COBREEDING LION GAVE BIRTH 7TH NOV
           AnimalID %in% c("DVF048") | #DEVILS SINGLE BREED (second female conceived after death of DVF048)
           Sampling_Cat %in% c("Slow_Conc","Slow_Pre") & BS_Original == "Breeder") | #BREEDER EVICTED AFTER CONCEIVED 
           ExperimentalGroup == "WickloWolf" & BS_Original == "Breeder")

```

##Model differences in eviction delay

```{r Model function}


#Lm 
evictiondelay_lm <- function(df) {
  glmmTMB( EvictionPairingDayDiff ~ Treatment, data = df)
}


#Poisson
evictiondelay_poiss <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, family = poisson, data = df)
}

#Generalized poisson
evictiondelay_genpoiss <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, family = genpois, data = df)
}
#Not tried yet

#Gamma models
evictiondelay_gamma <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, family = "Gamma", data = df)
}

#Gamma models
evictiondelay_gammalog <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, family = Gamma(link="log"), data = df)
}

#Not tried yet
#Negative binomial 1
evictiondelay_nb1 <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, family = nbinom1, data = df)
}

#Negative binomial 2
evictiondelay_nb2 <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, family = nbinom2, data = df)
}

evictiondelay_tweedie <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, data = df, family = "tweedie")
}

#Does not work, I ma not sure why. Perhaps because there is no random effect? 
evictiondelay_tweedieD <- function(df) {
  glmmTMB(EvictionPairingDayDiff ~ Treatment, data = df, dispformula = ~Treatment, family = tweedie)
}



```

```{r Model dataset}

#Nested dataset
EvictionDelay_Nested <- DC_Info_Group %>% 
  select(ExperimentalGroup,
         Treatment,
         EvictionPairingDayDiff) %>% 
  mutate(EvictionPairingDayDiff = as.integer(EvictionPairingDayDiff)) %>% 
  nest()
View(EvictionDelay)

```

```{r Run Model}

EvictionDelay_Models_Wide <- EvictionDelay_Nested %>%
  
  #RUN MODEL OVER EACH ROWS
  #How could I automate this in one line of code 
  #To learn
  mutate(LM = map(data, evictiondelay_lm),
         P = map(data, evictiondelay_poiss),
         GP = map(data, evictiondelay_genpoiss),
         G = map(data, evictiondelay_gamma),
         GLog = map(data,evictiondelay_gammalog),
         NB1 = map(data, evictiondelay_nb1),
         NB2 = map(data, evictiondelay_nb2),
         Tw = map(data, evictiondelay_tweedie),
         TwD = map(data, evictiondelay_tweedieD))


#Long format
EvictionDelay_Models <- EvictionDelay_Models_Wide %>% 
  
  pivot_longer(cols = LM:TwD, names_to = "ModelType", values_to = "Model")

View(EvictionDelay_Models)

```

```{r MOdel info}


#Model info 
#Treatment to be used in predict function
pdata <- data.frame(Treatment = c("Sub", "Queen"))


#Put all model info together
EvictionDelay_Models_Info <- EvictionDelay_Models %>%
  
  #MODEL INFO 
  #Returned as list 
  mutate(Info = purrr::map(Model, ~family(.x))) %>% 
  
  #ADD FAMILY
  mutate(Family = purrr::map(Info, ~ pluck(.x$family))) %>% 
  
  #ADD LINK 
  mutate(Link = purrr::map(Info, ~ pluck(.x$link))) %>% 
  
  #ADD LINK INVERSE 
  mutate(LinkInv = purrr::map(Info, ~ pluck(.x$linkinv))) %>% 
  
  #ADD AIC 
  mutate(AIC = purrr::map_dbl(Model,~AIC(.x))) %>% 
  
  #ADD SIMULATED RESIDUALS
  mutate(SimResid = map(Model, ~simulateResiduals(fittedModel = .x, plot = F))) %>% 
  
  # #GGPREDICT 
  # mutate(Effect = map(Model, ~ Effect(mod = .x, term = "Treatment"))) %>% 
  # 
    #ADD MODEL PREDICTION
  mutate(Predict = map(Model, ~ predict(.x, newdata = pdata, type = "link", se.fit = TRUE))) %>% 
  
  #ADD MODEL PREDICTION
  mutate(Predict_R = map(Model, ~ predict(.x, newdata = pdata, type = "response", se.fit = TRUE))) 
View(EvictionDelay_Models_Info)

```

```{r Model output}

#EffectSize
EvictionDelay_ModelOutput_Link <- EvictionDelay_Models_Info %>% 
  
  #ADD COEFF
  mutate(Coeff = map(Model, ~tidy(.x))) %>%
  
  #UNNEST MODEL COEFF 
  unnest(Coeff) %>% 

  #ADD CI
  #The std.error are the std.error of the contrast, not of the predicted values, except for the intercept (because the intercept is the predicted value in relation to which the contrasts are expressed)
  mutate(Lower = estimate - (1.96*std.error),
         Upper = estimate + (1.96*std.error)) %>% 
  
  mutate_if(is.numeric, round, 5) %>% 
  
  #SELECT 
  select(
         ModelType,
         term,
         estimate,
         std.error,
         statistic,
         p.value,
         Lower,
         Upper)
  
View(EvictionDelay_ModelOutput_Link)


```

```{r Best models}
#Based on AIC 
#All 3 give warning 
#would need to ask Jacky what they mena and what shoudl be chosen


#There are 3 models with AIC of 141
#Glog
#G
#Tweedie Dispersion


#GLog 
Model_ValidationPlot_GLog <-  EvictionDelay_Models_Info %>% 
  select(
         ModelType,
         SimResid) %>% 
  
  filter(ModelType == "GLog") %>% 
  
  #PLOT MODEL 
  mutate(ModelPlot = purrr::map(SimResid, ~plot(.x))) 


#Gamma
Model_ValidationPlot_G <-  EvictionDelay_Models_Info %>% 
  select(ModelType,
         SimResid) %>% 
  
  filter(ModelType == "G") %>% 
  
  #PLOT MODEL 
  mutate(ModelPlot = purrr::map(SimResid, ~plot(.x))) 

#Tweedie dispersion 
Model_ValidationPlot_G <-  EvictionDelay_Models_Info %>% 
  select(ModelType,
         SimResid) %>% 
  
  filter(ModelType == "TwD") %>% 
  
  #PLOT MODEL 
  mutate(ModelPlot = purrr::map(SimResid, ~plot(.x))) 


```

```{r Plot}

#Data
EvictionDelay <- DC_Info_Group %>% 
  left_join(.,DC_Info_F %>% 
              filter(EvictionStatus == "Evictor") %>% 
              select(ExperimentalGroup, 
                     BS_Original))

View(EvictionDelay)

#Plot
#Remove group without eviction
ggplot(EvictionDelay %>% 
         filter(!is.na(BS_Original)),
       aes(x=Treatment,y=as.integer(EvictionPairingDayDiff))) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 2.5, aes(col = BS_Original)) +

  theme_classic()

```

###Eviction trigger

Is eviction triggered by activation, pregnancies or parturition of
Evictor? Evictee? Both?

Activation will be determined through hormone analyses and can for now
only be backtracked for animal that successfully gave birth.

Pregnancies can be determined through LH, but hormone analyses could
point detect undetected pregnancies .

4 females that were evicted produced a litter (Licher, Corbeau, Black
Label, Guiness).

Corbeau (129 days) and Guiness (12 days) gave birth before they were
evicted.

Licher (43 days) and Black label (23 days) gave birth after they were
evicted. Thus both were pregnant at the time of eviction

```{r}

names(DC_Info)

#Evicted females that gave birth 
Parturition_Evictee <- DC_Info %>% 
  filter(EvictionStatus == "Evictee" & !is.na(FirstParturitionDate))
View(Parturition_Evictee)

#Evicted female that gave birth before eviction 
Parturition_Evictee_Before <- Parturition_Evictee %>% 
  filter(EvictionDate > FirstParturitionDate)
View(Parturition_Evictee_Before)


#Evicted females that gave birth after eviction
Parturition_Evictee_After <- Parturition_Evictee %>% 
  filter(EvictionDate < FirstParturitionDate)
View(Parturition_Evictee_After)

```

#Relationship BM and Age

We had decided to constrain queen (which are also older) to be heavier.
Thus in the queen treatment, Age and BM will be confounded. Perhaps, it
would be good to add 4 queens that are lighter than sub?

Are age and BM confounded?

##Absolute

At the individual level, it does not seem. But what is most relevant is
to have a look at: i)queen treatment where queens are consistently older
but also heavier by design =\> we would need queen lighter than sub

ii) sub treatment: Are heavier animals consistently older

```{r Corvif}

```

```{r Plot}

#Correlation by breeding status 
#Points may be pulled by extreme points
ggplot(ClosestWeight_Milestone, aes(x = Age, y = Weight, color = BS_Original)) +
                           geom_point() + 
  geom_smooth(method = "lm")


#Correlation by breeding status and treatment 
#Points may be pulled by extreme points
ggplot(ClosestWeight_Milestone, aes(x = Age, y = Weight, color = PlotCategory)) +
                           geom_point() + 
  geom_smooth(method = "lm")


#Boxplot
ggplot(ClosestWeight_Milestone,
       aes(x=PlotCategory,y=Age/365)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.3, height = 0, size = 3, alpha = 0.8, aes(col = Weight)) +

  theme_classic()


```

#Relationship BM, Original BS and eviction

In the sub treatment, differences in body-mass are pretty consistent
throughout the experiment.

The heavier sub at isolation evicted the lighter sub in all but 2 groups
(8/10). i) Lighter animals (CUF031) evicted heavier (CUF012) in Trolls
ii) No eviction in Devils peak where DVF061 is \>35g heavier than DVF048

In the Queen treatment, differences in body-mass are pretty consistent
throughout the experiment, though variance seems to increase

In contrast to the sub treatment, heavier females are consistently
evicting lighter ones. In fact only 4/11 females that were heavier at
isolation evicted, including the two sub that were heavier than the
queen (Chouffe and BitBurger). 5/11 females, all queens, that were
heavier at isolation and pairing (3/5 at eviction) were evicted by the
lighter sub. 2/11 groups where the queen was heavier than then sub have
had no eviction.

Overall this highlight a different relationship between BM difference
and likelihood of eviction in the Sub and the queen treatment. This is
because despite being heavier, queen are more likely to be evicted than
sub. Out of the 9 cases where there was eviction, the queen evicted 2x
only and was evicted 7 times (2x it was lighter). 4 evicted queens were
lighter than the sub at eviction (2 at isolation) whereas 3 were heavier
(5 at isolation). That shows that among the 7 queens that were evicted,
two did not maintain their BM advantage.

Overall, it doesn't seem that the animals that evict have been gaining
more BM throughout the experiment, relative to the evictor (sometimes
the BM difference ecame more positive, sometimes more negative)

It is worth noticing that the three groups where there has been no
eviction (Sub: DevilsPeak, DOS = 18/07/2022; Queen: Tusker, DOS =
18/01/2022; WicklowWolf = 02/03/2023) are characterized by the largest
group difference (no competition?)

```{r Summary}

#SummaryTable Wide
SummaryTable_BMBS <- BM_EvictorFocal %>% 
   filter(EvictionStatus != "InGroup") %>% 
   group_by(DateType,
            Treatment,
            BS_Original) %>% 
   summarize(Heavier = sum(WeightDiff > 0),
          Lower = sum(WeightDiff <0)) %>% 
   ungroup()
View(SummaryTable_BMBS)
 

#Summary Long format
SummaryTable_BMBS_Long <- SummaryTable_BMBS %>% 
   pivot_longer(cols = Heavier:Lower,names_to = "BM",values_to = "Count")
View(SummaryTable_BMBS_Long)
 

#Plot 
ggplot(SummaryTable_BMBS_Long,
   aes(x = BS_Original, y = Count, fill = BM)) +
  facet_grid(DateType ~ Treatment) +
  geom_col(position = "stack")

```

```{r Details}

#No eviction 
View(EvictorFocal %>% 
       filter( EvictionStatus== "InGroup"))
#WicklowWolf in Q treatment
#Tusker in Q treatment 
#DevilsPeak in Sub treatment


#Lighter sub that evicted heavier sub
View(EvictorFocal %>% 
       filter(Treatment == "Sub",
              EvictionStatus != "Evictee",
              HeavierRef == 2))
View(EvictorFocal)
#1/10 CUF031 evicted CUF012 in Trolls


#Lighter sub at isolation that evicted heavier queen
View(EvictorFocal %>% 
       filter(Treatment == "Queen",
              BS_Original == "Helper",
              EvictionStatus == "Evictor",
              DateType == "Isolation",
              HeavierRef == 2))
#5 sub evicted queens that were lighter 


#Lighter sub at eviction that evicted heavier queen 
View(EvictorFocal %>% 
       filter(Treatment == "Queen",
              BS_Original == "Helper",
              EvictionStatus == "Evictor",
              DateType == "Eviction",
              WeightDiff <= 0))
#Licher
#Black Label 
#Corbeau 

```

##Focal heavier

In the queen treatment 3 evictee (4 until pairing) are heavier and all
of these individuals are queens

```{r Plot}

#Heavier as focal 
ggplot(HeavierIsol,
       aes(x=DateType,y=WeightDiff)) + 
  
  facet_wrap(~ Treatment) +
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.2, height = 0, size = 2.5, aes(col=EvictionStatus, shape = BS_Original)) +
  #geom_point(size = 2, alpha = 0.7, aes(col=EvictionStatus, shape = BS_Original)) +
  
  geom_line(aes(group = AnimalID), alpha = 0.5) +
  
  geom_hline(yintercept = 0) +

  theme_classic()


```

## Focal evictor

```{r Plot}

#Heavier as focal 
ggplot(EvictorFocal,
       aes(x=DateType,y=WeightDiff)) + 
  
  facet_wrap(~ Treatment) +
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=BS_Original, shape = EvictionStatus)) +
  #geom_point(size = 2, alpha = 0.7, aes(col=EvictionStatus, shape = BS_Original)) +
  
  geom_line(aes(group = AnimalID), alpha = 0.5) +
  
  geom_hline(yintercept = 0) +

  theme_classic()


```

```{r Comparisons}

ggplot(ClosestWeight_Milestone,
       aes(x=EvictionStatus_Plot,y=Weight)) + 
  
  facet_grid(DateType ~ Treatment) +
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=BS_Original, shape = EvictionStatus)) +
  #geom_point(size = 2, alpha = 0.7, aes(col=EvictionStatus, shape = BS_Original)) +
  
  geom_line(aes(group = ExperimentalGroup), alpha = 0.5) +
  
  geom_hline(yintercept = 0) +
  
  ylim(90,200)+

  theme_classic()


```

##For Loop I can try to replicate body mass of both females in the pair
throughout the experiment for each experimental unit. It will be useful
to see which of the body-mass are asscoiated with pregnancies (this
would affect the difference in body mass between the two individuals)

The figure should show:

Vertical lines: - Isolation - Pairing - Eviction - First parturition (of
both animals? only one)

LineType: - Original BS

Colour: - Final eviction status

This has been started but not finished. At this stage, I think it is
unecessary

```{r DataPrep}

#I will use isolation day as the reference 


#Join DC_Info with weight 
Plot_BM <- DC_Info %>%
  
  #RETAIN FEMALES
  filter(Sex == "F") %>% 
  
  #ADD WEIGHT
  left_join(.,DC_Weight) %>% 
  
  #ARRANGE
  arrange(ExperimentalGroup,
          AnimalID,
          WeightDate) %>%
  
  #ADD WEIGHT - ISOLATION DAY DIFF 
  mutate(Isolation_DayDiff = WeightDate - IsolationDate) %>% 

  #ADD WEIGHT - PAIRING DAY DIFF
  mutate(Pairing_DayDiff = WeightDate - PairingDate) %>% 
  
  #ADD PAIRING DAY DIFF TO PLOT
  mutate(Pairing_DayDiff_ToPlot = case_when(Pairing_DayDiff >= 0 ~ Pairing_DayDiff))

View(Plot_BM)

```

```{r One colony}
unique(Plot_BM$ExperimentalGroup)


#################################################Vertical lines

Pairing <- DC_Info_F %>% 
  filter(ExperimentalGroup == "Trolls") %>%
  mutate(PairingIsolation_DayDiff = PairingDate - IsolationDate) %>% #Could be added in DC_Info 
  pull(PairingIsolation_DayDiff) %>% 
  unique()
Pairing


Eviction <- DC_Info_F %>% 
  filter(ExperimentalGroup == "Trolls") %>%
  mutate(EvictionIsolation_DayDiff = EvictionDate - IsolationDate) %>% #Could be added in DC_Info 
  pull(EvictionIsolation_DayDiff) %>% 
  unique()
Eviction
  


#################################################Plot single group
  
  


ggplot(Plot_BM %>% 
         filter(ExperimentalGroup == "Trolls"), aes(x=Isolation_DayDiff, y=Weight, colour = EvictionStatus)) + 
  
  #ADD POINTS 
  geom_point(size = 1.5) +
  
  #ADD LINE
  geom_line(aes(group = AnimalID, linetype = BS_Original)) +
  
  #ADD VERTICAL LINES 
  geom_vline(xintercept = 0, colour = "black", linetype = "dashed") +
  geom_vline(xintercept = Pairing, colour = "blue", linetype = "dashed") +
  geom_vline(xintercept = Eviction, colour = "red", linetype = "dashed") +
  
  #POINT LABLELS
  geom_text(aes(label=Pairing_DayDiff_ToPlot, vjust= -0.5), size = 3) 
  #check_overlap = TRUE
      
 


```

```{r For loop}

```

#Relationship Age, Original BS and eviction

In the queen treatment, queens are obviously always older than the
subordinate they were paired with. Thus when queen evicts (n=2) they are
older and when sub evict (n=7) they are younger

In the sub treatment older evicted 7 times and younger evicted 2 times.
In

For future rounds we shall try to find younger sub that are heavier than
older sub (while maximizing BM difference? )

```{r Summary}

#This section is not really menaingful 

View(AgeDiff_EvictorFocal)

#SummaryTable Wide
SummaryTable_AgeBS <- AgeDiff_EvictorFocal  %>% 
   filter(EvictionStatus != "InGroup") %>% 
   group_by(Treatment,
            BS_Original) %>% 
   summarize(Older = sum(AgeDiff > 0),
          Younger = sum(AgeDiff <0), 
          Same = sum(AgeDiff == 0)) %>% 
   ungroup()
View(SummaryTable_AgeBS)
 

#Summary Long format
SummaryTable_AgeBS_Long <- SummaryTable_AgeBS %>% 
   pivot_longer(cols = Older:Same,names_to = "Age",values_to = "Count")
View(SummaryTable_AgeBS_Long)
 

#Plot 
ggplot(SummaryTable_AgeBS_Long,
   aes(x = BS_Original, y = Count, fill = Age)) +
  facet_grid(~ Treatment) +
  geom_col(position = "stack")


```

```{r Details}

#Younger sub that evicted older sub 
View(AgeDiff_EvictorFocal %>% 
       filter(Treatment == "Sub",
              AgeDiff <0) %>% 
       left_join(.,BM_EvictorFocal,by=c("AnimalID" = "AnimalID")))
#CUF031 (Trolls), lighter than evictee
#SOF006 (Firestone), heavier than evictee
#MIF016 (DjuDju), heavier than evictee


```

##Older focal

```{r Plot}


#Older as focal 
ggplot(OlderFocal,
       aes(x=Treatment,y=AgeDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=EvictionStatus)) +
  #geom_point(size = 2, alpha = 0.7, aes(col=EvictionStatus, shape = BS_Original)) +

  theme_classic()



```

##Evictor focal

```{r Plot}


#Heavier as focal 
#With InGroup
ggplot(AgeDiff_EvictorFocal,
       aes(x=Treatment,y=AgeDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=BS_Original, shape = EvictionStatus)) +
  
  geom_hline(yintercept = 0) +

  theme_classic()



#Heavier as focal 
#With InGroup
ggplot(AgeDiff_EvictorFocal %>% 
         filter(EvictionStatus != "InGroup"),
       aes(x=Treatment,y=AgeDiff)) + 
  
  #ADD BOXPLOT
  geom_boxplot(outlier.shape = NA) +
  
  #ADD POINTS 
  geom_jitter(width = 0.1, height = 0, size = 2.5, aes(col=BS_Original, shape = EvictionStatus)) +
  
  geom_hline(yintercept = 0) +

  theme_classic()


```

```{r Comparisons}

```

#Timing of eviction

Relative to pairing Relative to Conception Relative to Parturition When
the two females got pregant (Licher and Black Label)

#Taking into account the gestation status of both animals
