---
title: "Untitled"
output: html_document
date: "2024-08-14"
editor_options: 
  chunk_output_type: console
---


```{r Package}

library(tidyverse)

library(officer)
library(patchwork)

```

```{r Directory}


Dir_DC <- "C:/Users/Philippe/Dropbox/PhD_20150515/Research projects/DMR_HelperBreedingOpp/DC/DC_Analyses"

setwd(Dir_DC)

```

```{r Data}

#Group info 
#The Sampling_Cat of Tusker must be changed to slow_Post as the evictor had produced litter before eviction
DC_Info_Group <- read.csv("DC_Info_Group_20240710.csv") %>% 
  mutate(IsolationDate = ymd(IsolationDate),
         PairingDate = ymd(PairingDate),
         EvictionDate = ymd(EvictionDate))
names(DC_Info_Group)


#Individual info 
DC_Info_F <- read.csv("DC_Info_F_20240816.csv") %>% 
  #REFORMAT DATE
  mutate(KingRemovalDate = ymd(KingRemovalDate),
         OriginalGroup_LastParturitionDate = ymd(OriginalGroup_LastParturitionDate),
         IsolationDate = ymd(IsolationDate),
         PairingDate = ymd(PairingDate),
         EvictionDate = ymd(EvictionDate)) %>% 
  #ADD SAMPLING CAT 
  left_join(., DC_Info_Group %>% 
              distinct(ExperimentalGroup,
                       Sampling_Cat)) %>% 
  
  #RELEVEL SAMPLING CAT
  #To be moved to data prep (all releveling should be done there)
  mutate(Sampling_Cat = fct_relevel(Sampling_Cat,"Rapid_Conc", "Rapid_PreFirst", "Slow_PostFirst","Slow_Conc", "Slow_PreFirst", "Slow_None", "NoEviction")) %>% 
  relocate(Sampling_Cat) %>% 
  
  #ADD QUEEN CAT 
    #ADD A COLUMN THAT CAN DISTINGUISH Q EE AND OR
  mutate(QueenType = case_when(Treatment == "Queen" & BS_Original == "Breeder" & EvictionStatus == "Evictor" ~ "QOR",
                               Treatment == "Queen" & BS_Original == "Helper" & EvictionStatus == "Evictee" ~ "QOR",
                               Treatment == "Queen" & BS_Original == "Breeder" & EvictionStatus == "Evictee" ~ "QEE",
                               Treatment == "Queen" & BS_Original == "Helper" & EvictionStatus == "Evictor" ~ "QEE")) %>% 
  mutate(QueenType = fct_relevel(QueenType, "QOR", "QEE")) %>%
  
  #CORRECT EXPERIMENTAL GROUP
  #Must be corrected in DataPrep 
  arrange(PairingDate, ExperimentalGroup) %>% 
  mutate(ExperimentalUnit = match(ExperimentalGroup,
                                  unique(ExperimentalGroup))) %>% 
  #ARRANGE 
  arrange(Sampling_Cat,
          ExperimentalGroup,
          EvictionStatus)


#Urine info 
#check what info is there
DC_Info_Urine_F <- read.csv("DC_Info_Urine_F_20240816.csv") %>% 
  rename(SampleID = UrineNumber)
names(DC_Info_Urine_F)


#Hormone concentration 
#write csv
DC_Conc_All <-read.csv("DC_Conc_All_20240814.csv")

names(DC_Info_Urine_F)
View(Data_ToPlot  %>% 
       distinct(QTcat))

#Hormone Info to plot 
# I will use non-conservative value
# Remove sample that have not been analysed
Data_ToPlot <- 
  
  #DC_URINE INFO 
  DC_Info_Urine_F %>%
  select(-ExperimentalUnit) %>% 
  
  #JOIN CONC
  inner_join(., DC_Conc_All) %>%
  
  #ADD RELEVANT DC_INFO_F
  left_join(DC_Info_F %>% 
              distinct(ExperimentalGroup,
                       OriginalGroup,
                     EvictionPairingDayDiff,
                     ExperimentalUnit,
                     LastOrGroupPartIsol_DayDiff,
                     QueenType)) %>% 
  
  #ONLY RETAIN NON-CONS VALUES FOR PLOTTING
  filter(ConcType == "NC") %>% 
  
  #RELEVEL QTCAT
  mutate(QTcat = fct_relevel(QTcat, "ND", "D", "Q")) %>% 
  
  
  # RELEVEL HORMONES
  mutate(Hormone = fct_relevel(Hormone, "E2", "P4", "A4", "DHEA", "T", "11KT", "Col", "Con")) %>% 
  
  #RELEVEL TREATMENT 
  mutate(Treatment = fct_relevel(Treatment, "Sub", "Queen")) %>% 
  
  #RELEVEL SAMPLING CAT
  mutate(Sampling_Cat = fct_relevel(Sampling_Cat,"Rapid_Conc", "Rapid_PreFirst", "Slow_PostFirst","Slow_Conc", "Slow_PreFirst", "Slow_None", "NoEviction")) %>% 
  
  #ADD HORMONE GROUP
  mutate(HormoneGroup = case_when(Hormone %in% c("E2", "P4") ~ "E",
                                  Hormone %in% c("A4", "DHEA") ~ "W",
                                  Hormone %in% c("T", "11KT") ~ "A",
                                  Hormone %in% c("Col", "Con") ~ "GC")) %>%
  mutate(HormoneGroup = fct_relevel(HormoneGroup,"E", "W","A","GC")) %>%
  
  #SELECT COLUMNS 
  select(Sampling_Cat,
         ExperimentalGroup,
         OriginalGroup,
         ExperimentalUnit,
         Treatment,
         AnimalID,
         BS_Original,
         QueenType,
         EvictionStatus,
         LastOrGroupPartIsol_DayDiff,
         UrineIsol_DayDiff,
         UrinePairing_DayDiff,
         UrineEviction_DayDiff,
         HormoneGroup,
         Hormone,
         ConcType,
         QTcat,
         Conc)

str(Data_ToPlot)
Data_ToPlot$Conc

# prevent scientific notations in case
options(scipen = 999)

```



#Til Isolation

##Single Group - Single Hormone - For Trial 

```{r graph settings}


#eviction status 
#Colour
Col_EvStatus <- setNames(c('grey', 'black', 'black'), c("Evictee","InGroup","Evictor"))

#BS_Original
#Helper get a joined line, breeder a two dashed line 
L_BS <- setNames(c('dashed', 'solid'), c("Breeder","Helper"))

#QTcat
Col_QTcat <- setNames(c('white', 'grey', 'black'), c("ND","D","Q"))


```


```{r Data}

#Subset the data 
ToPlot <- Data_ToPlot %>% 
  filter(UrinePairing_DayDiff <= 0) %>% 
  
  #ARRANGE
  #To match what is needed for graph
  arrange(Treatment, 
          Sampling_Cat,
          QueenType,
          ExperimentalUnit)
names(ToPlot)


#KING REMOVAL INFO 
#relative to isolation
KingRemov <- DC_Info_F %>% 
  mutate(KingRemoval = as.numeric(KingRemovalDate - IsolationDate)) %>% 
  distinct(ExperimentalGroup,
           KingRemoval) %>% 
  filter(ExperimentalGroup == "GROUP") %>% 
  pull(KingRemoval)


#LAST PARTURITION INFO
#Relative to isolation
LastPart <- DC_Info_F %>% 
  mutate(LastParturition = as.numeric(LastOrGroupPartIsol_DayDiff)) %>% 
  #RETAIN KING REMOVAL DATE OR WITHIN 100 days
  filter(LastParturition > -100) %>%
  #DISTINCT
  distinct(ExperimentalGroup,
         LastParturition) %>% 
  filter(ExperimentalGroup == "GROUP") %>% 
  pull(LastParturition)


#PAIRING INFO
#Relative to isolation
Pairing <- DC_Info_Group %>% 
  mutate(Pairing = as.numeric(PairingDate - IsolationDate)) %>% 
  select(ExperimentalGroup,
         Pairing) %>% 
  filter(ExperimentalGroup == "GROUP") %>% 
  pull(Pairing)


#TITLE INFO
Info <- DC_Info_F %>%
    filter(ExperimentalGroup == "GROUP") %>%
    distinct(Sampling_Cat, ExperimentalGroup, OriginalGroup,Treatment, ExperimentalUnit, LastOrGroupPartIsol_DayDiff)


```


```{r Plot }

p <- ggplot(ToPlot %>% 
              filter(ExperimentalGroup == "Asahi", Hormone == "E2"), 
            aes(x = UrineIsol_DayDiff, y = Conc, group = AnimalID, 
                linetype = BS_Original, fill = QTcat)) +
  
  # ADD LINE
  geom_line(size = 1, aes(color = EvictionStatus)) +
  
  # ADD POINTS with shapes for each AnimalID and ensure correct fill and color in the legend
  geom_point(size = 3, aes(shape = AnimalID), color = "black") +
  
  # SET COLORS FOR EVICTION STATUS (LINE COLORS)
  scale_color_manual(values = Col_EvStatus) +
  
  # SET LINE TYPE FOR BS_ORIGINAL
  scale_linetype_manual(values = L_BS) +
  
  # SET COLORS FOR QTcat (POINT FILL COLORS)
  scale_fill_manual(values = Col_QTcat) +
  
  # MANUALLY SET SHAPES FOR EACH AnimalID
  scale_shape_manual(values = c(21, 24)) +
  
  # CUSTOM LEGEND TITLES
  labs(shape = "AnimalID", fill = "QTcat", color = "Eviction Status") +
  
  # OVERRIDE POINT LEGEND TO SHOW THE CORRECT COLORS
  guides(
    fill = guide_legend(override.aes = list(shape = 21, color = "black")),
    color = guide_legend(order = 1),
    linetype = guide_legend(order = 2),
    shape = guide_legend(order = 3)
  ) +
  
  # MINIMAL THEME
  theme_minimal()+
  
  #REMOVE LEGEND FROM INDIVIDUAL GRAPH
  theme(legend.position = "none") 

#ADD VLINE KING REMOVAL
#RED
if(length(KingRemov) != 0){
    #SET NEW MIN X AXIS 
    new_min_x <- min(KingRemov) - 2  # Adjust to start before the marker
  p <- p +
    xlim(c(new_min_x, NA))+
    geom_vline(xintercept = KingRemov, colour = "red", linetype = "dashed", size = 1)}


#ADD VLINE LAST PARTURITION
#BLUE
#The selection of parturition to be shown as been made in the filter
if(length(LastPart) != 0){
  #SET NEW MIN X AXIS 
  new_min_x <- min(new_min_x, min(LastPart) - 2)  # Adjust to start before the marker
  p <- p +
    xlim(c(new_min_x, NA))+
    geom_vline(xintercept = LastPart, colour = "blue", linetype = "dashed", size = 1)}


  #ADD VLINE PAIRING
if(length(Pairing) != 0){
  p <- p +
    geom_vline(xintercept = Pairing, colour = "Brown", linetype = "dashed", size = 1)}



# Print the plot
print(p)

```


##Single Group - All Hormone - For Trial

Here I first create several pptx, the solution below for all group is better and I can adjust the code below in case

```{r for loop 1 group all hormones}


#CREATE A LIST 
List <- vector(mode = "list")


#Open power point 
ppt_E <-
  # Load template
  read_pptx()

ppt_W <-
  # Load template
  read_pptx()

ppt_A <-
  # Load template
  read_pptx()

ppt_GC <-
  # Load template
  read_pptx()


#INFO FOR TITLE
Info <- DC_Info_F %>%
    filter(ExperimentalGroup == "Trolls") %>%
    distinct(Sampling_Cat, ExperimentalGroup, Treatment, ExperimentalUnit)
  

for(j in (1:length(Hormones_ToPlot))) {
    
p <- ggplot(ToPlot %>% 
              filter(ExperimentalGroup == "Trolls", Hormone == Hormones_ToPlot[j]), 
            aes(x = UrineIsol_DayDiff, y = Conc, group = AnimalID, 
                linetype = BS_Original, fill = QTcat)) +
  
  # ADD LINE
  geom_line(size = 1, aes(color = EvictionStatus)) +
  
  # ADD POINTS with shapes for each AnimalID and ensure correct fill and color in the legend
  geom_point(size = 3, aes(shape = AnimalID), color = "black") +
  
  # SET COLORS FOR EVICTION STATUS (LINE COLORS)
  scale_color_manual(values = Col_EvStatus) +
  
  # SET LINE TYPE FOR BS_ORIGINAL
  scale_linetype_manual(values = L_BS) +
  
  # SET COLORS FOR QTcat (POINT FILL COLORS)
  scale_fill_manual(values = Col_QTcat) +
  
  # MANUALLY SET SHAPES FOR EACH AnimalID
  scale_shape_manual(values = c(21, 24)) +
  
  # CUSTOM LEGEND TITLES
  labs(shape = "AnimalID", fill = "QTcat", color = "Eviction Status") +
  
  # OVERRIDE POINT LEGEND TO SHOW THE CORRECT COLORS
  guides(
    fill = guide_legend(override.aes = list(shape = 21, color = "black")),
    color = guide_legend(order = 1),
    linetype = guide_legend(order = 2),
    shape = guide_legend(order = 3)
  ) +
  
    #Y LABELS
    ylab(label = paste(Hormones_ToPlot[j],"conc [ng/ml]", sep = " ")) +
  
  #SET MARGIN TO MINIMUM
  theme(plot.margin = margin(0, 0, 0, 0)) +
        
  # MINIMAL THEME
  theme_minimal()+
  
  #REMOVE LEGEND FROM INDIVIDUAL GRAPH
  theme(legend.position = "none") 

#ADD VLINE KING REMOVAL
#RED
if(length(KingRemov_Plot) != 0){
    #SET NEW MIN X AXIS 
    new_min_x <- min(KingRemov_Plot) - 2  # Adjust to start before the marker
  p <- p +
    xlim(c(new_min_x, NA))+
    geom_vline(xintercept = KingRemov_Plot, colour = "red", linetype = "dashed", size = 1)}


#ADD VLINE LAST PARTURITION
#BLUE
#The selection of parturition to be shown as been made in the filter
if(length(LastPart_Plot) != 0){
  #SET NEW MIN X AXIS 
  new_min_x <- min(new_min_x, min(LastPart_Plot) - 2)  # Adjust to start before the marker
  p <- p +
    xlim(c(new_min_x, NA))+
    geom_vline(xintercept = LastPart_Plot, colour = "blue", linetype = "dashed", size = 1)}


  #ADD VLINE PAIRING
if(length(Pairing_Plot) != 0){
  p <- p +
    geom_vline(xintercept = Pairing_Plot, colour = "Brown", linetype = "dashed", size = 1)}

print(p)

#PLACE FIGURE IN LIST 
List[[j]] <- p

print(p)
    
    
}


  #EXTRACT LEGEND OF FIRST GRAPH
Legend <- cowplot::get_legend(List[[1]] + theme(legend.position = "right"))


#STACK GRAPH VERTICALLY 
Oestrogen <- cowplot::plot_grid(List[[1]], List[[2]], ncol = 1)
W <- cowplot::plot_grid(List[[3]], List[[4]], ncol = 1)
Androgen <- cowplot::plot_grid(List[[5]], List[[6]], ncol = 1)
GC <- cowplot::plot_grid(List[[7]], List[[8]], ncol = 1)

#COMBINE GRAPH AND LEGENDS
Oestrogen_L <- cowplot::plot_grid(Oestrogen, Legend, ncol = 2, rel_widths = c(9, 1))
W_L <- cowplot::plot_grid(W, Legend, ncol = 2, rel_widths = c(9, 1))
Androgen_L <- cowplot::plot_grid(Androgen, Legend, ncol = 2, rel_widths = c(9, 1))
GC_L <- cowplot::plot_grid(GC, Legend, ncol = 2, rel_widths = c(9, 1))

  #DRAW TITLE
Title <- cowplot::ggdraw() + 
  cowplot::draw_label(
    paste(Info$Treatment,":",Info$Sampling_Cat,":",Info$ExperimentalGroup,":",Info$ExperimentalUnit,  sep = ""), 
    fontface = 'bold', 
    size = 12, 
    hjust = 0.5
  )

#COMBINE FINAL GRAPH WITH THE TITLE
Oestrogen_L_T<- cowplot::plot_grid(Title, Oestrogen_L, ncol = 1, rel_heights = c(0.1, 1))
W_L_T<- cowplot::plot_grid(Title, W_L, ncol = 1, rel_heights = c(0.1, 1))
Androgen_L_T<- cowplot::plot_grid(Title, Androgen_L, ncol = 1, rel_heights = c(0.1, 1))
GC_L_T<- cowplot::plot_grid(Title, GC_L, ncol = 1, rel_heights = c(0.1, 1))
  

#CREATE AN EDITABLE PLOT 
  Oestrogen <- rvg::dml(ggobj = Oestrogen_L_T)
  W <- rvg::dml(ggobj = W_L_T)
  Androgen <- rvg::dml(ggobj = Androgen_L_T)
  GC <- rvg::dml(ggobj = GC_L_T)
  


#CREATE POWER POINT
  #E PP
  ppt_E <- ppt_E %>% 
  # ADD SLIDE 
  add_slide(layout = "Title and Content", master = "Office Theme") %>%
  # ADD BOXPLOT
  ph_with(value = Oestrogen,
          location = ph_location(left = 0, top = 0, width = 10, height = 7.5)) %>%
  #PRINT PDF
  print('E_PreP.pptx')

  
  #WEAK ANDROGEN PP
  ppt_W <- ppt_W %>% 
  # ADD SLIDE 
  add_slide(layout = "Title and Content", master = "Office Theme") %>%
  # ADD BOXPLOT
  ph_with(value = Oestrogen,
          location = ph_location(left = 0, top = 0, width = 10, height = 7.5)) %>%
  #PRINT PDF
  print('W_PreP.pptx')

  
  #ANDROGEN PP
  ppt_A <- ppt_A %>% 
  # ADD SLIDE 
  add_slide(layout = "Title and Content", master = "Office Theme") %>%
  # ADD BOXPLOT
  ph_with(value = Oestrogen,
          location = ph_location(left = 0, top = 0, width = 10, height = 7.5)) %>%
  #PRINT PDF
  print('A_PreP.pptx')
  
  #GC PP 
  ppt_GC <- ppt_GC %>% 
  # ADD SLIDE 
  add_slide(layout = "Title and Content", master = "Office Theme") %>%
  # ADD BOXPLOT
  ph_with(value = Oestrogen,
          location = ph_location(left = 0, top = 0, width = 10, height = 7.5)) %>%
  #PRINT PDF
  print('GC_PreP.pptx')





```


##All individuals

Show all individuals graphs in power point 

Vertical line red = King removal 
Vertical blue line = Last parturition 
Vertical brown line = Pairing 

King Removal is shown for all groups from the breeding treatment where the king was removed and also all the sub treatment that were formed from the same original group.

Last parturition is only shown if it occurred within 100 days. The number of days since last parturition is shown in the title as well as the original group


PROBLEM WITH CURRENT CODES

1) I could sort out queen treatment so it shows first groups where queen have evicted, then groups where the queen was evicted. It may help to see some patterns

2) only show QTcat of first graph since the legend is being extracted from it. Is there a way to show all levels even the ones for which there is no data? Alternatively the QTcat can be removed from the legend in p (I think one can selectively remove levels of the legend)



```{r Settings}

#eviction status 
#Colour
Col_EvStatus <- setNames(c('grey', 'black', 'black'), c("Evictee","InGroup","Evictor"))

#BS_Original
#Helper get a joined line, breeder a two dashed line 
L_BS <- setNames(c('dashed', 'solid'), c("Breeder","Helper"))

#QTcat
Col_QTcat <- setNames(c('white', 'grey', 'black'), c("ND","D","Q"))

```


One must arrange the data in a way that suits the graph. 

```{r Data}

#Subset the data 
ToPlot <- Data_ToPlot %>% 
  
  #RETAIN [] FROM BEFORE PAIRING
  filter(UrinePairing_DayDiff <= 0) %>% 
  
  #ARRANGE
  #To match what is needed for graph
  arrange(Treatment, 
          Sampling_Cat,
          ExperimentalUnit)

levels(ToPlot$QTcat)

```


```{r Vector}


#Vector of individuals to loop over
Group_ToPlot <- DC_Info_F %>% 
  #ARRANGE
  arrange(Treatment,Sampling_Cat,) %>%
  #DISTINCT
  distinct(ExperimentalGroup) %>% 
  pull() 


#Vector of hormone group
HormonesGroup_ToPlot <- ToPlot %>%
  #ARRANGE
  arrange(HormoneGroup) %>% 
  #DISTINCT
  distinct(HormoneGroup) %>%
  pull()
  

#Vector of hormones 
Hormones_ToPlot <- ToPlot %>% 
  #ARRANGE
  arrange(Hormone) %>%
  #DISTINCT
  distinct(Hormone) %>% 
  pull()

```


```{r}

#FOR EACH GROUP OF HORMONE 
#I want one ppt
for(h in (1:length(HormonesGroup_ToPlot))) {

#CREATE POWER POINT
ppt <-
  # Load template
  read_pptx()

#VECTOR OF HORMONES TO PLOT 
#would probably be better to have it straight as a vector
Hormones_ToPlot <- ToPlot %>%
  filter(HormoneGroup == HormonesGroup_ToPlot[h]) %>% 
  arrange(Hormone) %>% 
  distinct(Hormone) %>% 
  pull()


#LOOP OVER EACH EXP GROUP
for(i in (1: length(Group_ToPlot))) {
  
#CREATE LIST
List <- vector(mode = "list")

#KING REMOVAL INFO 
#relative to isolation
KingRemov <- DC_Info_F %>% 
  mutate(KingRemoval = as.numeric(KingRemovalDate - IsolationDate)) %>% 
  distinct(ExperimentalGroup,
           KingRemoval) %>% 
  filter(ExperimentalGroup == Group_ToPlot[i]) %>% 
  pull(KingRemoval)


#LAST PARTURITION INFO
#Relative to isolation
LastPart <- DC_Info_F %>% 
  mutate(LastParturition = as.numeric(LastOrGroupPartIsol_DayDiff)) %>% 
  #RETAIN KING REMOVAL DATE OR WITHIN 100 days
  filter(LastParturition > -100) %>%
  #DISTINCT
  distinct(ExperimentalGroup,
         LastParturition) %>% 
  filter(ExperimentalGroup == Group_ToPlot[i]) %>% 
  pull(LastParturition)


#PAIRING INFO
#Relative to isolation
Pairing <- DC_Info_Group %>% 
  mutate(Pairing = as.numeric(PairingDate - IsolationDate)) %>% 
  select(ExperimentalGroup,
         Pairing) %>% 
  filter(ExperimentalGroup == Group_ToPlot[i]) %>% 
  pull(Pairing)


#TITLE INFO
Info <- DC_Info_F %>%
    filter(ExperimentalGroup == Group_ToPlot[i]) %>%
    distinct(Sampling_Cat, ExperimentalGroup, OriginalGroup,Treatment,QueenType, ExperimentalUnit, LastOrGroupPartIsol_DayDiff)


#LOOP OVER EACH HORMONES
for(j in (1:length(Hormones_ToPlot))) {
    
p <- ggplot(ToPlot %>% 
              filter(HormoneGroup == HormonesGroup_ToPlot[h], ExperimentalGroup == Group_ToPlot[i], Hormone == Hormones_ToPlot[j]), 
            aes(x = UrineIsol_DayDiff, y = Conc, group = AnimalID, 
                linetype = BS_Original, fill = QTcat)) +
  
  # ADD LINE
  geom_line(size = 1, aes(color = EvictionStatus)) +
  
  # ADD POINTS with shapes for each AnimalID and ensure correct fill and color in the legend
  geom_point(size = 3, aes(shape = AnimalID), color = "black") +
  
  # SET COLORS FOR EVICTION STATUS (LINE COLORS)
  scale_color_manual(values = Col_EvStatus) +
  
  # SET LINE TYPE FOR BS_ORIGINAL
  scale_linetype_manual(values = L_BS) +
  
  # SET COLORS FOR QTcat (POINT FILL COLORS)
  scale_fill_manual(values = Col_QTcat) +
  
  # MANUALLY SET SHAPES FOR EACH AnimalID
  scale_shape_manual(values = c(21, 24)) +
  
  # CUSTOM LEGEND TITLES
  labs(shape = "AnimalID", fill = "QTcat", color = "Eviction Status") +
  
  # OVERRIDE POINT LEGEND TO SHOW THE CORRECT COLORS
  guides(
    fill = guide_legend(override.aes = list(shape = 21, color = "black")),
    color = guide_legend(order = 1),
    linetype = guide_legend(order = 2),
    shape = guide_legend(order = 3)
  ) +
  
    #Y LABELS
    ylab(label = paste(Hormones_ToPlot[j],"conc [ng/ml]", sep = " ")) +
  
  #SET MARGIN TO MINIMUM
  theme(plot.margin = margin(0, 0, 0, 0)) +
        
  # MINIMAL THEME
  theme_minimal()+
  
  #REMOVE LEGEND FROM INDIVIDUAL GRAPH
  theme(legend.position = "none") 

#ADD VLINE KING REMOVAL
#RED
if(length(KingRemov) != 0){
    #SET NEW MIN X AXIS 
    new_min_x <- min(KingRemov) - 2  # Adjust to start before the marker
  p <- p +
    xlim(c(new_min_x, NA))+
    geom_vline(xintercept = KingRemov, colour = "red", linetype = "dashed", size = 1)}


#ADD VLINE LAST PARTURITION
#BLUE
#The selection of parturition to be shown as been made in the filter
if(length(LastPart) != 0){
  #SET NEW MIN X AXIS 
  new_min_x <- min(new_min_x, min(LastPart) - 2)  # Adjust to start before the marker
  p <- p +
    xlim(c(new_min_x, NA))+
    geom_vline(xintercept = LastPart, colour = "blue", linetype = "dashed", size = 1)}


  #ADD VLINE PAIRING
if(length(Pairing) != 0){
  p <- p +
    geom_vline(xintercept = Pairing, colour = "Brown", linetype = "dashed", size = 1)}

#PLACE FIGURE IN LIST 
List[[j]] <- p
    
    
}


#EXTRACT LEGEND OF FIRST GRAPH
Legend <- cowplot::get_legend(List[[1]] + theme(legend.position = "right"))


#STACK GRAPH VERTICALLY 
Stacked <- cowplot::plot_grid(List[[1]], List[[2]], ncol = 1)


#COMBINE GRAPH AND LEGENDS
Stacked_WithL <- cowplot::plot_grid(Stacked, Legend, ncol = 2, rel_widths = c(9, 1))

#DRAW TITLE
Title <- cowplot::ggdraw() + 
  cowplot::draw_label(
    paste(Info$Treatment,":",Info$Sampling_Cat,":",Info$ExperimentalGroup,":",Info$OriginalGroup,":",Info$QueenType,":",Info$ExperimentalUnit,":",Info$LastOrGroupPartIsol_DayDiff,sep = ""), 
    fontface = 'bold', 
    size = 12, 
    hjust = 0.5
  )

#COMBINE FINAL GRAPH WITH THE TITLE
FinalPlot <- cowplot::plot_grid(Title, Stacked_WithL, ncol = 1, rel_heights = c(0.1, 1))
  
#CREATE AN EDITABLE PLOT 
FinalPlot_Ed <- rvg::dml(ggobj = FinalPlot)

#ADD GRAPH TO PP
ppt <- ppt %>% 
  # ADD SLIDE 
  add_slide(layout = "Title and Content", master = "Office Theme") %>%
  # ADD BOXPLOT
  ph_with(value = FinalPlot_Ed,
          location = ph_location(left = 0, top = 0, width = 10, height = 7.5))
  
}

#PRINT PDF 
ppt <-   ppt %>% 
  print(paste("PrePair_",HormonesGroup_ToPlot[h],".pptx",sep = ""))

}


names(ToPlot)
```














#The next part is to be moved in the sample selection files

Selection of samples to assess whether females ovulate after the removal of the breeding male. 

I should finalize the selection only after I have visualized all profile til pairing

```{r BF ovulation sample}
names(DC_Info_F)
#Distribution of delay between last parturition in original group and isolation 
View(DC_Info_F %>% 
       filter(!is.na(KingRemovalDate)) %>% 
       select(AnimalID, 
              BS_Original,
              ExperimentalGroup, 
              Treatment,
              KingRemovalDate,
              LastOrGroupPartIsol_DayDiff) %>% 
       arrange(desc(LastOrGroupPartIsol_DayDiff)))
#Between 19 and 591 days 


#Retain all samples after last parturition and after removal of king 
BF_Ovulation <- DC_Info_Urine_F %>%
  #ADD DAY DIFF ISOL LAST PARTURITION
  left_join(., DC_Info_F %>% 
              select(AnimalID,
                     LastOrGroupPartIsol_DayDiff)) %>% 
  #RETAIN BREEDER TREATMENT
  filter(BS_Original == "Breeder") %>% 
  #RETAIN SAMPLES AFTER KING REMOVAL 
  filter(UrineKingRemoval_DayDiff > 0) %>%
  #RETAIN SAMPLES AFTER LAST PARTURION 
  filter(UrineLastParturitionOirginalGroup_DayDiff > 0) %>% 
  #RETAIN SAMPLES BEFORE PAIRING
  filter(UrinePairing_DayDiff < 0) %>% 
  #ARRANGE
  arrange(Sampling_Cat,
          desc(LastOrGroupPartIsol_DayDiff),
          ExperimentalGroup) %>% 
  #SELECT 
  select(Sampling_Cat, 
         ExperimentalGroup,
         AnimalID,
         LastOrGroupPartIsol_DayDiff,
         UrineParturition_DayDiff,
         UrineKingRemoval_DayDiff,
         UrineLastParturitionOirginalGroup_DayDiff,
         UrineIsol_DayDiff,
         UrinePairing_DayDiff,
         UrineNumber)

View(BF_Ovulation)

```

