---
title: "Untitled"
output: html_document
date: "2024-02-06"
---

#Package

```{r}

library(tidyverse)

```


#General 

1) In firestone the breeding female ORF005 died when she gave birth (after she had evicted ORF018). 

After this the male DRM006 was used to found Kasteel. This has consequences for sample selection. 

```{r Data}

#DC Info Females
DC_Info_F <- read.csv("DC_Info_F_20240318.csv") %>% 
  mutate(BirthDate = ymd(BirthDate),
         PairingDate = ymd(PairingDate),
         IsolationDate = ymd(IsolationDate),
         DeathDate = ymd(DeathDate),
         LastDate = ymd(LastDate),
         FirstDCConceptionDate = ymd(FirstDCConceptionDate),
         FirstDCParturitionDate = ymd(FirstDCConceptionDate),
         EvictionDate = ymd(EvictionDate))
names(DC_Info_F)



#Urine info 
#DC_Urine_F_20240318.csv
DC_Info_Urine_F <- read.csv("DC_Info_Urine_F_20240318.csv") %>% 
  mutate(EvictionDate = ymd(EvictionDate),
         UrineDate = ymd(UrineDate))
names(DC_Info_Urine_F)



#Sample inventory _Inventory
Inventory <- read.csv("Freezer_Inventory_20240318.csv") %>% 
  mutate(Date = dmy(Date)) %>% 
  filter(!is.na(SampleID))
View(Inventory)
#8133


#Latest inventory 
Inventory_Latest <- Inventory %>% 
  group_by(SampleID) %>% 
  slice_max(Date) %>% 
  ungroup()
View(Inventory_Latest)
#8063


#Are there samples that have 2 eppendorfs? 
Inventory_Duplicates <- Inventory_Latest %>% 
  group_by(SampleID) %>% 
  filter(n() > 1) %>% 
  ungroup() %>% 
  slice_max(Date) %>% 
  arrange(SampleID) %>% 
  #ADD COLLECTION INFO 
  left_join(., Urine_Collected %>% 
              select(UrineNumber,
                     AnimalID,
                     UrineDate,
                     Eppendorfs), by = c("SampleID" = "UrineNumber")) %>% 
  relocate(AnimalID:Eppendorfs)
View(Inventory_Duplicates)
#1 samples have 2 eppendorfs and still must be corrected. 
#I sent a mail about it on the 19/03/2024 to Dave and Channen

names(Urine_Collected)

write.csv(Inventory_Duplicates, "Inventory_Duplicates_20240318.csv",row.names = FALSE)

#How many eppendorfs were collected from these samples
Duplicated  <- Inventory_Duplicates %>% 
  distinct(SampleID) %>% 
  #ADD NB OF EPPENDORFS COLLECTED
  left_join(., Urine_Collected %>% 
              select(UrineNumber,
                     Eppendorfs), by = c("SampleID" = "UrineNumber"))
#Always one, therefore it shold not be possible to have 2 rows for these in the inventory

```


#Sample lag 

Normally female should have been sampled approximately once a week during the experiment. 

SOF001 from Corbeau was not sampled for 46 days 
ORF017 from Wicklow was not sampled for 45 days
VGF002 from Wicklow was not sampled for 34 days 



```{r}

SampleLag <- DC_Info_Urine_F %>%
  filter(UrinePairing_DayDiff >= 0, 
         EvictionStatus == "Evictee" & UrineEviction_DayDiff <= 10 | EvictionStatus %in% c("InGroup", "Evictor")) %>% 
  group_by(AnimalID) %>% 
  mutate(LagUrineDate = lag(UrineDate)) %>% 
  ungroup() %>% 
  mutate(LastSampleDelay = UrineDate - LagUrineDate) %>% 
  filter(!is.na(LastSampleDelay)) %>% 
  arrange(desc(LastSampleDelay))

View(SampleLag)

```


#Question 1: 

Determine differences between BF and NBF when there is no breeding opportunity and determine whether ovulation occurs 

Take 1 sample after two weeks 
Take last 2 samples before pairing 

3 samples per female = 156 samples 


```{r Isolation}
names(DC_Info_Urine_F)

#two weeks 
Isol_2W <- DC_Info_Urine_F %>% 
  filter(UrineIsol_DayDiff >= 14) %>% 
  group_by(AnimalID) %>% 
  slice_min(UrineIsol_DayDiff) %>% 
  ungroup()
View(Isol_2W)
#50 samples all good


#Pre-pairing
#In the worse case I could only get the last sample before pairing
Isol_PrePair <- DC_Info_Urine_F %>% 
  filter(UrinePairing_DayDiff <= 0) %>% 
  group_by(AnimalID) %>% 
  slice_max(UrineIsol_DayDiff, n=2) %>% 
  ungroup()
View(Isol_PrePair)

#Check for duplicates
View(Isol_PrePair %>% 
       group_by(AnimalID) %>% 
       mutate(Count = n_distinct(UrineNumber)) %>% 
       ungroup)
#ERF002 from Leffe has 2 samples on a given day, but one of them must be wrong because they have been collected almost at the same time. Check side label and only take the first and correct 

Sel_Isol <- bind_rows(Isol_2W,
                      Isol_PrePair) %>% 
  mutate(SampleReason = "Isolation")
View(Sel_Isol)
#150 samples

```


```{r Post paring}

#Samples that were collected on the day of eviction
#Have asked the project if they should be considered pre or post eviction
#For now I assume that they are pre-eviction
EvictionSample <- DC_Info_Urine_F %>% 
  filter(UrineEviction_DayDiff == 0)

write.csv(EvictionSample, "EvictionSample_ToCheck_20240215.csv", row.names = FALSE)
#Awaiting answer


#Post pairing samples 
Sel_PostPair <- DC_Info_Urine_F %>% 
  filter(UrinePairing_DayDiff > 0, 
         UrinePairing_DayDiff <= 10, 
         UrineEviction_DayDiff <= 0 | is.na(UrineEviction_DayDiff)) %>% 
  mutate(SampleReason = "PostPair")
  
View(Sel_PostPair)
#149 samples


#Samples pre individuals 
PostPair_Count <- Sel_PostPair %>% 
  group_by(ExperimentalGroup, 
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(PostPair_Count)
#Between 1 and 6 samples per individual 


View(anti_join(DC_Info_F, PostPair_Count))
#The only sample that is missing is from Ashai where eviction occured on day 0

View(DC_Info_F)

```

Pre-Eviction samples not accounted for in post-pairing samples. I have opted for 16 days pre-pairing.

```{r Pre-Eviction }

#Pre-Eviction
Sel_PreEviction <- DC_Info_Urine_F %>%
  #REMOVE SAMPLES ALREADY COUNTED IN POST PAIRING
  #filter(!UrineNumber %in% Sel_PostPair$UrineNumber) %>% 
  #FILTER
  filter(UrinePairing_DayDiff > 0, 
         UrineEviction_DayDiff <= 0,
         UrineEviction_DayDiff >= -16) %>%  # the number used here is mostly important for the slow eviction where sampling was not that frequent. 
  mutate(SampleReason = "PreEviction16")

View(Sel_PreEviction)
#10 days =  32 samples
#12 days = 34 samples
#14 days =  35 samples
#16 days =  42 samples between 2 and 6 samples per individual at the excpetion of SOF001 that has no samples
#18 days =  42 samples
#20 days =  44 samples


PreEviction_Count <- Sel_PreEviction %>% 
  group_by(Sampling_Cat,
           ExperimentalGroup,
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(PreEviction_Count)
#Samples from evictor SOF001 in Corbeau (Slow_Conc) are missing. 
#I suspect that it is because eviction occurred really late. Weirdly there is no samples between 184 and 230 days post pairing


#Ask the project to ask the reason 
SOF001 <- DC_Info_Urine_F %>% 
  filter(AnimalID == "SOF001")
write.csv(SOF001, "SOF001_Urine.csv", row.names = FALSE)


#View the samples gathered for slow eviction 
View(PreEviction %>% 
       filter(Sampling_Cat %in% c("Slow_Conc","Slow_PreFirst","Slow_None")) %>% 
       arrange(ExperimentalGroup, AnimalID))

```

No samples has been collected post-eviction yet so no need remove samples collected before

```{r Post eviction}

#First sample post eviction
PostEviction_1 <- DC_Info_Urine_F %>%
  #FILTER
  filter(UrineEviction_DayDiff > 0) %>% 
  group_by(AnimalID) %>% 
  slice_min(UrineEviction_DayDiff) %>% 
  ungroup() %>% 
  mutate(SampleReason = "PostEviction1")
View(PostEviction_1)
#All samples have been collected within 2 days of eviction 
#However, only 43 females meaning that 7 are missing 

#Animals that lack a post-eviction sample 
PostEviction_MissingID <- DC_Info_F %>% 
  select(ExperimentalGroup, 
         AnimalID, 
         BS_Original,
         EvictionStatus, 
         DeathDate,
         EvictionDate) %>% 
  left_join(., SamplingCat) %>% 
  relocate(Sampling_Cat) %>% 
  anti_join(.,PostEviction_1)
View(PostEviction_MissingID )
#Samples are missing from the 3 females where there has been no eviction 
#VGF002 is missing but it seems because she died on the day of eviction so normal there is no sample


#First sample after 14 days post eviction. I cannot really remember why I used that rational. 
#I think it had to do with when I expected to have last sample of evictor, so the two condition would more or less match
#I could always add samples at a later stage
PostEviction_14 <- DC_Info_Urine_F %>%
  #FILTER
  filter(UrineEviction_DayDiff >= 14) %>% 
  group_by(AnimalID) %>% 
  slice_min(UrineEviction_DayDiff) %>% 
  ungroup() %>% 
  mutate(SampleReason = "PostEviction14")
View(PostEviction_14)
#All samples within 9 days except Darling brew wirth 13 and 15 days 
#42 individuals so one more missing as after 1 day 

Post14_Count <- PostEviction_14 %>% 
  group_by(Sampling_Cat,
           ExperimentalGroup,
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(Post14_Count )


#All post eviction samples
Sel_PostEviction <- bind_rows(PostEviction_1, 
                              PostEviction_14)
View(Sel_PostEviction)

```


#Activation-Pregnancy samples

All samples collected between 100 days and 80 days to determine:

- Reproductive activation of some females
- hormone profile of early gestation. 
- Effect of presence of other female on gestation profile of early gestation


We are only missing sample of one gestation, RSF008 the evictor from Guinness where sampling seem to have been stopped before the first successful conception

```{r First conception}

names(DC_Info_Urine_F)

#Are there evictee that gave birth within 100 days of eviction 
View(DC_Info_F %>% 
  filter(EvictionStatus == "Evictee"))

Sel_FirstConc <- DC_Info_Urine_F %>% 
  #REMOVE BITBURGER QUEEN THAT GOT PREGNANT AFTER EVICTION
  filter(AnimalID != "DRF004") %>% 
  
  #REMOVE SAMPLES POST-PAIRING 
  #I DECIDED TO REMOVE THIS SO I CAN SEE FOR EACH SAMPLE ALL THE REASONS WHY THEY WERE SELECTED 
  #filter(!UrineNumber %in% Sel_PostPair$UrineNumber) %>%

  #REMOVE SAMPLES PRE-EVICTION
  #I DECIDED TO REMOVE THIS SO I CAN SEE FOR EACH SAMPLE ALL THE REASONS WHY THEY WERE SELECTED
  #filter(!UrineNumber %in% Sel_PreEviction$UrineNumber) %>%

  #REMOVE SAMPLES POST-EVICTION
  #I DECIDED TO REMOVE THIS SO I CAN SEE FOR EACH SAMPLE ALL THE REASONS WHY THEY WERE SELECTED
  #filter(!UrineNumber %in% Sel_PostEviction$UrineNumber) %>%

  #RETAIN FIRST LITTER 
  filter(NextLitter_IndCount_Colony == 1) %>%               
  #FILTER SAMPLES WITHIN TIME RANGE NEEDED 
  filter(NextParturition_ParturitionDayDiff >=- 100,
         NextParturition_ParturitionDayDiff <= -80) %>% 
  mutate(SampleReason = "FirstConc")
View(Sel_FirstConc)
#219 samples but that does not take into account samples already selected previously
#146 if samples already selected are removed


#Count of samples
Sel_FirstConc_Count <- Sel_FirstConc %>% 
  group_by(Sampling_Cat,
           ExperimentalGroup,
           EvictionStatus,
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(Sel_FirstConc_Count)
#Seems that evictor from Guiness has no samples RRF008, no samples for almost 90 days around eviction 

View(DC_Info_F)

```


#Reproductive activation

All females that were evicted early did not successfully conceive in their group 

Rapid_Conc: 

- All samples of evictor are already covered 

- All samples of evictees are already covered for If a female has not activated before eviction she is unlikely to ovulate in the absence of a male. In the worse case we could select a few samples post eviction or before the end of the experiment 


Rapid_Pre: 

- For evictor, the date of activation could be anytime until the first successful conception. Take one sample every 14 days from paring until successful conception and then refine. 

- All samples of evictees are already covered for If a female has not activated before eviction she is unlikely to ovulate in the absence of a male. In the worse case we could select a few samples post eviction or before the end of the experiment 


Slow_Conc:

- For evictor and evictee, the date of activation could be anytime until the first successful conception. Take one sample every 14 days from paring until successful conception and then refine. 


Slow_Pre

- For evictor and evictee, the date of activation could be anytime until the first successful conception. Take one sample every 14 days from paring until successful conception and then refine.  

- For evictor one may wonder whether one wants to analyse past eviction if we think it is quite likely they activated before


No eviction

- all females gave birth. Take one sample every 14 days until conception and then refine.    


Keep in mind that I have all samples from 100 til 80 days pre-first parturition.


I decided to:

1) select the sample that is the closest to each 14 day benchmark, whether it was taken before or after. 

2) If the difference with the 14 days benchmark is the same for the sample collected just before and just after, I selected the sample collected after

3) I wanted to avoid the same sample being selected 2x. How do I do that? 


Originally I had decided to go for 21 days but increased the time resolution following Seagers' feedback 


```{r 14 days }

RA_Prep_14 <- DC_Info_Urine_F %>%
  
  #RETAIN ALL SAMPLES BETWEEN PAIRING AND FIRST SUCCESSFULL CONCEPTION
      filter(UrinePairing_DayDiff > 0,
         UrineFirstConception_DayDiff <= 0 | AnimalID == "ORF017",  #because ORF017 in Wicklow has not succesfully conceived when samples were shipped
         AnimalID != "DRF004") %>%  #evictee from BitBurger that got preg after eviction
  
  #DIVIDE 14
  mutate(Div14 = UrinePairing_DayDiff/14,
         Div14_1 = floor(Div14),
         Remainder14 = as.integer(UrinePairing_DayDiff) %% 14)



#Retain closest sample after each 14 day benchmark
Min14 <-  RA_Prep_14 %>% 
  #RETAIN ONLY FIRST SAMPLE OF EACH 14 DAYS PERIOD AND LAST SAMPLE OF PREVIOUS PERIOD
  group_by(AnimalID, 
           Div14_1) %>% 
  slice_min(Remainder14) %>% 
  ungroup() %>% 
  mutate(Slice = "Min")
  

#Retain closest sample before each 14 day benchmark
Max14 <-  RA_Prep_14 %>% 
  #RETAIN ONLY FIRST SAMPLE OF EACH 14 DAYS PERIOD AND LAST SAMPLE OF PREVIOUS PERIOD
  group_by(AnimalID, 
           Div14_1) %>% 
  slice_max(Remainder14) %>% 
  ungroup() %>% 
  mutate(Slice = "Max")


#Merge min and max
#I will then have to decide for each period whether I am gonna select the Min or the Max
MinMax14 <- bind_rows(Min14,
                      Max14) %>% 
    #ARRANGE
  arrange(Sampling_Cat,
          ExperimentalGroup, 
          EvictionStatus,
          AnimalID,
          UrineNumber) %>% 
  
  #REMOVE FIRST SAMPLE 
  filter(!(Div14_1 == 0 & Slice == "Min")) %>% 
  
  #LAG INFO 
  group_by(AnimalID) %>% 
  mutate(Remainder_Lag = abs(lag(Remainder14)-14),
         UrineDate_Lag = lag(UrineDate),
         UrineNumber_Lag = lag(UrineNumber)) %>% 
  ungroup()
```


```{r}

  
  
View(MinMax14)
  

View(RA_Prep_14)



#Second step of preparation
#generates a dataset that shows first sample of a given period and last sample of previous period
RA_Prep2_14 <- RA_Prep_14 %>% 
  

  
  #REMOVE FIRST PERIOD 
  #Because this is for the first 14 days and has already been covered 
  filter(!Div14_1 == 0) %>% 
  
  #COMPUTE DIFFERENCE TO DECIDE WHETHER LAST OR FIRST SAMPLE OF PERIOD IS BETTER 
  mutate(Remainder14_Lag = abs(Lag - 14))
View(RA_Prep2_14)
#83 samples when using 21 days intervals 
#131 samples when using 14 days interval. I think I will go with this considering that there are a few samples that have not been shipped because they were in the freezer that got defrosted


#Check if all expected individuals are here 
View(RA_Prep2 %>% 
       distinct(Sampling_Cat,
                ExperimentalGroup,
                EvictionStatus,
                AnimalID) %>% 
       arrange(Sampling_Cat,
               ExperimentalGroup,
               EvictionStatus))

names(RA_Prep2_14)




ToPrint <- RA_Prep_14 %>% 
  select(Sampling_Cat,
         ExperimentalGroup,
         BS_Original,
         EvictionStatus,
         AnimalID,
         UrineNumber,
         UrinePairing_DayDiff,
         UrineFirstConception_DayDiff,
         UrineEviction_DayDiff,
         UrineDate, 
         Div14:Remainder14) %>% 
  
  arrange(Sampling_Cat,
          ExperimentalGroup,
          EvictionStatus,
          UrineNumber)

View(ToPrint)











#Select among closest sample for each time period 
Sel_RA_14_SampleID <- RA_Prep2_14 %>% 
  
  #SELECT SAMPLE ID
  mutate(Urine_ToSelect = case_when(Remainder14 < Remainder14_Lag ~ UrineNumber,
                                 Remainder14 > Remainder14_Lag ~ Lag_UrineNumber,
                                 Remainder14 == Remainder14_Lag ~ UrineNumber)) %>% 
  
  #TYPE OF SAMPLE SELECETED 
  mutate(SelectionType = case_when(Remainder14 < Remainder14_Lag ~ "After14",
                                 Remainder14 > Remainder14_Lag ~ "Before14",
                                 Remainder14 == Remainder14_Lag ~ "After14")) 


#After14 benchmark 
After14 <- Sel_RA_14_SampleID %>% 
  filter(SelectionType == "After14") %>% 
  select(Urine_ToSelect, 
         SelectionType,
         Div14_1,
         Remainder14)


#Before14 benchmark 
Before14 <- Sel_RA_14_SampleID %>% 
  filter(SelectionType == "Before14") %>%
    select(Urine_ToSelect, 
           SelectionType,
           Div14_1,
           Remainder14_Lag) %>% 
  rename(Remainder14 = Remainder14_Lag)


#Merge before and after and add urine info 
AfterBefore14 <- bind_rows(After14,
                           Before14) %>% 
  rename(UrineNumber = Urine_ToSelect) %>% 
  
  #ADD URINE INFO 
  left_join(., DC_Info_Urine_F) %>% 
  
  #ARRANGE CHRONOLOGICALLY
  group_by(AnimalID) %>% 
  arrange(UrineDate, UrineNumber) %>% 
  #ADD THE DIFFERENCE IN DAYS BETWEEN THE SAMPLES 
  mutate(UrineDyDiff = UrineDate - lag(UrineDate)) %>% 
  ungroup()

View(AfterBefore14)
  
  


#Are there samples that appeared 2x? 
View(AfterBefore14 %>% 
  group_by(Urine_ToSelect) %>% 
  filter(n()> 1) %>% 
  ungroup())


View(AfterBefore14)



  
  
names(Sel_RA_14_SampleID)
  


Sel_RA_14 <- 



  #REMOVE SAMPLES SELECTED BEFORE
  #does not change the number of samples if samples already selected before are removed
  
  #REMOVE SAMPLES POST-PAIRING  
  #filter(!UrineNumber %in% Sel_PostPair$UrineNumber) %>% 
  #REMOVE SAMPLES PRE-EVICTION 
  #filter(!UrineNumber %in% Sel_PreEviction$UrineNumber) %>% 
  #REMOVE SAMPLES POST-EVICTION
  #filter(!UrineNumber %in% Sel_PostEviction$UrineNumber) %>% 
  #REMOVE SAMPLES FIRST CONC
  #filter(!UrineNumber %in% Sel_FirstConc$UrineNumber) %>%
  #ADD SELECTION REASON 
  mutate(SampleReason = "RADet")
View(Sel_RA_14)
#131 if samples already selected are in the list
#102 if they are removed


#Count of samples
Sel_RA_Count <- Sel_RA %>% 
  group_by(Sampling_Cat,
           ExperimentalGroup,
           EvictionStatus,
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(Sel_RA_Count)

```


#All Samples 

All selected samples

```{r All samples}

DC_Analyses <- bind_rows(Sel_Isol, # isolation
                         Sel_PostPair,
                         Sel_PreEviction,
                         Sel_PostEviction,
                         Sel_FirstConc,
                         Sel_RA_14) %>% 
  
  #JOIN INVENTORY 
  left_join(.,Inventory, by=c("UrineNumber" = "SampleID") )

View(DC_Analyses)
#830 samples
#836 after I have 

names(Inventory)
names(DC_Analyses)


#only checking sample 
View(DC_Analyses %>% 
       distinct(UrineNumber))
#658 samples unique 

```


#All selected samples that are available in Neuchatel

