---
title: "Untitled"
output: html_document
date: "2024-02-06"
---

#Package

```{r}

library(tidyverse)

```


#General 

1) In firestone the breeding female ORF005 died when she gave birth (after she had evicted ORF018). 

After this the male DRM006 was used to found Kasteel. This has consequences for sample selection. 

```{r Data}

names(DC_Info_F)

#DC Info Females
DC_Info_F <- read.csv("DC_Info_F_20240326.csv") %>% 
  mutate(BirthDate = ymd(BirthDate),
         KingRemovalDate = ymd(KingRemovalDate),
         OriginalGroup_LastParturitionDate = ymd(OriginalGroup_LastParturitionDate),
         PairingDate = ymd(PairingDate),
         IsolationDate = ymd(IsolationDate),
         DeathDate = ymd(DeathDate),
         LastDate = ymd(LastDate),
         FirstDCConceptionDate = ymd(FirstDCConceptionDate),
         FirstDCParturitionDate = ymd(FirstDCConceptionDate),
         EvictionDate = ymd(EvictionDate))
names(DC_Info_F)



#Urine info 
#DC_Urine_F_20240318.csv
DC_Info_Urine_F <- read.csv("DC_Info_Urine_F_20240326.csv") %>% 
  mutate(EvictionDate = ymd(EvictionDate),
         UrineDate = ymd(UrineDate))
names(DC_Info_Urine_F)



#Sample inventory _Inventory
Inventory <- read.csv("Freezer_Inventory_20240318.csv") %>% 
  mutate(Date = dmy(Date)) %>% 
  filter(!is.na(SampleID))
View(Inventory)
#8133


#Latest inventory 
Inventory_Latest <- Inventory %>% 
  group_by(SampleID) %>% 
  slice_max(Date) %>% 
  ungroup()
View(Inventory_Latest)
#8063

```


#Inventory check 

```{r}


#Are there samples that have 2 eppendorfs? 
Inventory_Duplicates <- Inventory_Latest %>% 
  group_by(SampleID) %>% 
  filter(n() > 1) %>% 
  ungroup() %>% 
  slice_max(Date) %>% 
  arrange(SampleID) %>% 
  #ADD COLLECTION INFO 
  left_join(., Urine_Collected %>% 
              select(UrineNumber,
                     AnimalID,
                     UrineDate,
                     Eppendorfs), by = c("SampleID" = "UrineNumber")) %>% 
  relocate(AnimalID:Eppendorfs)
View(Inventory_Duplicates)
#1 samples have 2 eppendorfs and still must be corrected. 
#I sent a mail about it on the 19/03/2024 to Dave and Channen

names(Urine_Collected)

write.csv(Inventory_Duplicates, "Inventory_Duplicates_20240318.csv",row.names = FALSE)

#How many eppendorfs were collected from these samples
Duplicated  <- Inventory_Duplicates %>% 
  distinct(SampleID) %>% 
  #ADD NB OF EPPENDORFS COLLECTED
  left_join(., Urine_Collected %>% 
              select(UrineNumber,
                     Eppendorfs), by = c("SampleID" = "UrineNumber"))
#Always one, therefore it shold not be possible to have 2 rows for these in the inventory

```


#Sample lag 

Normally female should have been sampled approximately once a week during the experiment. 

SOF001 from Corbeau was not sampled for 46 days 
ORF017 from Wicklow was not sampled for 45 days
VGF002 from Wicklow was not sampled for 34 days 



```{r}

SampleLag <- DC_Info_Urine_F %>%
  filter(UrinePairing_DayDiff >= 0, 
         EvictionStatus == "Evictee" & UrineEviction_DayDiff <= 10 | EvictionStatus %in% c("InGroup", "Evictor")) %>% 
  group_by(AnimalID) %>% 
  mutate(LagUrineDate = lag(UrineDate)) %>% 
  ungroup() %>% 
  mutate(LastSampleDelay = UrineDate - LagUrineDate) %>% 
  filter(!is.na(LastSampleDelay)) %>% 
  arrange(desc(LastSampleDelay))

View(SampleLag)

```


#Question 1: 

Determine differences between BF and NBF when there is no breeding opportunity and determine whether ovulation occurs 

Take 1 sample after two weeks 
Take last 2 samples before pairing 

3 samples per female = 156 samples 


```{r Isolation}
names(DC_Info_Urine_F)

#two weeks 
Isol_2W <- DC_Info_Urine_F %>% 
  filter(UrineIsol_DayDiff >= 14) %>% 
  group_by(AnimalID) %>% 
  slice_min(UrineIsol_DayDiff) %>% 
  ungroup()
View(Isol_2W)
#50 samples all good


#Pre-pairing
#In the worse case I could only get the last sample before pairing
Isol_PrePair <- DC_Info_Urine_F %>% 
  filter(UrinePairing_DayDiff <= 0) %>% 
  group_by(AnimalID) %>% 
  slice_max(UrineIsol_DayDiff, n=2) %>% 
  ungroup()
View(Isol_PrePair)

#Check for duplicates
View(Isol_PrePair %>% 
       group_by(AnimalID) %>% 
       mutate(Count = n_distinct(UrineNumber)) %>% 
       ungroup)
#ERF002 from Leffe has 2 samples on a given day, but one of them must be wrong because they have been collected almost at the same time. Check side label and only take the first and correct 

```


```{r Sel}

Sel_Isol <- bind_rows(Isol_2W,
                      Isol_PrePair) %>% 
  distinct(UrineNumber) %>% 
  mutate(SampleReason = "Isolation")
View(Sel_Isol)
#150 samples

```


#Question 2

Effect of the presence of:

- The king -> affect the reproductive status of the BF and generates an assymetry in breeding opportunity. => King were only removed in some group, the ones where 2 sub were taken from the sub treatment. Some of these groups were also used to create Queen treatment and thus the king was removed.

There are 5 groups where the Sub were not subjected to an reproductively active queen at the time of isolation



- The queen.

- The removal from the natal group.

on the hormonal profile of NBF. 

In question 1) only samples post-isolation are selected. Here one would add a longitudinal component to the question. 

This was not part of the original suggestion I had made to Dave and TCB and I thought about adding these at a later stage on the 19/03/2024 after I found out that samples that had been defrosted where not shipped to the NPAC, thereby decreasing the number of samples that could be analyzed.

Before extracting and analysing, assess the number of extra samples and consequences on number of samples compared to the suggestion I had sent to Dave and TCB (if my memory is good it was about 680 samples). If the number of samples is roughly the same I could probably go ahead.

This question basically complements Question by adding samples of NBF and BF while they were still in their original group, specifically 

i) samples of NBF while the BF was reproductively active (the king was present). For this we may only have samples of when the queen was pregnant, but one may ask if it would not be better to select samples at conception.

ii) samples of BF and NBF after the king had been removed

iii) For queen one may also add all samples collected between her last parturition and removal from the group.

Based on the overview of data I should take closest sample to pairing and then closest sample to 14 days. This may mean that a few females were still lactating 

```{r PreIsol delay}

#Delay from Parturition to isolation
ParturitionIsol_Delay <- DC_Info_F %>% 
  select(Treatment,
         ExperimentalGroup,
         OriginalGroup,
         OriginalGroup_LastParturitionDate,
         IsolationDate) %>% 
  mutate(ParturitionIsolation_DayDiff = OriginalGroup_LastParturitionDate - IsolationDate) %>% 
  distinct()
View(ParturitionIsol_Delay)
#Orycterope (Kastel, wicklow) 19 days 
#Plaka plaka (Delirium Chouffe) 26 days 
#Ruru (Licher, Darling brew) 26 days 



ggplot(ParturitionIsol_Delay, aes(x = Treatment, y = ParturitionIsolation_DayDiff))+
  geom_boxplot()+
  geom_jitter()



```

Post-Part and Pre-Isol samples 

```{r samples}

PostPartPreIsol <- DC_Info_Urine_F %>% 
  filter(UrineIsol_DayDiff <= 0, #samples collected before isolation
         UrineLastParturitionOirginalGroup_DayDiff >= 0) %>%  #after the last parturition of the queen) 
  #ONLY RETAIN RELEVANT INFO 
    select(ExperimentalUnit,
         ExperimentalGroup,
         Treatment,
         BS_Original,
         AnimalID,
         UrineIsol_DayDiff,
         UrineNumber) %>% 
  arrange(ExperimentalUnit,
          BS_Original)
View(PostPartPreIsol)

```

For pre isolation sample 

Sample 36751 from TIF039 -16 days isolation seem to not have exported and instead 36757 was exported. I realized this when extracting. Thus I replaced that sample with 36852 - days pre-isolation. 36751 will appear in the list returned below. 

```{r Pre-Isol 14 days}

#Collected within 14 days of parturition
PostPartPreIsol14 <- PostPartPreIsol %>% 
  filter(UrineIsol_DayDiff >= - 14)
View(PostPartPreIsol14)
#152 samples


#Missing sample 
PreIsol14_MissingSample <- anti_join(DC_Info_F %>% 
            select(ExperimentalGroup,
                   ExperimentalUnit,
                   Treatment,
                   BS_Original,
                   AnimalID), PostPartPreIsol14) %>% 
  arrange(ExperimentalUnit, 
          BS_Original)
View(PreIsol14_MissingSample)

write.csv(PreIsol14_MissingSample,"PreIsol14_MissingSample.csv",row.names = FALSE)
  

#Summary
PostPartPreIsol14_Summary <- PostPartPreIsol14 %>% 
  group_by(ExperimentalUnit,
           ExperimentalGroup,
           BS_Original,
           AnimalID) %>% 
  summarise(Count = n(),
         Min = min(UrineIsol_DayDiff),
         Max = max(UrineIsol_DayDiff))
View(PostPartPreIsol14_Summary)

```


```{r 21 days}


#Collected within 21 days of parturition
PostPartPreIsol21 <- PostPartPreIsol %>% 
  filter(UrineIsol_DayDiff >= - 21)
View(PostPartPreIsol21)
#152 samples


#Missing sample 
PreIsol21_MissingSample <- anti_join(DC_Info_F %>% 
            select(ExperimentalGroup,
                   ExperimentalUnit,
                   Treatment,
                   BS_Original,
                   AnimalID), PostPartPreIsol21) %>% 
  arrange(ExperimentalUnit, 
          BS_Original)
View(PreIsol21_MissingSample)

  

#Summary
PostPartPreIsol21_Summary <- PostPartPreIsol21 %>% 
  group_by(ExperimentalUnit,
           ExperimentalGroup,
           BS_Original,
           AnimalID) %>% 
  summarise(Count = n(),
         Min = min(UrineIsol_DayDiff),
         Max = max(UrineIsol_DayDiff))
View(PostPartPreIsol21_Summary)
```


Latest sample before isolation

```{r Day 0}

PostPartPreIsol_Latest <- PostPartPreIsol %>% 
  group_by(AnimalID) %>% 
  slice_max(UrineIsol_DayDiff) %>% 
  ungroup()

View(PostPartPreIsol_Latest)

#

```

```{r Sel}

Sel_PreIsol1 <- PostPartPreIsol_Latest %>% 
  select(UrineNumber) %>% 
  mutate(SampleReason = "PreIsol1")

```

```{r Day 14}

#In case two values returned the same value I selected 1 randomly
PostPartPreIsol14 <- PostPartPreIsol %>%
  mutate(Delta14 = abs(as.integer(UrineIsol_DayDiff+14))) %>% 
  group_by(AnimalID) %>% 
  slice_min(Delta14) %>% 
  slice_sample(n=1) %>% 
  ungroup()
View(PostPartPreIsol14)


```


```{r Sel}

Sel_PreIsol14 <- PostPartPreIsol14 %>% 
  select(UrineNumber) %>% 
  mutate(SampleReason = "PreIsol14")
```


#Question 3

Effect of breeding opportunity on hormone levels and hormonal correlates of dominance and eviction

## Post-Pairing 

```{r Post paring}

#Samples that were collected on the day of eviction
#Have asked the project if they should be considered pre or post eviction
#For now I assume that they are pre-eviction
EvictionSample <- DC_Info_Urine_F %>% 
  filter(UrineEviction_DayDiff == 0)

write.csv(EvictionSample, "EvictionSample_ToCheck_20240215.csv", row.names = FALSE)
#Awaiting answer


#Post pairing samples 
PostPair <- DC_Info_Urine_F %>% 
  filter(UrinePairing_DayDiff > 0, 
         UrinePairing_DayDiff <= 10, 
         UrineEviction_DayDiff <= 0 | is.na(UrineEviction_DayDiff)) 
  
View(PostPair)
#149 samples


#Samples pre individuals 
PostPair_Count <- Sel_PostPair %>% 
  group_by(ExperimentalGroup, 
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(PostPair_Count)
#Between 1 and 6 samples per individual 


View(anti_join(DC_Info_F, PostPair_Count))
#The only sample that is missing is from Ashai where eviction occured on day 0

View(DC_Info_F)

```


```{r Sel}

Sel_PostPair <- PostPair %>%
  distinct(UrineNumber) %>% 
  mutate(SampleReason = "PostPair10")

```


## Pre eviction 

Pre-Eviction samples not accounted for in post-pairing samples. I have opted for 16 days pre-pairing.

```{r Pre-Eviction }

#Pre-Eviction
PreEviction <- DC_Info_Urine_F %>%
  #REMOVE SAMPLES ALREADY COUNTED IN POST PAIRING
  #filter(!UrineNumber %in% Sel_PostPair$UrineNumber) %>% 
  #FILTER
  filter(UrinePairing_DayDiff > 0, 
         UrineEviction_DayDiff <= 0,
         UrineEviction_DayDiff >= -16)

View(PreEviction)
#10 days =  32 samples
#12 days = 34 samples
#14 days =  35 samples
#16 days =  42 samples between 2 and 6 samples per individual at the excpetion of SOF001 that has no samples
#18 days =  42 samples
#20 days =  44 samples


PreEviction_Count <- PreEviction %>% 
  group_by(Sampling_Cat,
           ExperimentalGroup,
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(PreEviction_Count)
#Samples from evictor SOF001 in Corbeau (Slow_Conc) are missing. 
#I suspect that it is because eviction occurred really late. Weirdly there is no samples between 184 and 230 days post pairing


#Ask the project to ask the reason 
SOF001 <- DC_Info_Urine_F %>% 
  filter(AnimalID == "SOF001")
write.csv(SOF001, "SOF001_Urine.csv", row.names = FALSE)


#View the samples gathered for slow eviction 
View(PreEviction %>% 
       filter(Sampling_Cat %in% c("Slow_Conc","Slow_PreFirst","Slow_None")) %>% 
       arrange(ExperimentalGroup, AnimalID))

```


```{r Sel}

Sel_PreEviction <- PreEviction %>%
  distinct(UrineNumber) %>% 
  mutate(SampleReason = "PreEviction16")


```


##Post eviction 

No samples has been collected post-eviction yet so no need remove samples collected before

```{r Post eviction}

#First sample post eviction
PostEviction_1 <- DC_Info_Urine_F %>%
  #FILTER
  filter(UrineEviction_DayDiff > 0) %>% 
  group_by(AnimalID) %>% 
  slice_min(UrineEviction_DayDiff) %>% 
  ungroup() %>% 
  mutate(SampleReason = "PostEviction1")
View(PostEviction_1)
#All samples have been collected within 2 days of eviction 
#However, only 43 females meaning that 7 are missing 

#Animals that lack a post-eviction sample 
PostEviction_MissingID <- DC_Info_F %>% 
  select(ExperimentalGroup, 
         AnimalID, 
         BS_Original,
         EvictionStatus, 
         DeathDate,
         EvictionDate) %>% 
  left_join(., SamplingCat) %>% 
  relocate(Sampling_Cat) %>% 
  anti_join(.,PostEviction_1)
View(PostEviction_MissingID )
#Samples are missing from the 3 females where there has been no eviction 
#VGF002 is missing but it seems because she died on the day of eviction so normal there is no sample


#First sample after 14 days post eviction. I cannot really remember why I used that rational. 
#I think it had to do with when I expected to have last sample of evictor, so the two condition would more or less match
#I could always add samples at a later stage
PostEviction_14 <- DC_Info_Urine_F %>%
  #FILTER
  filter(UrineEviction_DayDiff >= 14) %>% 
  group_by(AnimalID) %>% 
  slice_min(UrineEviction_DayDiff) %>% 
  ungroup()
View(PostEviction_14)
#All samples within 9 days except Darling brew wirth 13 and 15 days 
#42 individuals so one more missing as after 1 day 

Post14_Count <- PostEviction_14 %>% 
  group_by(Sampling_Cat,
           ExperimentalGroup,
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(Post14_Count )

```


```{r Sel}

#All post eviction samples
Sel_PostEviction <- bind_rows(PostEviction_1, 
                              PostEviction_14) %>% 
  distinct(UrineNumber) %>% 
  mutate(SampleReason = "PostEviction14")
View(Sel_PostEviction)

```


##Activation-Pregnancy samples

All samples collected between 100 days and 80 days to determine:

- Reproductive activation of some females
- hormone profile of early gestation. 
- Effect of presence of other female on gestation profile of early gestation


We are only missing sample of one gestation, RSF008 the evictor from Guinness where sampling seem to have been stopped before the first successful conception

```{r First conception}

names(DC_Info_Urine_F)

#Are there evictee that gave birth within 100 days of eviction 
View(DC_Info_F %>% 
  filter(EvictionStatus == "Evictee"))

FirstConc <- DC_Info_Urine_F %>% 
  #REMOVE BITBURGER QUEEN THAT GOT PREGNANT AFTER EVICTION
  filter(AnimalID != "DRF004") %>% 
  
  #REMOVE SAMPLES POST-PAIRING 
  #I DECIDED TO REMOVE THIS SO I CAN SEE FOR EACH SAMPLE ALL THE REASONS WHY THEY WERE SELECTED 
  #filter(!UrineNumber %in% Sel_PostPair$UrineNumber) %>%

  #REMOVE SAMPLES PRE-EVICTION
  #I DECIDED TO REMOVE THIS SO I CAN SEE FOR EACH SAMPLE ALL THE REASONS WHY THEY WERE SELECTED
  #filter(!UrineNumber %in% Sel_PreEviction$UrineNumber) %>%

  #REMOVE SAMPLES POST-EVICTION
  #I DECIDED TO REMOVE THIS SO I CAN SEE FOR EACH SAMPLE ALL THE REASONS WHY THEY WERE SELECTED
  #filter(!UrineNumber %in% Sel_PostEviction$UrineNumber) %>%

  #RETAIN FIRST LITTER 
  filter(NextLitter_IndCount_Colony == 1) %>%               
  #FILTER SAMPLES WITHIN TIME RANGE NEEDED 
  filter(NextParturition_ParturitionDayDiff >=- 100,
         NextParturition_ParturitionDayDiff <= -80)
View(Sel_FirstConc)
#219 samples but that does not take into account samples already selected previously
#146 if samples already selected are removed


#Count of samples
Sel_FirstConc_Count <- FirstConc %>% 
  group_by(Sampling_Cat,
           ExperimentalGroup,
           EvictionStatus,
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(Sel_FirstConc_Count)
#Seems that evictor from Guiness has no samples RRF008, no samples for almost 90 days around eviction 

View(DC_Info_F)

```

```{r Sel}

Sel_FirstConc <-  FirstConc %>% 
  distinct(UrineNumber) %>% 
  mutate(SampleReason = "FirstConc")

```

##Reproductive activation

All females that were evicted early did not successfully conceive in their group 

Rapid_Conc: 

- All samples of evictor are already covered 

- All samples of evictees are already covered for If a female has not activated before eviction she is unlikely to ovulate in the absence of a male. In the worse case we could select a few samples post eviction or before the end of the experiment 


Rapid_Pre: 

- For evictor, the date of activation could be anytime until the first successful conception. Take one sample every 14 days from paring until successful conception and then refine. 

- All samples of evictees are already covered for If a female has not activated before eviction she is unlikely to ovulate in the absence of a male. In the worse case we could select a few samples post eviction or before the end of the experiment 


Slow_Conc:

- For evictor and evictee, the date of activation could be anytime until the first successful conception. Take one sample every 14 days from paring until successful conception and then refine. 


Slow_Pre

- For evictor and evictee, the date of activation could be anytime until the first successful conception. Take one sample every 14 days from paring until successful conception and then refine.  

- For evictor one may wonder whether one wants to analyse past eviction if we think it is quite likely they activated before


No eviction

- all females gave birth. Take one sample every 14 days until conception and then refine.    


Keep in mind that I have all samples from 100 til 80 days pre-first parturition.


I decided to:

1) select the sample that is the closest to each 14 day benchmark, whether it was taken before or after. 

2) If the difference with the 14 days benchmark is the same for the sample collected just before and just after, I selected the sample collected after

3) I wanted to avoid the same sample being selected 2x. How do I do that? 


Originally I had decided to go for 21 days but increased the time resolution following Seagers' feedback 

Plot suggest Closest Max is the best, but there will be a few samples to add 


```{r 14 days }

RA_Prep_14 <- DC_Info_Urine_F %>%
  
  #RETAIN ALL SAMPLES BETWEEN PAIRING AND FIRST SUCCESSFULL CONCEPTION
      filter(UrinePairing_DayDiff > 0,
         UrineFirstConception_DayDiff <= 0 | AnimalID == "ORF017",  #because ORF017 in Wicklow has not succesfully conceived when samples were shipped
         AnimalID != "DRF004") %>%  #evictee from BitBurger that got preg after eviction
  
  #DIVIDE 14
  mutate(Div14 = UrinePairing_DayDiff/14,
         Div14_1 = floor(Div14),
         Remainder14 = as.integer(UrinePairing_DayDiff) %% 14)



#Retain closest sample after each 14 day benchmark
Min14 <-  RA_Prep_14 %>% 
  #RETAIN ONLY FIRST SAMPLE OF EACH 14 DAYS PERIOD AND LAST SAMPLE OF PREVIOUS PERIOD
  group_by(AnimalID, 
           Div14_1) %>% 
  slice_min(Remainder14) %>% 
  ungroup() %>% 
  mutate(Slice = "Min")
View(Min14)
#165 entries
  

#Retain closest sample before each 14 day benchmark
Max14 <-  RA_Prep_14 %>% 
  #RETAIN ONLY FIRST SAMPLE OF EACH 14 DAYS PERIOD AND LAST SAMPLE OF PREVIOUS PERIOD
  group_by(AnimalID, 
           Div14_1) %>% 
  slice_max(Remainder14) %>% 
  ungroup() %>% 
  mutate(Slice = "Max")
View(Max14)
#166 entries


#Merge min and max
#I will then have to decide for each period whether I am gonna select the Min or the Max
MinMax14 <- bind_rows(Min14,
                      Max14) %>% 
    #ARRANGE
  arrange(Sampling_Cat,
          ExperimentalGroup, 
          EvictionStatus,
          AnimalID,
          UrineNumber)
View(MinMax14)
#331 entries
  

#Put the lag info (The max remainder) next to the min remainder for each period.
#In that way I have the two closest sample of each benchmark next to each other 

MinMax14_Wide <- MinMax14 %>% 
  # ADD LAG INFO 
  #For each period we have the min after and min before (Max of previous period) 14 days mark 
  group_by(AnimalID) %>% 
  mutate(Difference_Lag = abs(lag(Remainder14)-14),
         UrineNumber_Lag = lag(UrineNumber),
         UrineDate_Lag = lag(UrineDate),
         Period_Lag = lag(Div14_1),
         Slice_Lag = lag(Slice)) %>% 
  ungroup() %>% 
  
  #RETAIN ONLY MIN OF EACH PERIOD 
  filter(Slice == "Min") %>% 
  
  #REMOVE PERIOD 1
  filter(Div14_1 != 0)
#131



#Out of the 331 entries, how many times is the difference with remainder the same between AFTER and BEFORE benchmark? 
MinMax14_Equal <-  MinMax14_Wide %>% 
  filter(Remainder14 == Difference_Lag)
View(MinMax14_Equal)
#Out of the 131 entries there are 25  for which there closest sample before and after are the same.

```

What happens if one consistently select the samples after the 14 days benchmark.

```{r Min}

#Min
Sel_RA_Min <- MinMax14_Wide %>% 
  
  #SELECT
  select(Sampling_Cat,
         ExperimentalGroup,
         AnimalID,
         Div14_1,
         UrineNumber,
         UrineDate,
         Remainder14) %>% 
  
  #ADD DIFFERENCE IN DAYS WITH PREVIOUS SAMPLES
  group_by(AnimalID) %>% 
  mutate(UrineDayDiff = UrineDate - lag(UrineDate)) %>% 
  ungroup() %>% 
  
  #ADD SELECTION TYPE
  mutate(SelectionType = "Min")
View(Sel_RA_Min)


#Max
Sel_RA_Max <- MinMax14_Wide %>% 
  
  #SELECT
  select(Sampling_Cat,
         ExperimentalGroup,
         AnimalID,
         Div14_1,
         UrineNumber_Lag,
         UrineDate_Lag,
         Difference_Lag) %>% 
  
  #RENAME
  rename(UrineNumber = UrineNumber_Lag,
         UrineDate = UrineDate_Lag,
         Remainder14 = Difference_Lag) %>% 
  
  #ADD DIFFERENCE IN DAYS WITH PREVIOUS SAMPLES
  group_by(AnimalID) %>% 
  mutate(UrineDayDiff = UrineDate - lag(UrineDate)) %>% 
  ungroup() %>% 
  
  #ADD SELECTION TYPE
  mutate(SelectionType = "Max")
View(Sel_RA_Max)


############################Closest Min

#If Min and Max are equal take Min, take min

#Filter min 
ClosestMin_Min <- MinMax14_Wide %>% 
  
  #RETAIN MIN
  filter(Remainder14 <= Difference_Lag) %>% 
  
  #SELECT
  select(Sampling_Cat,
         ExperimentalGroup,
         AnimalID,
         Div14_1,
         UrineNumber,
         UrineDate,
         Remainder14) 
  

#Filter max 
ClosestMin_Max <- MinMax14_Wide %>% 
  
  #RETAIN MIN
  filter(Remainder14 > Difference_Lag) %>% 
  
    #SELECT
  select(Sampling_Cat,
         ExperimentalGroup,
         AnimalID,
         Div14_1,
         UrineNumber_Lag,
         UrineDate_Lag,
         Difference_Lag) %>% 
  
  #RENAME
  rename(UrineNumber = UrineNumber_Lag,
         UrineDate = UrineDate_Lag,
         Remainder14 = Difference_Lag)
  

#Merge
ClosestMin <- bind_rows(ClosestMin_Min,
                        ClosestMin_Max) %>% 
  
  #ARRANGE
  arrange(Sampling_Cat,
          ExperimentalGroup,
          AnimalID,
          UrineDate,
          UrineNumber) %>% 
  
  #ADD DIFFERENCE IN DAYS WITH PREVIOUS SAMPLES
  group_by(AnimalID) %>% 
  mutate(UrineDayDiff = UrineDate - lag(UrineDate)) %>% 
  ungroup() %>% 
  
  #ADD SELECTION TYPE
  mutate(SelectionType = "ClosestMin")


#############################################Closest Max

#If Min and Max are equal take Min, take max
#This is teh one I ultimately took for sample 

#Filter min 
ClosestMax_Min <- MinMax14_Wide %>% 
  
  #RETAIN MIN
  filter(Remainder14 < Difference_Lag) %>% 
  
  #SELECT
  select(Sampling_Cat,
         ExperimentalGroup,
         AnimalID,
         Div14_1,
         UrineNumber,
         UrineDate,
         Remainder14) 
  

#Filter max 
ClosestMax_Max <- MinMax14_Wide %>% 
  
  #RETAIN MIN
  filter(Remainder14 >= Difference_Lag) %>% 
  
    #SELECT
  select(Sampling_Cat,
         ExperimentalGroup,
         AnimalID,
         Div14_1,
         UrineNumber_Lag,
         UrineDate_Lag,
         Difference_Lag) %>% 
  
  #RENAME
  rename(UrineNumber = UrineNumber_Lag,
         UrineDate = UrineDate_Lag,
         Remainder14 = Difference_Lag)
  

#Merge
ClosestMax <- bind_rows(ClosestMax_Min,
                        ClosestMax_Max) %>% 
  
  #ARRANGE
  arrange(Sampling_Cat,
          ExperimentalGroup,
          AnimalID,
          UrineDate,
          UrineNumber) %>% 
  
  #ADD DIFFERENCE IN DAYS WITH PREVIOUS SAMPLES
  group_by(AnimalID) %>% 
  mutate(UrineDayDiff = UrineDate - lag(UrineDate)) %>% 
  ungroup() %>% 
  
  #ADD SELECTION TYPE
  mutate(SelectionType = "ClosestMax")


#Count of samples
Sel_RA_Count <- Sel_RA %>% 
  group_by(Sampling_Cat,
           ExperimentalGroup,
           EvictionStatus,
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(Sel_RA_Count)



#################################################All selection 

RA_Sel_AllTypes <- bind_rows(Sel_RA_Min,
                             Sel_RA_Max,
                             ClosestMin,
                             ClosestMax)
View(RA_Sel_AllTypes)

```


Based on the plotting, closest Max seems to give the best outcome. 

Thus, I should follow this and will then add the samples to increase the resolution.

```{r Plot RA}

#Plot Remainder 
#Closest mina nd max are the same and it is what is to be expected 
#Closest Mina nd Max will differe by how many days between samples
RA_Remainder_Plot <- ggplot(RA_Sel_AllTypes, aes(x = SelectionType, y=Remainder14)) + 
  geom_boxplot() +
  geom_jitter(height = 0, size=2, width = 0.3, alpha = 0.5)


#Day diff with outliers
RA_DayDiff_Plot <- ggplot(RA_Sel_AllTypes, aes(x = SelectionType, y=UrineDayDiff)) + 
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(height = 0, size=2, width = 0.3, alpha = 0.5) +
  geom_hline(yintercept = 14, linetype = "dashed", color = "red")


#Day Diff without outliers
RA_DayDiff_Plot <- ggplot(RA_Sel_AllTypes %>% 
                            filter(UrineDayDiff <=30), aes(x = SelectionType, y=UrineDayDiff)) + 
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(height = 0, size=2, width = 0.3, alpha = 0.5) +
  geom_hline(yintercept = 14, linetype = "dashed", color = "red")
  

```

I will have to deal with outliers as some samples are used for two distinct time period and sometimes the interval between samples is way too long.

On the 20/03/2024 I had not added any samples to deal with this 

```{r Outliers}

#Animals that have not been sampled for incredibly long amount of time 
DayDiff30 <- 


#Animals for which the same sample is used for 2 different time period. 

```

```{r Sel}

names(ClosestMax)

Sel_RA <- ClosestMax %>% 
  distinct(UrineNumber) %>% 
  mutate(SampleReason = "RA")

```


#Sample List 

##Freezer position

```{r All samples}

#All samples to be analysed on the 20/03/2024. At that date no samples before isolation was choses

SampleList <- bind_rows(Sel_PreIsol1,
                        Sel_PreIsol14,
                        Sel_Isol, 
                         Sel_PostPair,
                         Sel_PreEviction,
                         Sel_PostEviction,
                         Sel_FirstConc,
                         Sel_RA) %>%
  #JOIN INVENTORY 
  left_join(.,Inventory, by=c("UrineNumber" = "SampleID") )

View(SampleList)
#932 samples before inventory 



#write a csv that can be used to get sample out of the freezer 
write.csv(SampleList %>% 
            arrange(BoxID,
                    BoxPosition), "SampleList_20240326.csv", row.names = FALSE)

```


## with info 

Just join all the info that will be helpful to organize the sequence on the batch but also to check whether I may not have anything suspicious on the list.

The relevant info to each list will be selected in the DC_SampleExtraction document

```{r}

SampleList_Info <- SampleList %>% 
  
  #ADD INFO 
  left_join(.,DC_Info_Urine_F) %>% 
  
  #RELEVEL FACTOR SAMPLE REASON 
  mutate(SampleReason = fct_relevel(SampleReason, c("PreIsol1","PreIsol14","Isolation","PostPair10","PreEviction16","PostEviction14","RA","FirstConc")))
View(SampleList_Info)

View(SampleList_Info %>% 
       filter(SampleReason %in% c("PreIsol1","PreIsol14")) %>% 
       filter(is.na(BoxPosition)))
#18 samples are missing 


#write csv
write.csv(SampleList_Info,"SampleList_Info_20240326.csv",row.names = FALSE)

```


#Sample Count 

Sample Count on the 20/03/2024. Before selection of pre-isolation sample and before increase of time resolution of reproductive activation

```{r All}

#Count of samples to be analysed
SampleCount <- SampleList %>% 
  distinct(UrineNumber)
View(SampleCount)
#750 samples 
#This must be contrasted with the suggestion I had sent to TCB and Dave
#Check for each section how much samples I have (after discunting the one previosuly selected)
#This should be done before I start the extraction of post pairing samples 

```

```{r Summary }

#Count of sample missing by group 
SampleCount_Summary <- SampleList_Info %>% 

  group_by(Sampling_Cat,
           ExperimentalUnit,
           ExperimentalGroup,
           Treatment,
           AnimalID, 
           SampleReason) %>% 
  summarize(Count = n_distinct(UrineNumber))
View(MissingSample)

```

#Missing sample

```{r All}

#How many of these samples are here at NPAC 
SampleCount_NPAC <- SampleList %>% 
  filter(!is.na(BoxID)) %>% 
  distinct(UrineNumber)
View(SampleCount_NPAC)
#649 samples 
#Thus almost 100 samples are missing.
#Send an email about this 


#How many samples are still missing after removal of the selected samples collected after packaging

```

```{r Summary}


#Count of sample missing by group 
MissingSample_Summary <- SampleList_Info %>% 
  
  #REMOVE MISSING SAMPLE 
  filter(is.na(BoxID)) %>% 
  
  #SUMMARIZE
  group_by(Sampling_Cat,
           ExperimentalUnit,
           ExperimentalGroup,
           Treatment,
           BS_Original,
           AnimalID, 
           SampleReason) %>%
  summarize(Count = n_distinct(UrineNumber)) %>% 
  
  arrange(ExperimentalUnit, 
          BS_Original,
          AnimalID,
          SampleReason) %>% 
  
  #PIVOT WIDER
  pivot_wider(names_from = SampleReason,values_from = Count, values_fill = 0) %>% 
  
  relocate(ExperimentalUnit) %>% 
  
  arrange(ExperimentalUnit) %>% 
  
  mutate(Total = Isolation + PostPair10 + PreEviction16 + PostEviction14 + RA + FirstConc)
View(MissingSample_Summary)

#When was blue moon started? why is there only 1 missing sample? ask Dave 


write.csv(MissingSample_Summary,"MissingSample_Summary_20240321.csv",row.names = FALSE)


```



