---
title: "Untitled"
output: html_document
date: "2024-02-06"
---

#Package

```{r}

library(tidyverse)

```


#General 

1) In firestone the breeding female ORF005 died when she gave birth (after she had evicted ORF018). 

After this the male DRM006 was used to found Kasteel. This has consequences for sample selection. 

```{r Data}

#Urine info 
DC_Info_Urine_F <- read.csv("DC_Info_Urine_F_20240214.csv") %>% 
  mutate(EvictionDate = ymd(EvictionDate,
         UrineDate = ymd(UrineDate)))
  
names(DC_Info_Urine_F )


#Current sample inventory _Inventory
Inventory <- 
```


#Sample lag 

Normally female should have been sampled approximately once a week during the experiment. 

SOF001 from Corbeau was not sampled for 46 days 
ORF017 from Wicklow was not sampled for 45 days
VGF002 from Wicklow was not sampled for 34 days 



```{r}

names(DC_Info_Urine_F)

SampleLag <- DC_Info_Urine_F %>%
  filter(UrinePairing_DayDiff >= 0, 
         EvictionStatus == "Evictee" & UrineEviction_DayDiff <= 10 | EvictionStatus %in% c("InGroup", "Evictor")) %>% 
  group_by(AnimalID) %>% 
  mutate(LagUrineDate = lag(UrineDate)) %>% 
  ungroup() %>% 
  mutate(LastSampleDelay = UrineDate - LagUrineDate) %>% 
  filter(!is.na(LastSampleDelay)) %>% 
  arrange(desc(LastSampleDelay))

View(SampleLag)


View((DC_Info_Urine_F) %>% 
       filter(ExperimentalGroup == "Corbeau"))

```





#Question 1: 

Determine differences between BF and NBF when there is no breeding opportunity and determine whether ovulation occurs 

Take 1 sample after two weeks 
Take last 2 samples before pairing 

3 samples per female = 156 samples 


```{r Isolation}
names(DC_Info_Urine_F)

#two weeks 
Isol_2W <- DC_Info_Urine_F %>% 
  filter(UrineIsol_DayDiff >= 14) %>% 
  group_by(AnimalID) %>% 
  slice_min(UrineIsol_DayDiff) %>% 
  ungroup()
View(Isol_2W)
#50 samples all good


#Pre-pairing
#In the worse case I could only get the last sample before pairing
Isol_PrePair <- DC_Info_Urine_F %>% 
  filter(UrinePairing_DayDiff <= 0) %>% 
  group_by(AnimalID) %>% 
  slice_max(UrineIsol_DayDiff, n=2) %>% 
  ungroup()
View(Isol_PrePair)

#Check for duplicates
View(Isol_PrePair %>% 
       group_by(AnimalID) %>% 
       mutate(Count = n_distinct(UrineNumber)) %>% 
       ungroup)
#ERF002 from Leffe has 2 samples on a given day, but one of them must be wrong because they have been collected almost at the same time. Check side label and only take the first and correct 

Sel_Isol <- bind_rows(Isol_2W,
                      Isol_PrePair)
View(Sel_Isol)
#150 samples

```


```{r Post paring}

#Samples that were collected on the day of eviction
#Have asked the project if they should be considered pre or post eviction
#For now I assume that they are pre-eviction
EvictionSample <- DC_Info_Urine_F %>% 
  filter(UrineEviction_DayDiff == 0)

write.csv(EvictionSample, "EvictionSample_ToCheck_20240215.csv", row.names = FALSE)
#Awaiting answer


#Post pairing samples 
Sel_PostPair <- DC_Info_Urine_F %>% 
  filter(UrinePairing_DayDiff > 0, 
         UrinePairing_DayDiff <= 10, 
         UrineEviction_DayDiff <= 0 | is.na(UrineEviction_DayDiff))
View(Sel_PostPair)
#149 samples


#Samples pre individuals 
PostPair_Count <- Sel_PostPair %>% 
  group_by(ExperimentalGroup, 
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(PostPair_Count)
#Between 1 and 6 samples per individual 


View(anti_join(DC_Info_F, PostPair_Count))
#The only sample that is missing is from Ashai where eviction occured on day 0

View(DC_Info_F)

```

Pre-Eviction samples not accounted for in post-pairing samples. I have opted for 16 days pre-pairing.

```{r Pre-Eviction }

#Pre-Eviction
Sel_PreEviction <- DC_Info_Urine_F %>%
  #REMOVE SAMPLES ALREADY COUNTED IN POST PAIRING
  filter(!UrineNumber %in% Sel_PostPair$UrineNumber) %>% 
  #FILTER
  filter(UrinePairing_DayDiff > 0, 
         UrineEviction_DayDiff <= 0,
         UrineEviction_DayDiff >= -16) # the number used here is mostly important for the slow eviction where sampling was not that frequent. 

View(PreEviction)
#10 days =  32 samples
#12 days = 34 samples
#14 days =  35 samples
#16 days =  42 samples between 2 and 6 samples per individual at the excpetion of SOF001 that has no samples
#18 days =  42 samples
#20 days =  44 samples


PreEviction_Count <- PreEviction %>% 
  group_by(Sampling_Cat,
           ExperimentalGroup,
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(PreEviction_Count)
#Samples from evictor SOF001 in Corbeau (Slow_Conc) are missing. I suspect it is because eviction occurred really late. Weirdly there is no samples between 184 and 230 days post pairing


#Ask the project to ask the reason 
SOF001 <- DC_Info_Urine_F %>% 
  filter(AnimalID == "SOF001")
write.csv(SOF001, "SOF001_Urine.csv", row.names = FALSE)


#View the samples gathered for slow eviction 
View(PreEviction %>% 
       filter(Sampling_Cat %in% c("Slow_Conc","Slow_PreFirst","Slow_None")) %>% 
       arrange(ExperimentalGroup, AnimalID))

```

No samples has been collected post-eviction yet so no need remove samples collected before

```{r Post eviction}

#First sample post eviction
PostEviction_1 <- DC_Info_Urine_F %>%
  #FILTER
  filter(UrineEviction_DayDiff > 0) %>% 
  group_by(AnimalID) %>% 
  slice_min(UrineEviction_DayDiff) %>% 
  ungroup()
View(PostEviction_1)
#All samples have been collected within 2 days of eviction 
#However, only 43 females meaning that 7 are missing 

#Animals that lack a post-eviction sample 
PostEviction_MissingID <- DC_Info_F %>% 
  select(ExperimentalGroup, 
         AnimalID, 
         BS_Original,
         EvictionStatus, 
         DeathDate,
         EvictionDate) %>% 
  left_join(., SamplingCat) %>% 
  relocate(Sampling_Cat) %>% 
  anti_join(.,PostEviction_1)
View(PostEviction_MissingID )
#Samples are missing from the 3 females where there has been no eviction 
#VGF002 is missing but it seems because she died on the day of eviction so normal there is no sample


#First sample after 7 days post eviction
#I could equally go for 10 days. Let's have a thought what is best
PostEviction_14 <- DC_Info_Urine_F %>%
  #FILTER
  filter(UrineEviction_DayDiff >= 14) %>% 
  group_by(AnimalID) %>% 
  slice_min(UrineEviction_DayDiff) %>% 
  ungroup()
View(PostEviction_14)
#All samples within 9 days except Darling brew wirth 13 and 15 days 
#42 individuals so one more missing as after 1 day 

Post14_Count <- PostEviction_14 %>% 
  group_by(Sampling_Cat,
           ExperimentalGroup,
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(Post14_Count )
  
Sel_PostEviction <- bind_rows(PostEviction_1, 
                              PostEviction_14)
View(Sel_PostEviction)

```



#Activation-Pregnancy samples

All samples collected between 100 days and 80 days to determine:

- Reproductive activation of some females
- hormone profile of early gestation. 
- Effect of presence of other female on gestation profile of early gestation


We are only missing sample of one gestation, evictor from Guiness where sampling seem to have been stopped before the first succesful conception

```{r First conception}

View(DC_Info_Urine_F)

#Are there evictee that gave birth within 100 days of eviction 
View(DC_Info_F %>% 
  filter(EvictionStatus == "Evictee"))

Sel_FirstConc <- DC_Info_Urine_F %>% 
  #REMOVE BITBURGER QUEEN THAT GOT PREGNANT AFTER EVICTION
  filter(AnimalID != "DRF004") %>% 
  #REMOVE SAMPLES POST-PAIRING  
  filter(!UrineNumber %in% Sel_PostPair$UrineNumber) %>% 
  #REMOVE SAMPLES PRE-EVICTION 
  filter(!UrineNumber %in% Sel_PreEviction$UrineNumber) %>% 
  #REMOVE SAMPLES POST-EVICTION
  filter(!UrineNumber %in% Sel_PostEviction$UrineNumber) %>% 
  #RETAIN FIRST LITTER 
  filter(NextLitter_IndCount_Colony == 1) %>%               
  #FILTER SAMPLES WITHIN TIME RANGE NEEDED 
  filter(NextParturition_ParturitionDayDiff >=- 100,
         NextParturition_ParturitionDayDiff <= -80)
View(Sel_FirstConc)
#146 samples 

#Count of samples
Sel_FirstConc_Count <- Sel_FirstConc %>% 
  group_by(Sampling_Cat,
           ExperimentalGroup,
           EvictionStatus,
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(Sel_FirstConc_Count)
#Seems that evictor from Guiness has no samples RRF008, no samples for almost 90 days around eviction 

View(DC_Info_F)

```


#Reproductive activation

All females that were evicted early did not successfully conceive in their group 

Rapid_Conc: 

- All samples of evictor are already covered 

- All samples of evictees are already covered for If a female has not activated before eviction she is unlikely to ovulate in the absence of a male. In the worse case we could select a few samples post eviction or before the end of the experiment 


Rapid_Pre: 

- For evictor, the date of activation could be anytime until the first successful conception. Take one sample every 21 days from paring until successful conception and then refine. 

- All samples of evictees are already covered for If a female has not activated before eviction she is unlikely to ovulate in the absence of a male. In the worse case we could select a few samples post eviction or before the end of the experiment 

Slow_Conc:

- For evictor and evictee, the date of activation could be anytime until the first successful conception. Take one sample every 21 days from paring until successful conception and then refine. 


Slow_Pre

- For evictor and evictee, the date of activation could be anytime until the first successful conception. Take one sample every 21 days from paring until successful conception and then refine.  

- For evictor one may wonder whether one wants to analyse past eviction if we think it is quite likely they activated before


No eviction

- all females gave birth. Take one sample every 21 days until conception and then refine.  


Keep in mind that I have all samples from 100 til 80 days pre-first parturition 
```{r}

names(DC_Info_Urine_F)

View(DC_Info_Urine_F)

View(DC_Info_F)
View(SamplingCat)

#retain samples until conception of first litter 
#Take one sample every three week and then refine
#retain samples of ORF017 that is the only evictor that had not succesfully conceived at the 

RA_Prep <- DC_Info_Urine_F %>%
  
  #RETAIN ALL SAMPLES BETWEEN PAIRING AND FIRST SUCCESSFULL CONCEPTION
      filter(UrinePairing_DayDiff > 0,
         UrineFirstConception_DayDiff <= 0 | AnimalID == "ORF017",  #because ORF017 in Wicklow has not succesfully conceived when samples were shipped
         AnimalID != "DRF004") %>%  #evictee from BitBurger that got preg after eviction
  
  #DIVIDE 21
  mutate(Div21 = as.integer(UrinePairing_DayDiff/21),
         Div21_1 = floor(Div21),
         Remainder21 = as.integer(UrinePairing_DayDiff) %% 21) %>% 
  
  #LAG 
  group_by(AnimalID) %>% 
  mutate(Lag = lag(Remainder21),
         Lag_UrineNumber = lag(UrineNumber)) %>% 
  ungroup()
View(RA_Prep)


RA_Prep2 <- RA_Prep %>% 
  
  #RETAIN ONLY FIRST SAMPLE OF EACH 21 DAYS PERIOD
  #it also show last sample of previous 21 days period 
  group_by(AnimalID, 
           Div21_1) %>% 
  slice_min(Remainder21) %>% 
  ungroup() %>% 
  
  #REMOVE FIRST PERIOD 
  #Because this is for teh first 21 days 
  filter(!Div21_1 == 0) %>% 
  
  #COMPUTE DIFFERENCE TO DECIDE WHETHER LAST OR FIRST SAMPLE OF PERIOD IS BETTER 
  mutate(Remainder21_Lag = abs(Lag - 21))
View(RA_Prep2)
#83 samples


#Check if all expected individuals are here 
View(RA_Prep2 %>% 
       distinct(Sampling_Cat,
                ExperimentalGroup,
                EvictionStatus,
                AnimalID) %>% 
       arrange(Sampling_Cat,
               ExperimentalGroup,
               EvictionStatus))


#Remove samples already done 
Sel_RA <- RA_Prep2 %>% 
  
  #REMOVE SAMPLES SELECTED BEFORE
  #does not change the number of samples
  #REMOVE SAMPLES POST-PAIRING  
  filter(!UrineNumber %in% Sel_PostPair$UrineNumber) %>% 
  #REMOVE SAMPLES PRE-EVICTION 
  filter(!UrineNumber %in% Sel_PreEviction$UrineNumber) %>% 
  #REMOVE SAMPLES POST-EVICTION
  filter(!UrineNumber %in% Sel_PostEviction$UrineNumber) %>% 
  #REMOVE SAMPLES FIRST CONC
  filter(!UrineNumber %in% Sel_FirstConc$UrineNumber)
View(Sel_RA)


#Count of samples
Sel_RA_Count <- Sel_RA %>% 
  group_by(Sampling_Cat,
           ExperimentalGroup,
           EvictionStatus,
           AnimalID) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(Sel_RA_Count)




```


#All Samples 

```{r All samples}

DC_Analyses <- bind_rows(Sel_Isol, # isolation
                         Sel_PostPair,
                         Sel_PreEviction,
                         Sel_PostEviction,
                         Sel_FirstConc,
                         Sel_RA)

View(DC_Analyses)

```



