---
title: "Untitled"
output: html_document
date: "2024-03-20"
---

#Samples to add on last batch? 

Run all individual graph before making a final decision

Conception: 

37269: MBF004(Bitburger) Rapid_PreFirst, day-78 pre first, since there is no sample that were collected between day -91 and day -78. 

RA



#package

```{r}

library(tidyverse)

```


#Data

I probably need to reupdate these two lists after my pc has done automatic update during the night of the 01 to 02 April 2024 and I am not sure the csv below refelct the latest version.

I guess not because I had made changes to the inventory after that and the date of the file correspond to the latest change 

```{r}

SampleList <- read.csv("SampleList_20240326.csv")
  
SampleList_Info <- read.csv("SampleList_Info_20240326.csv")

View(SampleList_Info %>% 
       distinct(UrineNumber,.keep_all = TRUE,
                BoxPosition))

#List of samples extracted so far
ExtractionList <- read.csv()

```


#Pre-Pairing samples 


##Step 1: Isolation samples 

```{r}

names(SampleList_Info)

#All isolation sample that should be analyzed
Isol <- SampleList_Info %>% 
  filter(SampleReason == "Isolation")
View(Isol)

levels(Isol$BS_Original)

#Check
View(Isol %>% 
       filter(UrinePairing_DayDiff >= 0))
#All Good


#Number of isolation samples present at the NPAC
#To get box and position to get samples out of the freezer 
Isol_FreezerOut <- Isol %>% 
  filter(!is.na(BoxID)) %>% 
  
  #ARRANGE
  arrange(BoxID,
          BoxPosition) %>% 
  
  select(AnimalID,
         UrineNumber,
         BoxID,
         BoxPosition) %>%
  
  #ADD NEW BOX 
  mutate(NewBox = case_when(
    row_number() <= 79 ~ 1,
    TRUE ~ 2)) %>% 
  
  #ADD NEW POSITION
   mutate(NewPosition = case_when(
    row_number() <= 79 ~ row_number() + 2,
    TRUE ~ row_number() - 79
  ))


#Write csv
write.csv(Isol_FreezerOut,"Isol_FreezerOut_20240321.csv",row.names = FALSE)


View(Isol_FreezerOut)
#127 samples are here in Neuchatel


#To place in correct sequence of extraction 
Isol_ExtractionSequ <- Isol %>% 
  #REMOVE SAMPLE ABSENT
  filter(!is.na(BoxID)) %>%
  #ARRANGE 
  #Wanted to avoid queen and helpers all being done one separate batch 
  #I accepted the risk of carry-over effect 
  arrange(ExperimentalUnit, #Ascending order of group
          BS_Original, #Helper First then queen
          AnimalID,
          UrineNumber) %>% 
  
  #SELECT 
  select(ExperimentalUnit,
         ExperimentalGroup,
         Treatment,
         AnimalID,
         BS_Original,
         UrineNumber) %>% 
  
  #JOIN TO BOX POSITION AFTER SAMPLES TAKEN OUT OF FREEZER
  #I take samples out of freezer in ascending order of box and position id
  left_join(.,Isol_FreezerOut %>% 
              select(UrineNumber,
                     NewBox,
                     NewPosition))

View(Isol_ExtractionSequ)

write.csv(Isol_ExtractionSequ,"Isol_ExtractionSequ_20240321.csv",row.names = FALSE)

```


##Step 2

Pre-isolation sample. Out of the 100 that should be available, There are 82 of them here at the NPAC, possibly because some have thawed and were not exported and possibly because some samples were not collected


Sample 36751 from TIF039 -16 days isolation seem to not have exported and instead 36757 was exported. I had made a mistake in the inventory assuming 36757 was 36751. I realized the mistake when extracting and I corrected the inventory the 1st April 2024.

I replaced 36751 sample with 36852 - days pre-isolation. 36751 will appear in the list returned below but NOT in the extraction list that I corrected manually

```{r}

names(SampleList_Info)

#All isolation sample that should be analyzed
PreIsol <- SampleList_Info %>% 
  filter(SampleReason %in% c("PreIsol1","PreIsol14"))
View(PreIsol)
#100 samples including duplicates


View(PreIsol %>% 
       distinct(UrineNumber))
#88 distinct urine which means that for 6 out of 50 animals the sample closest to isolation day and to day 14 are the same


#Check
View(PreIsol %>% 
       filter(UrineIsol_DayDiff > 0))
#All Good


#Number of preisolation samples present at the NPAC
#To get box and position to get samples out of the freezer 
PreIsol_FreezerOut <- PreIsol %>% 
  filter(!is.na(BoxID)) %>% 
  
  #ARRANGE
  arrange(BoxID,
          BoxPosition) %>% 
  
  select(AnimalID,
         SampleReason,
         UrineNumber,
         BoxID,
         BoxPosition) %>%
  
  #ADD NEW BOX 
  mutate(NewBox = case_when(
    row_number() <= 81 ~ 1,
    TRUE ~ 2)) %>% 
  
  #ADD NEW POSITION
   mutate(NewPosition = case_when(
    row_number() <= 81 ~ row_number(),
    TRUE ~ row_number() - 81
  ))
View(PreIsol_FreezerOut)
#82 samples 


#Write csv
#The list contains the duplicate
write.csv(PreIsol_FreezerOut,"PreIsol_FreezerOut_20240327.csv",row.names = FALSE)


View(PreIsol_FreezerOut %>% 
       distinct(UrineNumber))
#71 samples are here in Neuchatel and to be analyzed


#To place in correct sequence of extraction 
PreIsol_ExtractionSequ <- PreIsol %>% 
  
  #REMOVE SAMPLE ABSENT
  filter(!is.na(BoxID)) %>%
  
  distinct(UrineNumber,.keep_all = TRUE) %>% 
  
  #ARRANGE 
  #Wanted to avoid queen and helpers all being done one separate batch 
  #I accepted the risk of carry-over effect 
  arrange(ExperimentalUnit, #Ascending order of group
          BS_Original, #Helper First then queen
          AnimalID,
          UrineNumber) %>% 
  
  #SELECT 
  select(ExperimentalUnit,
         ExperimentalGroup,
         Treatment,
         AnimalID,
         BS_Original,
         UrineNumber) %>% 
  
  #JOIN TO BOX POSITION AFTER SAMPLES TAKEN OUT OF FREEZER
  #I take samples out of freezer in ascending order of box and position id
  left_join(.,PreIsol_FreezerOut %>% 
              select(UrineNumber,
                     NewBox,
                     NewPosition) %>% 
              group_by(UrineNumber) %>% 
              slice_min(NewPosition))

View(PreIsol_ExtractionSequ)


write.csv(PreIsol_ExtractionSequ,"PreIsol_ExtractionSequ_20240327.csv",row.names = FALSE)


```

#Post pairing samples 

```{r}

PostPairing <- SampleList_Info %>%
  
  #REMOVE PRE PAIRING SAMPLES
  #DAYDIFF = 0 WAS CONSIDERED ISOLATION
  filter(UrinePairing_DayDiff > 0)


#How many samples per sampling category
PostPairing_Count <- PostPairing %>% 
  group_by(Sampling_Cat) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(PostPairing_Count)


#How many samples available on site per category 
PostPairing_Count_NPAC <- PostPairing %>% 
  filter(!is.na(BoxPosition)) %>% 
  group_by(Sampling_Cat) %>% 
  summarize(Count = n_distinct(UrineNumber)) %>% 
  ungroup()
View(PostPairing_Count_NPAC)

```


##Step 3 

I will do the Rapid_Conc last as it will allow me to add the samples to increase time resolution of activation.


```{r Freezer Out}

#All post-pairing samples, except RapidConc
Eviction_RapidConc_Out <- PostPairing %>%
  
  #RETAIN ALL SAMPLING CAT EXCEPT RAPID CONC AND NONE 
  filter(Sampling_Cat %in% c("Rapid_PreFirst", "Slow_Conc", "Slow_PreFirst", "Slow_None")) %>% 
  
  droplevels() %>% 
  
  #ADD SAMPLE REASON COUNT 
  group_by(UrineNumber) %>% 
  mutate(ReasonCount = paste0("R",row_number())) %>% 
  ungroup() %>% 
  
  #PIVOT WIDER 
  pivot_wider(names_from = ReasonCount,values_from = SampleReason)

View(Eviction_RapidConc_Out)
#287 samples 


#Check
View(Eviction_RapidConc_Out %>% 
       filter(UrineIsol_DayDiff <= 0))
#All Good


#Number of preisolation samples present at the NPAC
#To get box and position to get samples out of the freezer 
RapidConc_Out_FreezerOut <- Eviction_RapidConc_Out %>% 
  
  #REMOVE SAMPLES NOT IN NEUCHATEL
  filter(!is.na(BoxID)) %>% 
  
  #ARRANGE
  arrange(BoxID,
          BoxPosition) %>% 
  
  #SELECT
  select(AnimalID,
         R1:R3,
         UrineNumber,
         BoxID,
         BoxPosition) %>% 
  
  arrange(BoxID,
          BoxPosition) %>%
  
  #ADD NEW BOX 
  mutate(NewBox = case_when(
    row_number() <= 81 ~ 1,
    row_number() > 81 & row_number() < 163 ~ 2,
    TRUE ~ 3)) %>% 
  
  #ADD NEW POSITION
   mutate(NewPosition = case_when(
    row_number() <= 81 ~ row_number(),
    row_number() > 81 & row_number() < 163 ~ row_number() - 81,
    TRUE ~ row_number() - 162
  ))


View(RapidConc_Out_FreezerOut)
#258 unique samples


#Write csv
#The list contains the duplicate
write.csv(RapidConc_Out_FreezerOut,"RapidConc_Out_FreezerOut_ToPrint_20240402.csv",row.names = FALSE)

```


Only retain relevant columns

```{r Relevant columns}

#To place in correct sequence of extraction 
Eviction_RapidConc_Out_RelCol <- Eviction_RapidConc_Out %>% 
  
  #REMOVE SAMPLES NOT IN NEUCHATEL
  filter(!is.na(BoxID)) %>% 
  
  #SELECT 
  select(Sampling_Cat,
         ExperimentalUnit,
         ExperimentalGroup,
         Treatment,
         AnimalID,
         BS_Original,
         EvictionStatus,
         UrinePairing_DayDiff,
         UrineParturition_DayDiff,
         R1:R3,
         UrineNumber) %>% 
  
  #JOIN TO BOX POSITION AFTER SAMPLES TAKEN OUT OF FREEZER
  #I take samples out of freezer in ascending order of box and position id
  left_join(.,RapidConc_Out_FreezerOut %>% 
              select(UrineNumber,
                     NewBox,
                     NewPosition)) %>% 
  
  #ADD EXTRACTION VOLUME
  mutate(Vol = case_when(UrineParturition_DayDiff >= -90 & UrineParturition_DayDiff < 0 ~ 50, 
                         TRUE ~ 100))

View(Eviction_RapidConc_Out_RelCol)


```


##Rapid_PreFirst 

MISSING SAMPLES: 

SOFOO6 (Firestone): first conception sample as she died when she gave birth and did not have LitterInfo on which filter for selection was applied. Thus were not returned in selection due to the code

1) 34171
2) 34256
3) 34348 

Info will have to be added manually in the relevant table that lead to litter Info

MBF004 (Bitburger) evictor has no sample between 91 and 78 days pre first. Sample 37269 could be added on last batch (d-78)


```{r Rapid_Pre Sequence}

#To check visually
Rapid_Pre_Check <- Eviction_RapidConc_Out_RelCol %>% 
  filter(Sampling_Cat == "Rapid_PreFirst") %>% 
  arrange(ExperimentalUnit,
          EvictionStatus,
          UrineNumber)
View(Rapid_Pre_Check)

#CSV
write.csv(Rapid_Pre_Check,"Rapid_Pre_Check_20240401.csv",row.names = FALSE)


#Organize Extraction Sequence
Rapid_Pre_ExtractionSequ <- Eviction_RapidConc_Out_RelCol %>% 
  filter(Sampling_Cat == "Rapid_PreFirst") %>% 
  arrange(desc(EvictionStatus), #Evictee first as they are unlikely to have high E2 and P4 levels
          ExperimentalUnit,
          UrineNumber)

View(Rapid_Pre_ExtractionSequ)
#52 samples


write.csv(Rapid_Pre_ExtractionSequ,"Rapid_Pre_ExtractionSequ_20240402.csv",row.names = FALSE)

```


```{r Slow_Conc Sequence}

#To check visually
Slow_Conc_Check <- Eviction_RapidConc_Out_RelCol %>% 
  filter(Sampling_Cat == "Slow_Conc") %>% 
  arrange(ExperimentalUnit,
          EvictionStatus,
          UrineNumber)
View(Slow_Conc_Check)

#CSV
write.csv(Slow_Conc_Check,"Slow_Conc_Check_20240401.csv",row.names = FALSE)


#Organize Extraction Sequence
#Perhaps will need to organize differently on batch 
Slow_Conc_ExtractionSequ <- Eviction_RapidConc_Out_RelCol %>% 
  filter(Sampling_Cat == "Slow_Conc") %>% 
  arrange(desc(EvictionStatus), #Evictee first as they are unlikely to have high E2 and P4 levels
          ExperimentalUnit,
          UrineNumber)

View(Slow_Conc_ExtractionSequ)
#52 samples


write.csv(Slow_Conc_ExtractionSequ,"Slow_Conc_ExtractionSequ_20240402.csv",row.names = FALSE)

```

