---
title: "Untitled"
output: html_document
date: '2023-04-03'
editor_options: 
  chunk_output_type: console
---

#General 

1) Whenever relevant, do I need to get samples up to -88d or shall I take a slightly longer period? Til D85? D80? always get a few pregnant sample? Perhaps would be good to consistently go through a few pregnancy samples.


#Data from Prep

```{r Import}

#DC_Info_F 
#CSV available


#Urine samples
#DC_Urine_F CSV available


```

The next part could be moved in data prep as I can use it for interesting plotting

##Group Info 

```{r DataPrep}

#Group Info
GroupInfo <- DC_Info_Group %>% 
  
  #RELEVANT GROUP INFO
  select(ExperimentalGroup,
         Treatment,
         EvictionStatus_Group,
         BreederCount,
         CoBreeding,
         IsolationDate,
         PairingDate,
         EvictionDate,
         EvictionPairingDayDiff,
         EvictionCategory) %>% 
  arrange(Treatment,
          EvictionStatus_Group,
          EvictionPairingDayDiff)
View(GroupInfo)


#Evictor Info
#Must add original BS Status
EvictorInfo <- DC_Info_F %>% 
  arrange(Treatment,
          ExperimentalGroup,
          EvictionStatus) %>% 
  group_by(ExperimentalGroup) %>% 
  slice(1) %>% 
  ungroup() %>% 
  
  left_join(.,DC_Dates_F_GestStat %>% 
              filter(DateType == "Eviction"), 
            by=c("AnimalID" = "AnimalID", "EvictionDate" = "Date")) %>%
  
  select(ExperimentalGroup,
         AnimalID,
         BS_Original,
         EvictionDate,
         EvictionPairingDayDiff,
         ConceptionPairingDayDiff,
         ConceptionEvictionDayDiff,
         ParturitionEvictionDayDiff,
         GestationStatus_Trimester) %>% 
  
  #RENAME
  rename(EvictorID = AnimalID,
         Evictor_BSOriginal = BS_Original,
         Evictor_ConceptionPairingDayDiff =  ConceptionPairingDayDiff,
         Evictor_ConceptionEvictionDayDiff = ConceptionEvictionDayDiff,
         Evictor_ParturitionEvictionDayDiff =ParturitionEvictionDayDiff,
         Evictor_GestationStatus = GestationStatus_Trimester)
View(EvictorInfo )


#Evictee Info 
#Must add original BS Status
EvicteeInfo <- DC_Info_F %>% 
  filter(!(AnimalID %in% EvictorInfo$EvictorID)) %>%
  
  #ADD GESTATION STATUS
  left_join(.,DC_Dates_F_GestStat %>% 
              filter(DateType == "Eviction"), 
            by=c("AnimalID" = "AnimalID", "EvictionDate" = "Date")) %>%
  
  #SELECT
  select(ExperimentalGroup,
         AnimalID,
         BS_Original,
         EvictionDate,
         ConceptionPairingDayDiff,
         ConceptionEvictionDayDiff,
         ParturitionEvictionDayDiff,
         GestationStatus_Trimester) %>%
  
  #RENAME
  rename(EvicteeID = AnimalID,
         Evictee_BSOriginal = BS_Original,
         Evictee_ConceptionPairingDayDiff =  ConceptionPairingDayDiff,
         Evictee_ConceptionEvictionDayDiff = ConceptionEvictionDayDiff,
         Evictee_ParturitionEvictionDayDiff =ParturitionEvictionDayDiff,
         Evictee_GestationStatus = GestationStatus_Trimester)

names(GroupInfo)

#Merge group and individual info 
EvictionInfo <- GroupInfo %>% 
  
  #RELEVANT EVICTOR INFO 
  left_join(.,EvictorInfo) %>% 
  
  #RELEVANT EVICTEE INFO 
  left_join(., EvicteeInfo) %>% 
  
  #RELOCATE
  relocate(EvicteeID, .after = EvictorID) %>% 
  
  relocate(Evictee_BSOriginal, .after = Evictor_BSOriginal) %>% 
  
  relocate(Evictee_ConceptionPairingDayDiff,.after = Evictor_ConceptionPairingDayDiff) %>% 

  relocate(Evictee_ConceptionEvictionDayDiff, .after = Evictor_ConceptionEvictionDayDiff) %>% 
  
  relocate(Evictee_ParturitionEvictionDayDiff, .after = Evictor_ParturitionEvictionDayDiff) %>% 
  
  relocate(Evictee_GestationStatus,.after = Evictor_GestationStatus)
  

View(EvictionInfo)
View(DC_Info_F)
#Must manually assign a parturition date to SOF006 in Firestone on the 20/12/2023

#For Corbeau ARF028 produced two litters before being evicted, delays are calculated with first conception and parturition, is that an issue? Keep in mind she was evicted the day she gave birth to second litter 

write.csv(EvictionInfo,"EvictionInfo_20230205.csv",row.names = FALSE)

  
```

```{r Eviction Type}


#Early eviction
EarlyEviction <- DC_Info_F %>% 
  filter(EvictionPairingDayDiff <= 21)
View(EarlyEviction)
#14 groups


#Late eviction
LateEviction <- DC_Info_F %>% 
  filter(EvictionPairingDayDiff > 21)
#4 groups 
  

#Late or no eviction
LateOrNoEviction <- DC_Info_F %>% 
  filter(EvictionPairingDayDiff > 21 | is.na(EvictionDate))
View(LateOrNoEviction)
#7 groups

#NoEviction
NoEviction <- DC_Info_F %>% 
  filter(is.na(EvictionDate))
View(NoEviction)
#3 groups


```


```{r Gestation status}

##################################################Early eviction 
#Q1)Predictor of eviction 
#Q2) When did the evictor activate
#Q3) Did the evictee activate
#Q4) if yes to 3) When did the evictee activate? 
#Q5


#Category 1
#Early evictor that conceived around eviction
#7 groups could be up to 4 more
EarlyOr_Conc <- EvictionInfo %>% 
       filter(Evictor_GestationStatus == "Conception",
              EvictionCategory == "Early")
View(EarlyOr_Conc)
#Eviction between 1 and 5 days post-pairing 
#Eviction between 100 and 91 pre-parturition => Activation within 12 days of eviction



#Category 2
#Early evictor that succesfully conceived long after eviction
#3 groups; could be up to 4 more
EarlyOr_PreFirst <- EvictionInfo %>% 
       filter(Evictor_GestationStatus == "PreFirstConception" & 
              EvictionCategory == "Early" | 
                ExperimentalGroup == "Firestone")
View(EarlyOr_PreFirst)
#did they activate shortly after eviction like in category 1 or just before conception


#Too early to tell 
#4 groups
#will fall into 1 or 2
EarlyOr_TooEarly <- EvictionInfo %>% 
       filter(Evictor_GestationStatus == "NotPregnant",
              EvictionCategory == "Early",
              ExperimentalGroup != "Firestone")
View(EarlyOr_TooEarly)
#Eviction occurred between 1 and 5 days 



##################################################Late eviction
#Category 3
LateOr_Conc <- EvictionInfo %>% 
       filter(Evictor_GestationStatus == "Conception",
              EvictionCategory == "Late")
View(LateOr_Conc )




LateOr_PreFirst <- EvictionInfo %>% 
       filter(Evictor_GestationStatus == "NotPregnant",
              EvictionCategory == "Late")
View(LateOr_PreFirst)





#All Evictor that conceived at eviction
Or_Conc <- EvictionInfo %>% 
       filter(Evictor_GestationStatus == "Conception") %>% 
  arrange(Treatment, 
          EvictionPairingDayDiff)
View(Or_Conc)




#Early evictor that did not conceive
EarlyOr_NoConc <- EvictionInfo %>% 
       filter(!Evictor_GestationStatus == "Conception",
              EvictionCategory == "Early") %>% 
    arrange(Treatment, 
          EvictionPairingDayDiff)
View(EarlyOr_NoConc)


###############################################Sub treatment 

#ST Evictor conception
View(EvictionInfo %>% 
       filter(Treatment == "Sub",
              Evictor_GestationStatus == "Conception"))

#ST Evictor not pregnant
View(EvictionInfo %>% 
       filter(Treatment == "Sub",
              Evictor_GestationStatus == "NotPregnant"))
#Two of them could be pregnant and thus fall in the category conception
#Firestone should be in Pre-First conception as she died giving birth and there was no DOB recorded

#ST Evictor Pre-firstConception
View(EvictionInfo %>% 
       filter(Treatment == "Sub",
              Evictor_GestationStatus == "PreFirstConception"))
#Two of them could be pregnant and thus fall in the category conception


###############################################Queen treatment

#QT Early Evictor Conception
View(EvictionInfo %>% 
       filter(Treatment == "Queen",
              Evictor_GestationStatus == "Conception",
              EvictionTime == "Early"))

#QT Late Evictor Conception
View(EvictionInfo %>% 
       filter(Treatment == "Queen",
              Evictor_GestationStatus == "Conception",
              EvictionTime == "Late"))


#QT Early Evictor NotPreg
View(EvictionInfo %>% 
       filter(Treatment == "Queen",
              Evictor_GestationStatus == "NotPregnant",
               EvictionTime == "Early"))
#Two of them could be pregnant and thus fall in the category conception


#QT Late Evictor NotPreg
View(EvictionInfo %>% 
       filter(Treatment == "Queen",
              Evictor_GestationStatus == "NotPregnant",
               EvictionTime == "Late"))


#QT Early Evictor PreFirstConception 
View(EvictionInfo %>% 
       filter(Treatment == "Queen",
              Evictor_GestationStatus == "PreFirstConception",
               EvictionTime == "Early"))

#QT Late Evictor PreFirstConception 
View(EvictionInfo %>% 
       filter(Treatment == "Queen",
              Evictor_GestationStatus == "PreFirstConception",
               EvictionTime == "Late"))


```

Try to plot information on reproductive stage of evictor and evictee. Should be moved into data exploration. Valid for  

```{r Plot gestation status}

#Data to plot
GestationInfo_ToPlot <- EvictionInfo %>% 
  select(ExperimentalGroup,
              EvictionTime,
              Treatment,
              Evictor_BSOriginal,
              Evictee_BSOriginal,
              EvictionStatus_Group,
              Evictor_GestationStatus,
              Evictee_GestationStatus,
              BreederCount) %>% 
  mutate(Evictor_GestationStatus = case_when(Evictor_GestationStatus == "Conception" ~ "Conc",
                                             Evictor_GestationStatus == "NotPregnant" ~ "NotPreg", 
                                             Evictor_GestationStatus == "PreFirstConception" ~ "PreFirstConc")) %>% 
  filter(!is.na(Evictor_GestationStatus))
View(GestationInfo_ToPlot)



#All data
ggplot(GestationInfo_ToPlot,
       aes(x=Evictor_GestationStatus,fill=Evictee_GestationStatus)) + 
  
  geom_bar() +
  
  facet_grid(Treatment ~ EvictionTime) +

  theme_classic()


#Sub ecictor data 
ggplot(GestationInfo_ToPlot %>% 
         filter(Evictor_BSOriginal == "Helper"),
       aes(x=Evictor_GestationStatus,fill=Evictee_GestationStatus)) + 
  
  geom_bar() +
  
  facet_grid(Treatment ~ EvictionTime) +

  theme_classic()


# #Queen evictor
# ggplot(GestationInfo_ToPlot %>% 
#          filter(Evictor_BSOriginal == "Breeder"),
#        aes(x=Evictor_GestationStatus,fill=Evictee_GestationStatus)) + 
#   
#   geom_bar() +
#   
#   facet_grid(Treatment ~ EvictionTime) +
# 
#   theme_classic()

```

#Urine selection 

Strictly speaking, only this part should stay in the current code

At the moment, we will only select sample from females

##Data 

```{r Pre-isol}

#All pre-isolation 
Urine_PreIsol <- 
  
  #URINE
  DC_Info_Urine_F %>% 
  
  #RETAIN PRIOR TO ISOLATION 
  filter(UrineDate <= IsolationDate) %>%
  
  #ADD ISOLATION DAY DIFF 
  mutate(IsolationDayDiff = UrineDate - IsolationDate) %>% 
  
  #RETAN FIRST SAMPLE 
  group_by(AnimalID,
           UrineDate) %>% 
  slice_min(UrineNumber) %>% 
  ungroup() %>% 

  
  #ARRANGE 
  arrange(Treatment, 
          ExperimentalGroup,
          UrineDate, 
          AnimalID) %>% 
  
  #DISTINCT
  distinct()
View(Urine_PreIsol)
#351 samples preisolation 

```


```{r Isol}

#Isolation sample 
Urine_Isol <-   DC_Info_Urine_F %>% 
  
  filter(UrineDate > IsolationDate & UrineDate <= PairingDate) %>% 
  
  #ADD ISOLATION DIFF 
  mutate(IsolationDayDiff = UrineDate - IsolationDate) %>% 
  
  #ADD PAIRING DIFF 
  mutate(PairingDayDiff = UrineDate - PairingDate) %>%
  
  #RETAN FIRST SAMPLE 
  group_by(AnimalID,
           UrineDate) %>% 
  slice_min(UrineNumber) %>% 
  ungroup() %>% 

  
  #ADD COUNT SAMPLE 
  group_by(AnimalID) %>% 
  mutate(Count = n_distinct(UrineDate)) %>% 
  ungroup() %>% 
  
  #ARRANGE
  arrange(Treatment,
          ExperimentalGroup,
          AnimalID,
          UrineDate) %>% 
  
  #DISTINCT
  distinct()
  

View(Urine_Isol )
#363 samples

names(DC_Info_Urine_F)

```

```{r Post-pairing}

names(DC_Info_Urine_F )

Urine_PostPairing <- DC_Info_Urine_F  %>% 
  
  #RETAIN POST PAIRING
  filter(UrineDate > PairingDate) %>% 
  
  #ADD PAIRING DIFF 
  mutate(PairingDayDiff = UrineDate - PairingDate) %>% 
  
  #ADD EVICTION DIFF 
  mutate(EvictionDayDiff = UrineDate - EvictionDate) %>% 
  
  #ADD PARTURITION DIFFF 
  mutate(ParturitionDayDiff = UrineDate - NextParturition_ParturitionDate) %>% 

  #ADD IN GROUP OR NOT 
  mutate(InGroup = case_when(EvictionStatus == "Evictee" & EvictionDayDiff >= 0 ~ "No",
                             TRUE ~ "Yes")) %>% 
  
    #RETAN FIRST SAMPLE 
  group_by(AnimalID,
           UrineDate) %>% 
  slice_min(UrineNumber) %>% 
  ungroup() %>% 
  
    #DISTINCT
  distinct()

names(Urine_PostPairing)
#1191 samples
```


#Hormonal correlates of dominance and eviction


Select:
i) last two samples before pairing as baseline
ii) All samples within 10 days of pairing
iii) All samples within 10 days of eviction


```{r Baseline}

#Samples within two weeks of pairing
#Seems that there is a lot of variation
#ask to the project 
Urine_PreIsol_2W <- Urine_PreIsol %>% 
  
  #RETAIN SAMPLES LAST 2 WEEKS PRIOR ISOL
  filter(IsolationDayDiff >= -14) %>% 
  
  #SELECT 
  select(Treatment,
         ExperimentalGroup,
         AnimalID,
         BS_Original,
         EvictionStatus,
         IsolationDayDiff,
         UrineDate,
         UrineNumber) %>% 
  
  #ARRANGE 
  arrange(Treatment, 
          ExperimentalGroup,
          IsolationDayDiff, 
          AnimalID) %>% 
  
  distinct()
View(Urine_PreIsol_2W)

write.csv(Urine_PreIsol_Formatted,"DC_Urine_PreIsol.csv",row.names = FALSE)


#Summary
Urine_PreIsol_Summary <- Urine_PreIsol_2W %>%
  
  #ADD COUNT 
  group_by(ExperimentalGroup,
           AnimalID,
           BS_Original,
           Treatment) %>% 
  summarize(Count = n_distinct(UrineDate)) %>% 
  ungroup() %>% 
  arrange(Treatment,
          Count,
          BS_Original)
View(Urine_PreIsol_Summary)
#In the sub treatment, 5/10 groups that only have one sample 
#In the queen treatment 4/11 groups have only one sample

write.csv(Urine_PreIsol_Summary,"DC_Urine_PreIsol_Count.csv",row.names = FALSE)


#Selection
#Can be moved elsewhere
Urine_PrePair_Baseline <- Urine_PreIsol_2W %>% 
  
  #RETAIN 2 LATEST SAMPLES
  group_by(AnimalID) %>% 
  slice_max(UrineDate, n=2) %>%
  mutate(Count = n()) %>% 
  ungroup() %>% 
  
  #ARRANGE
  arrange(Treatment,
          ExperimentalGroup,
          AnimalID,
          UrineNumber)
View(Urine_PrePair_Baseline)

```

I should think, double check whether 10 days is a good number of days.

```{r post-pairing 10}

#Samples within 10 days post-pairing and prior to eviction
Urine_PostPairing10 <- Urine_PostPairing %>% 
  filter(PairingDayDiff <= 10,
         EvictionDayDiff <= 0|is.na(EvictionDayDiff)) %>% 
  #SELECT 
  select(ExperimentalGroup,
         Treatment,
         EvictionCategory,
         AnimalID,
         BS_Original,
         EvictionStatus,
         PairingDayDiff,
         EvictionDayDiff,
         UrineDate,
         UrineNumber) %>% 
  
  #ARRANGE
  arrange(Treatment,
          ExperimentalGroup,
          BS_Original,
          AnimalID,
          UrineNumber)
  
View(Urine_PostPairing10)
#125 samples


#Summary
View(Urine_PostPairing10 %>% 
       group_by(EvictionCategory, 
                ExperimentalGroup,
                EvictionPairingDayDiff,
                AnimalID,
                EvictionStatus) %>% 
       summarize(Count = n()))


```



```{r pre-eviction 16}
#would it be better 14 days before?

#Samples within 16 days post-pairing and prior to eviction
Urine_PreEviction16 <- Urine_PostPairing %>%
  
  #SAMPLES TIL 16 DAYS PRE-EVICTION
  filter(EvictionDayDiff <= 0,
         EvictionDayDiff >= -16) %>% 
  
  #REMOVE SAMPLES IN POST PAIRING 10
  filter(!UrineNumber %in% Urine_PostPairing10$UrineNumber) %>% 
  
  #SELECT 
  select(ExperimentalGroup,
         Treatment,
         EvictionCategory,
         AnimalID,
         BS_Original,
         EvictionStatus,
         PairingDayDiff,
         EvictionDayDiff,
         UrineDate,
         UrineNumber) %>% 
  
    
  #ARRANGE
  arrange(Treatment,
          ExperimentalGroup,
          BS_Original,
          AnimalID,
          UrineNumber)
View(Urine_PreEviction16)
#25 samples if 10 days 
#29 samples if 15 days
#32 samples if 16 days


#Summary
View(Urine_PreEviction10 %>% 
       group_by(EvictionCategory, 
                ExperimentalGroup,
                AnimalID,
                EvictionStatus) %>% 
       summarize(Count = n()))
#No sample on Corbeau evictor
#More sample on evictee in Licher and Guiness why


#Coverage for late eviction 
#Protocol says sample should be collected every 2 days til 21 days, then every week
View(Urine_PreEviction10 %>% 
       filter(ExperimentalGroup %in% c("Licher","BlackLabel","Corbeau","Guinness")))

View(DC_Info_F)


```

#Sampling categories 

```{r Category}

Cat1 <- Urine_PostPairing %>% 
  #EARLY - CONCEPTION 
  filter(EvictionCategory == "Early",
         Eviction_GS == "Conception") %>% 

  #DISTINCT 
  distinct(ExperimentalGroup)


Cat2 <- 

  
Cat3 <- Urine_PostPairing %>% 
  #LATE - CONCEPTION
  filter(EvictionCategory == "Late" & 
         Eviction_GS == "Conception") %>% 
  
  #DISTINCT 
  distinct(ExperimentalGroup)

Cat4 <- Urine_PostPairing %>% 
    
  #SAMPLES FROM CAT 4
  filter(EvictionCategory == "Late" & 
         is.na(Eviction_GS)) %>% 
  
  #DISTINCT 
  distinct(ExperimentalGroup)

```



#Rerproductive physiology of evictor

##Reproductive state at eviction

For category 1 we will use all samples til -88 pre-parturition and not included in earlier selection.

```{r Category 1}

RSRA_Or_Cat1 <- Urine_PostPairing %>% 
  
  #SAMPLES FROM CAT 1
  filter(EvictionCategory == "Early",
         Eviction_GS == "Conception") %>% 
  
  #EVICTOR
  filter(EvictionStatus == "Evictor") %>% 
  
  #RETAIN SAMPLES TIL 87 DAYS (SAMPLE EVERY 2 DAYS) %>% 
  filter(FirstDCParturitionDate == NextParturition_ParturitionDate,
         ParturitionDayDiff <= -87) %>% 
  
  #REMOVE SAMPLES IN POST PAIRING 10
  filter(!UrineNumber %in% Urine_PostPairing10$UrineNumber) %>% 
  
  #REMOVE SAMPLES IN PRE EVICTION 10
  filter(!UrineNumber %in% Urine_PreEviction10$UrineNumber)
View(RS_Or_Cat1)


#Add 2 gestation samples per female

```

For category 2, we will use all samples from 10 days prior to eviction til 16 days post-eviction that are not included in earlier selection. Data shows that females from category 1 conceived between 3 and 12 days of eviction so I chose a duration that was slightly longer to be on the safe side

```{r Category 2}

RS_Or_Cat2 <- Urine_PostPairing %>% 
  
  #SAMPLES FROM CAT 1
  filter(EvictionCategory == "Early" & 
         Eviction_GS == "PreFirstConception" |
           ExperimentalGroup == "Firestone") %>% 
  
  #EVICTOR
  filter(EvictionStatus == "Evictor") %>% 
  
  #RETAIN SAMPLES TIL 16 DAYS POST EVICTION %>% 
  filter(EvictionDayDiff <= 16) %>% 
  
  #REMOVE SAMPLES IN POST PAIRING 10
  filter(!UrineNumber %in% Urine_PostPairing10$UrineNumber) %>% 
  
  #REMOVE SAMPLES IN PRE EVICTION 10
  filter(!UrineNumber %in% Urine_PreEviction10$UrineNumber)
View(RS_Or_Cat2)
#Coverage is not great for DarlingBrew
#Make sure post eviction that samples are collected for evictor as for evictee


```

For category 3, we will use all samples from 10 days before eviction til 87 days prior to first parturition that are not included in earlier selection.

```{r Category 3}

RS_Or_Cat3 <- Urine_PostPairing %>% 
  
  #SAMPLES FROM CAT 1
  filter(EvictionCategory == "Late" & 
         Eviction_GS == "Conception") %>% 
  
  #EVICTOR
  filter(EvictionStatus == "Evictor") %>% 
  
  #RETAIN SAMPLES TIL 14 DAYS POST EVICTION %>% 
  filter(EvictionDayDiff >= - 10,
         EvictionDayDiff <= 16,
         ParturitionDayDiff <= -87) %>% 
  
  #REMOVE SAMPLES IN POST PAIRING 10
  filter(!UrineNumber %in% Urine_PostPairing10$UrineNumber) %>% 
  
  #REMOVE SAMPLES IN PRE EVICTION 10
  filter(!UrineNumber %in% Urine_PreEviction10$UrineNumber)

View(RS_Or_Cat3)
#7 samples
#The coverage is quite good but it would be interesting to see whether the ccoverage is good pre-eviction
View(Urine_PreEviction10 %>% 
filter(AnimalID %in% RS_Or_Cat3$AnimalID))
#Licher is missing the sample at day -1 as should have been taken


#Licher
View(RS_Or_Cat3 %>% 
       filter(ExperimentalGroup == "Licher"))


#Black label
View(RS_Or_Cat3 %>% 
       filter(ExperimentalGroup == "BlackLabel"))
```


For category 4, we will use all samples from 16 days before eviction til 16 post eviction that are not included in earlier selection 

```{r Category 4}

RS_Or_Cat4 <- Urine_PostPairing %>% 
  
  #SAMPLES FROM CAT 4
  filter(EvictionCategory == "Late" & 
         is.na(Eviction_GS)) %>% #Once they will have gotten pregnant, the code will have to be changed to "PreFirstConception", I should have Corbeau and Guiness there
  
  #EVICTOR
  filter(EvictionStatus == "Evictor") %>% 
  
  #SAMPLES FROM DAY -16 PRE TIL 16 DAYS POST-EVICTION
  filter(EvictionDayDiff >= -16,
         EvictionDayDiff <= 16) %>% 
  
  #REMOVE SAMPLES IN PRE EVICTION 16
  filter(!UrineNumber %in% Urine_PreEviction16$UrineNumber) %>% 
  
  #REMOVE SAMPLES IN POST PAIRING 16
  filter(!UrineNumber %in% Urine_PostPairing10$UrineNumber)
View(RS_Or_Cat4)

```



##Timing of reproductive activation

For Category 1, it is covered by RS at eviction

```{r Category 1}

```


For category 2, it could be that reproductive activation does occur after more than 14 days post-eviction. Thus I could analyse one additional sample every two weeks, plus narrowing down 

```{r Category 2}

RT_Or_Cat2 <- Urine_PostPairing %>% 
  
  #SAMPLES FROM CAT 1
  filter(EvictionCategory == "Early" & 
         Eviction_GS == "PreFirstConception" |
           ExperimentalGroup == "Firestone") %>% 
  
  #EVICTOR
  filter(EvictionStatus == "Evictor") %>% 
  
  #REMOVE SAMPLES IN POST PAIRING 10
  filter(!UrineNumber %in% Urine_PostPairing10$UrineNumber) %>% 
  
  #REMOVE SAMPLES IN PRE EVICTION 10
  filter(!UrineNumber %in% Urine_PreEviction10$UrineNumber) %>% 
  
  #REMOVE SAMPLES IN POST EVICTION 14
  filter(!UrineNumber %in% RS_Or_Cat2$UrineNumber) %>% 
  
  #TAKE SAMPLES TIL -88 DAYS
  #Would I need take one sample after?
  filter(ExperimentalGroup != "Firestone" & ParturitionDayDiff <= -87 &
         UrineDate < FirstDCParturitionDate | 
           ExperimentalGroup == "Firestone" & UrineDate <= "2022-09-23")

#Chouffe
#1 sample/week
View(RT_Or_Cat2 %>% 
       filter(ExperimentalGroup == "Chouffe"))

#Darling
#1 sample/week
View(RT_Or_Cat2 %>% 
       filter(ExperimentalGroup == "DarlingBrew"))
#2 samples

#Firestone
#1 sample/week
View(RT_Or_Cat2 %>% 
       filter(ExperimentalGroup == "Firestone"))
#13 samples


View(DC_Info_F)
```


For category 3, RA can occur anywhere between pairing date and eviction and it is possible that RA does occur earlier than 10 days pre-eviction. Thus, I will analyse one additional sample every two weeks from post-pairing D10 until pre-eviction D-10, then narrow down to highest resolution

```{r Category 3}

RT_Or_Cat3 <- Urine_PostPairing %>% 
  
  #SAMPLES FROM CAT 3
  filter(EvictionCategory == "Late" & 
         Eviction_GS == "Conception") %>% 
  
  #EVICTOR
  filter(EvictionStatus == "Evictor") %>% 
  
  #PRE-EVICTION SAMPLE 
  filter(EvictionDayDiff<=0) %>% 
  
  #REMOVE SAMPLES IN POST PAIRING 10
  filter(!UrineNumber %in% Urine_PostPairing10$UrineNumber) %>% 
  
  #REMOVE SAMPLES IN PRE EVICTION 10
  filter(!UrineNumber %in% Urine_PreEviction10$UrineNumber) %>% 
  
  #REMOVE SAMPLES IN POST EVICTION 14
  filter(!UrineNumber %in% RS_Or_Cat2$UrineNumber)

#Licher
View(RT_Or_Cat3 %>% 
       filter(ExperimentalGroup == "Licher"))
#5 samples to be analysed


#Black label
View(RT_Or_Cat3 %>% 
       filter(ExperimentalGroup == "BlackLabel"))
#10 amples to be analyzed
```


For category 4, RA can occur anywhere between pairing date and -88 days pre-parturition. It is possible that RA does occur earlier than 16 days pre-eviction or more than 16 days after eviction. 

I will analyse one additional sample every two weeks from post-pairing D10 until pre-eviction D-16, then narrow down to highest resolution. 

If RA has not been detected yet, I will extend analyses from D16 post eviction until first succesful conception. 

At the time of coding the succesful conception date has not been established because evictor had not given birth yet

```{r Category 4}

RT_Or_Cat4_Pre <- Urine_PostPairing %>% 
    
  #SAMPLES FROM CAT 4
  filter(EvictionCategory == "Late" & 
         is.na(Eviction_GS)) %>% #Once they will have gotten pregnant, the code will have to be changed to "PreFirstConception", I should have Corbeau and Guiness there
  
  #EVICTOR
  filter(EvictionStatus == "Evictor") %>% 
  
  #POST PAIRING AND PRE EVICTION SAMPLES
  filter(PairingDayDiff >= 0,
         EvictionDayDiff <= 0) %>% 

  #REMOVE SAMPLES IN PRE EVICTION 16
  filter(!UrineNumber %in% Urine_PreEviction16$UrineNumber) %>% 
  
  #REMOVE SAMPLES IN POST PAIRING 16
  filter(!UrineNumber %in% Urine_PostPairing10$UrineNumber)

View(RT_Or_Cat4_Pre)

#Corbeau
View(RT_Or_Cat4_Pre %>% 
       filter(ExperimentalGroup == "Corbeau"))
#13 samples to 14 samples will be needed


#Guiness
View(RT_Or_Cat4_Pre %>% 
       filter(ExperimentalGroup == "Guinness"))
#8 to 9 samples will be needed


#############################################Post eviction ssample

#I doubt that RA will occur more than 16 days after eviction but in case that is what results suggest
RT_Or_Cat4_Post <- Urine_PostPairing %>% 
    
  #SAMPLES FROM CAT 4
  filter(EvictionCategory == "Late" & 
         is.na(Eviction_GS)) %>% #Once they will have gotten pregnant, the code will have to be changed to "PreFirstConception", I should have Corbeau and Guiness there
  
  #EVICTOR
  filter(EvictionStatus == "Evictor") %>% 
  
  #POST PAIRING AND PRE EVICTION SAMPLES
  filter(EvictionDayDiff > 0) %>% 
  
  #PRE FIRST CONCEPTION (MANUALLY ESTABLISHED BASED ON EXPECTED DOB)
  filter(ExperimentalGroup == "Guinness" & UrineDate <= "2023-02-11" |
           ExperimentalGroup == "Corbeau" & UrineDate <= "2023-02-27") %>% 
  
  #REMOVE SAMPLE ABOUT RS AT EVICTION 
  filter(!UrineNumber %in% RS_Or_Cat4$UrineNumber)

View(RT_Or_Cat4_Post)






```


#Reproductive physiology of evictee

It seems that in the first group samples were only collected up to 14 days post-eviction.

Samples collected at the end of the experiment, during the few weeks before euthanasia could also be used but they are not counted in the current count. 

##Reproductive state at eviction 

For category 1-4, we will retain D1,3,7,14,28,42. There would be the possibility to add later samples.


```{r Category 1}


RSRA_Ee_Cat1 <- Urine_PostPairing %>% 
  
  #GROUP FROM CAT 1
  filter(ExperimentalGroup %in% Cat1$ExperimentalGroup) %>% 
  
  #EVICTOR
  filter(EvictionStatus == "Evictee") %>% 
  
  #KEEP POST EVICTION SAMPLES
  filter(EvictionDayDiff >=0)

View(RSRA_Ee_Cat1)


```

For Category 2-4, we will follow the same strategy as for category 1

##Reproductive activation 

For Category 1 and 2, it is covered by RS at eviction.

For Category 3, evicted females were pregnant so RA may have occured any time until 87 days pre-parturition (they gave birth in their isolation group).

I don't tink that I need samples at eviction as females were pregnant. But I cannot exclude at this stage that this may be required

```{r Category 3}

#Reproductive activation 
RA_Ee_Cat3 <- Urine_PostPairing %>% 
  
  #SAMPLES FROM CAT 3
  filter(ExperimentalGroup %in% Cat3$ExperimentalGroup) %>% 
  
  #EVICTOR
  filter(EvictionStatus == "Evictee") %>% 
  
  #REMOVE SAMPLES IN POST PAIRING 10
  filter(!UrineNumber %in% Urine_PostPairing10$UrineNumber) %>% 
  
  #REMOVE SAMPLES IN PRE EVICTION 10
  filter(!UrineNumber %in% Urine_PreEviction16$UrineNumber)

View(RA_Ee_Cat3)
#Licher from D11 to D27 post pairing - do 10, 20, 27 + increased 
#Black Label D15 to D88 post pairing - do 15, 29, 43, 57, 74, 80, 88 + increased 

```

```{r Category 4}


#Reproductive activation 
RA_Ee_Cat4 <- Urine_PostPairing %>% 
  
  #SAMPLES FROM CAT 3
  filter(ExperimentalGroup %in% Cat4$ExperimentalGroup) %>% 
  
  #EVICTOR
  filter(EvictionStatus == "Evictee") %>% 
  
  #REMOVE SAMPLES IN POST PAIRING 10
  filter(!UrineNumber %in% Urine_PostPairing10$UrineNumber) %>% 
  
  #REMOVE SAMPLES IN PRE EVICTION 10
  filter(!UrineNumber %in% Urine_PreEviction16$UrineNumber)

View(RA_Ee_Cat4)
#Corbeau only need to do the D-87 = potentially other samples of pregnancy

#Guiness from D11 to D48 post pairing - do 11 and every 14 days after + increased time resolution

```

#Reproductive physiology in non-eviction group 

In Tusker, there is co-breeding with both females producing offspring.

0 additional samples to be collected

```{r Tusker}
View(DC_Info_F)

Tusker <- Urine_PostPairing %>% 
  #TUSKER
  filter(ExperimentalGroup == "Tusker") %>% 
  #RETAIN PRE-ACTIVATION SAMPLE
  filter(PairingDayDiff <= -87) %>% 
  #REMOVE SAMPLES IN POST PAIRING 10
  filter(!UrineNumber %in% Urine_PostPairing10$UrineNumber) %>% 
  
  #REMOVE SAMPLES IN PRE EVICTION 10
  filter(!UrineNumber %in% Urine_PreEviction16$UrineNumber)

View(Tusker)
#All samples are already accounted for 


```

In Devils Peak there is tolerance of the breeding female towards the non breeding female.

DVF048 bred on the 11 Dec 2022, she successfully conceived 30 days after pairing

DVF061 never got pregnant 

Total estimated 22 samples 

```{r Devil's Peak}

DevilsPeak_Breeder <- Urine_PostPairing %>% 
  filter(ExperimentalGroup == "DevilsPeak") %>% 
  filter(ParturitionDayDiff <= -80) %>% 
  
  #REMOVE SAMPLES IN POST PAIRING 10
  filter(!UrineNumber %in% Urine_PostPairing10$UrineNumber) %>% 
  
  #REMOVE SAMPLES IN PRE EVICTION 10
  filter(!UrineNumber %in% Urine_PreEviction16$UrineNumber)
#we may not be able to detect RA very accurately 
View(DevilsPeak_Breeder)
#one could do every second samples and add 1
#7 samples 


#Non-breeder 
DevilsPeak_NonBreeder <- Urine_PostPairing %>% 
  filter(AnimalID == "DVF061")
View(DevilsPeak_NonBreeder)
#One sample every 2 weeks then increased time resolution 
#one seample every 2 weeks + what is needed 
#ca 15 samples

```


In wicklowwolf none of the females got pregnant but pairing only occured very recently so may be to early to tell. Expect to have first 3 months every two weeks  + increased resolution. 

Will fall into another category, just unclear which one. 

Predicted 18 samples

```{r Wicklow wolf }

View(DC_Info_F %>% 
       filter(ExperimentalGroup == "WicklowWolf"))

Wicklow <- Urine_PostPairing %>% 
  filter(ExperimentalGroup == "WicklowWolf")


```


##Pre-isolation

Selection will be same for all type of females. 

The original idea is to select the last two samples before isolation. I am unsure how consistent this will be across females and treatment, so it must be checked

It seems that there is a lot of inconsistencies and I am not sure I understand why. The aim was to have two samples before pairing collected after removal of pups and before isolation.





#Isolation 

At the moment I decided to go for d1 and every week after, but I wonder if I should not chose first 2 samples and last 2 samples with everything in between with a week interval 

That would increase from 5 to 7 samples per animals 

```{r Isolation}



#Formatted
Urine_Isol_Formatted <- Urine_Isol %>% 
  
    #SELECT 
  select(Treatment,
         ExperimentalGroup,
         AnimalID,
         BS_Original,
         EvictionStatus,
         IsolationPeriod,
         IsolationDayDiff,
         PairingDayDiff,
         Count,
         UrineNumber)
  

View(Urine_Isol_Formatted)
#363 samples preisolation 


#Summary
Urine_Isol_Summary <- Urine_Isol %>% 
  group_by(ExperimentalGroup,
           AnimalID,
           Treatment,
           IsolationPeriod) %>% 
  summarize(Count = n_distinct(UrineDate)) %>% 
  ungroup()
View(Urine_Isol_Summary)


```

#post-pairing 

I need to find what is the best strategy for hormone analyses. 

i) Early gestation with confirmed conception, when did they usually conceive? 

2) Do we need to do the same for evictee if they do not activate? I guess not 

```{r Data}

names(DC_Urine_F)
############################################All group 
Urine_InGroup <- DC_Urine_F %>% 
  filter(UrineDate > PairingDate & 
           UrineDate <= EvictionDate | UrineDate > PairingDate & is.na(EvictionDate))
View(Urine_InGroup)
#472 samples InGroup 
#Includes samples where there has been no eviction yet 

#Summary
Urine_InGroup_Summary <- Urine_InGroup %>% 
  group_by(ExperimentalGroup,
           AnimalID,
           Treatment,
           PairingDate,
           InGroupPeriod) %>% 
  
  #
  
  #ADD COUNT OF SAMPLES 
  summarize(Count = n_distinct(UrineDate)) %>% 
  ungroup() %>% 
  arrange(Treatment, 
          Count)
View(Urine_InGroup_Summary)

############################################Eviction Group 



############################################Early eviction



############################################Late eviction



```

##Early eviction

```{r}

names(DC_Info_F)

#How many days before first parturition did eviction occur 

View(DC_Info_F %>% 
       filter(EvictionCategory == "Early")
       )

```


##Late eviction 

##No eviction 


#Post eviction 

```{r}

#######################################PostEviction
Urine_PostEviction <- DC_Urine_F %>% 
  filter(UrineDate > EvictionDate)
View(Urine_PostEviction)
#731 samples


```

